---
title: "Import_PigmentandCorrelationData"
author:
- Sylwia Sliwinska-Wilczewska
- Mireille Savoie
- Naaman M. Omar 
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: BalticPhotoperiod.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

Import_PigmentData.Rmd imports: 
PAMAS files from Data/RawData/PAMASData.zip folder, 
ClarioPigments from ClarioPigments Catalog,
ClarioGrowth from ClarioGrowth Catalog,
GrowthCurveData from BalticPhotoperiod_Processed_GrowthCurve.Rds, 
and OlisJazData from BalticPhotoperiod_Processed_OlisSpectraAll.Rds

and stored in Data/ImportedData/ImportedPigmentData folder as: 
BalticPhotoperiod_Imported_PigmentData.Rds

This script contains Spearman correlations performed for cell counts taken from PAMAS and OD680 taken from ClarioSTAR (cell/mL). Additionally, Spearman correlations were made for the pigment content obtained using the filter method (measured on ClarioSTAR) with the absorbance obtained from Olis (pigment content - ug/mL). The cell counts data was added to the GrowthCurveData file (the cell count was calculated based on OD680 measured on MC; cell/mL). The obtained cell number was used to convert pigments (based on Olis) per cell (fg/cell). If it make sense...

The tables with the compiled correlations were saved in the BalticPhotoperiod\Output\TablesRDS folder as:
BalticPhotoperiod_Table_GrowthCorrelation.Rds,
BalticPhotoperiod_Table_PigmentsCorrelation.Rds


# Load libraries

```{r load libraries}
library(kableExtra)
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(strucchange)
library(dplyr)
library(magrittr)
library(googledrive)
library(googlesheets4)
library(readxl)
library(ggspectra)
library(ggpubr)
library(caret)
library(gcookbook)
library(scales)
```

# Set Project Variables

```{r set project variables}
Project <- "BalticO2"
DataOut <- file.path("..", "Data", "ImportedData", "ImportedPigmentsData")

FigPath <- file.path("..", "Output", "Figures")
FigRdsPath <- file.path("..", "Output", "FiguresRds")
TableRdsPath <- file.path("..", "Output", "TablesRDS")
```


------------------------------------------------ MetaData Catalog ------------------------------------------------------

# Read MetaData Catalog

```{r read locally stored metadata from rds}
CultureCatalog <- readRDS(file = file.path("..", "Data", "ImportedData", "ImportedMetaData", "CultureCatalog.Rds"))

CultureCatalog<-CultureCatalog %>% 
  select(-c(PrimaryOperator, Temp_c, ExpCul, ExpStartTime, O2_Category, Optode, OptodeCh, OptodeMeasure))
```

-------------------------------------- OD from MC (from growth curve) -----------------------------------------

# IMPORT GROWTH CURVE DATA FOR CORRELATION
(GrowthCurve already contain mean OD per h)

# Set project variables

```{r set project variables}
Project <- "BalticO2"
DataIn <- file.path("..", "Data", "ProcessedData", "ProcessedGrowthCurveData")
```

# List Growth curve Rds

```{r Exported Rmd}
list.files(path = DataIn, pattern = Project, full.names = TRUE)
```

# Read Growth curve Rds

```{r read ProcessFile Sol}
GrowthCurveFile <- "../Data/ProcessedData/ProcessedGrowthCurveData/BalticO2_Processed_GrowthCurve.Rds"  
GrowthCurveFileName <- str_split(string = GrowthCurveFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")

GrowthCurve <- readRDS(GrowthCurveFile)  %>%
  ungroup()
```


------------------------------------------------ Chla Turner ------------------------------------------------------
# Load Turner catalog

```{r load turner catalog, message = FALSE, warning = FALSE, echo=FALSE}
gs4_deauth()
ChlData<- read_sheet("https://docs.google.com/spreadsheets/d/13mQm0B3siS65UuGjNdzvpHFomfuwn6aAg7dBoq1IqrM/edit#gid=0")

as.data.frame(ChlData)
ChlData <- ChlData 

ChlData <- ChlData %>%  
  mutate(TurChl_ugL = as.numeric(Reading_rfu) * as.numeric(Chl_slope) + as.numeric(Chl_intercept)) %>% 
  mutate(DATE = ymd(`DATE`)) %>% 
  rename(SampleID=CultureID) %>% 
  rename(ObsDate=DATE) %>% 
  select(c(SampleID, ObsDate, TurChl_ugL, TIME)) %>% 
  filter(TurChl_ugL<2500)  #outliers

```

# Prepare ObsTime_count to match with MC ToD data

```{r}
ChlData<-ChlData %>% 
    filter(str_detect(SampleID, "SySl")) %>% 
  mutate(TIME2 = as.POSIXct(strptime(TIME, format = "%H%M%S")),
         ToD = format(TIME2, "%H")) %>% 
  select(-c(TIME2)) %>% 
  mutate(ToD=as.double(ToD))
```

# Calculate Chl mean from 3 technical replica

```{r, warning = FALSE}
ChlData <- ChlData %>%
  group_by(SampleID, ObsDate) %>%
  summarize(SampleID, ObsDate, TurChl_ugL, TIME, ToD,
            meanTurChl_ugL = mean(TurChl_ugL),
            sdTurChl_ugL = sd(TurChl_ugL)) %>%
  ungroup()
```

# Merge ChlData with CultureCatalog

```{r, warning = FALSE, echo=FALSE}
ChlDataMeta <- CultureCatalog %>%
  full_join(., ChlData, by = c("SampleID" = "SampleID")) 

ChlDataMeta <- ChlDataMeta %>%
group_by(SampleID) %>%
  arrange(ObsDate) %>%
  mutate(E_days = as.numeric((ObsDate - ExpDate[1]))) %>%
ungroup() %>% 
  mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA77G"~"PC-rich_077")) %>% 
  drop_na(E_days)  

```


# Merge Turner and MC OD (Growth Curve) data

```{r, warning = FALSE, echo=FALSE}

GrowthCurveTurner <- GrowthCurve %>%
  full_join(., ChlDataMeta, by = c("ToD" = "ToD", "SampleID" = "SampleID", "E_days"="E_days", "Strain"="Strain","Par_ue" = "Par_ue", "Photoperiod" = "Photoperiod", "Run" = "Run", "Tube" = "Tube", "O2" = "O2", "WL" = "WL", "LightShape" = "LightShape", "ExpDate" = "ExpDate", "ExpEndDate" = "ExpEndDate")) %>% 
  drop_na(TurChl_ugL) 
  #filter(meanDeltaOD_h>0.02) 
```

# Create preliminary plots

```{r preliminary plots}

GrowthCurveTurner %>%
  ggplot() +
  geom_point(aes(x = meanDeltaOD_h, y = TurChl_ugL)) +
  #labs(y = "Number of cells (N/mL)", x = "Absorbance" ~ "("~OD[750]~")") +
  ggh4x::facet_nested(rows = vars(Strain), labeller = labeller(Ex_WL = label_both, strain = label_value, Par_ue = label_both, WL = label_both, Photoperiod = label_value)) +
  theme_bw()

```

Pearson Correlation Coefficient and Linear Regression and coefficient of determination or R²
https://www.datacamp.com/tutorial/linear-regression-R

# Calculate Pearson correlation for cell count (MD Pico) vs OD720 (MC)

```{r}

CorrDeltaTur <- GrowthCurveTurner %>% 
  filter(Strain == "PC-rich_077")
my_dataDeltaOD<- CorrDeltaTur
ggscatter(my_dataDeltaOD, x = "meanDeltaOD_h", y = "TurChl_ugL", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson")
my_dataDeltaOD
lmDeltaOD = lm(TurChl_ugL~meanDeltaOD_h, data = my_dataDeltaOD)
summary(lmDeltaOD)
# ugChlmL = (DeltaOD*5281.07)+278.01
# Adjusted R-squared: 0.5942
# R=0.77; p<2.2e-16


CorrDeltaTur <- GrowthCurveTurner %>% 
  filter(Strain == "PE-rich_127") 
my_dataDeltaOD<- CorrDeltaTur
ggscatter(my_dataDeltaOD, x = "meanDeltaOD_h", y = "TurChl_ugL", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson")
my_dataDeltaOD
lmDeltaOD = lm(TurChl_ugL~meanDeltaOD_h, data = my_dataDeltaOD)
summary(lmDeltaOD)
# ugChlmL = (DeltaOD*9502.4)+107.4
# Adjusted R-squared: 0.8311
# R=0.91; p < 2.2e-16


```

# Create table with Pearson correlation and preliminary plot (Turner vs MC DeltaOD)

```{r}

data_textPaersonBA77G_720 <- data.frame(Linear_regression = c('µg Chl a/L = (DeltaOD*5281.07)+278.01'), Strain = c("PC-rich_077"), R_square = c(0.5942), R = c(0.77), p_value = c(0))

data_textPaersonBA127R_720 <- data.frame(Linear_regression = c('µg Chl a/L = (DeltaOD*9502.4)+107.4'), Strain = c("PE-rich_127"), R_square = c(0.8311), R = c(0.91), p_value = c(0))

TurnerGrowthCorrelation_Delta<-rbind(data_textPaersonBA77G_720, data_textPaersonBA127R_720)


GrowthCurveTurner %>% 
  filter(Strain == "PC-rich_077") %>% 
  ggplot(aes(x = meanDeltaOD_h, y = TurChl_ugL)) +
  geom_point(aes(x = meanDeltaOD_h, y = TurChl_ugL), show.legend = "none", colour = "midnightblue", size = 3, alpha = 0.4) +
  geom_text(data=data_textPaersonBA77G_720, aes(x=0.06, y=10000, label=Linear_regression), size=4) +
  geom_smooth(method=lm, se=FALSE, colour = "gray22") +
  stat_cor(method="pearson") +
  #labs(y = "Number of cells (N" ~mL^-1 ~")", x = "Absorbance (720 nm)") +
  theme_bw() 


GrowthCurveTurner %>% 
  filter(Strain == "PE-rich_127") %>% 
  ggplot(aes(x = meanDeltaOD_h, y = TurChl_ugL)) +
  geom_point(aes(x = meanDeltaOD_h, y = TurChl_ugL), show.legend = "none", colour = "midnightblue", size = 3, alpha = 0.4) +
  geom_text(data=data_textPaersonBA127R_720, aes(x=0.06, y=10000, label=Linear_regression), size=4) +
  geom_smooth(method=lm, se=FALSE, colour = "gray22") +
  stat_cor(method="pearson") +
  #labs(y = "Number of cells (N" ~mL^-1 ~")", x = "Absorbance (720 nm)") +
  theme_bw() 

rm(data_textPaersonBA77G_720, data_textPaersonBA127R_720)
```
# Save RDS that create stats and tables

```{r save rds}
saveRDS(TurnerGrowthCorrelation_Delta, file.path(TableRdsPath, paste(Project, "Tab_TurnerDeltaODCorrelation.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```


--------------------------------------------------- MD Pico --------------------------------------

# IMPORT MD PICO CORRELATION DATA

```{r set project variables, warning = FALSE, echo = FALSE}
Project <- "BalticO2"
zip_file <- file.path("..", "Data", "RawData", "MDPico.zip")

# List files in the extracted folder with a ".txt" extension
CountFiles <- unzip(zip_file, list = TRUE)
CountFiles <- CountFiles[grepl(".csv$", CountFiles$Name), "Name"]
print(CountFiles)

FileID <- "ExperimentSummaryData"
FileEncode <- "UTF-8" 
HeaderRows <- 0
DelimCS <- ","
```

# Read fread_plus function

```{r data read adds filename and cdate, warning=FALSE, message=FALSE, echo=FALSE}
# Define function to read and process each file
fread_plus <- function(Flnm, FileEncode, Delim) {
  con <- unz(zip_file, Flnm)
  
  # Read the file using read.table
  data <- read.table(con, skip = HeaderRows, encoding = FileEncode, sep = Delim, header = TRUE)
  
  # Use tryCatch to handle errors during the closing of the connection
  tryCatch(
    close(con),
    error = function(e) {
      warning("Error closing connection: ", e$message)
    })
  
  data <- data %>%
    mutate(Filename = Flnm, CDateTime = ymd_hms(file.info(zip_file)$ctime)) 
  return(data)
}

# Use map_df to read and process all files in CountFiles
MDPicoTidy <- CountFiles %>%
  map_df(~fread_plus(Flnm = ., FileEncode = FileEncode, Delim = DelimCS))
```

```{r tidy CountTidy}

MDPicoTidy <- MDPicoTidy %>% 
  select(-c("Concentration", "Group", "Compound", "CDateTime")) %>% # remove superfluous columns
  mutate(Filename = str_remove(string = Filename, pattern = ".csv")) %>%
  mutate(Filename = str_remove(string = Filename, pattern = "../MDPico/")) %>%
  separate(Filename, into = c("ObsDate", "Project", "Initials",  "PlateNr", "IndStud", "Organism", "Count"), sep = "([\\/\\/\\_\\_\\_\\_\\_])", remove = FALSE) %>%
  select(-c("IndStud", "Organism", "Count")) %>% 
  mutate(ObsDate = ymd_hm(ObsDate)) 

```


Load MDPicoMetaData catalog
```{r load local metadatacatalog, message = FALSE, warning = FALSE, echo=FALSE}
gs4_deauth()

# this is the URL or ID of a Sheet readable by anyone (with a link)

MDPicoMetaData <- read_sheet("https://docs.google.com/spreadsheets/d/1Lerp5u25kzBtaBbnOYElYqUP59cn68gJpxxayhnGdkw/edit#gid=0") %>%
  #mutate(Date = as.numeric(Date)) %>%
  mutate(Date = ymd_hm(`Date`)) %>%
  separate(Date, into = c("Date_count", "Time_count"), sep = " ", remove = FALSE) %>%
  mutate(Date_count = ymd(`Date_count`)) 
```


# Merge MD Pico and Culture catalog

```{r}
MDPicoMeta <- MDPicoMetaData %>%
  left_join(., CultureCatalog, by = c("SampleID" = "SampleID")) %>% 
  drop_na(Strain)
```

# check if I do not lost some data!

```{r}
MDPicoAll <- MDPicoTidy %>%
  mutate(PlateNr = as.double(PlateNr)) %>%
  left_join(., MDPicoMeta, by = c("Well.Name" = "WellNumber", "PlateNr" = "PlateNumber")) %>% 
  drop_na(Strain)
```

```{r, warning = FALSE}
MDPicoAll <- MDPicoAll %>%
  mutate(culture_inocul_L = as.double(culture_inocul_L)) %>%
  mutate(CapAreaPercentage = as.double(CapAreaPercentage)) %>%

  mutate(CellmL_MDPico = (`Cell.Count` * (0.001/culture_inocul_L)) /(CapAreaPercentage/100)) %>%
  # mutate(cellsml = `cellsmlwithoutpercentage`/(CapAreaPercentage/100))
group_by(Date, SampleID) %>%

summarize(Well.Name, Cell.Count, Filename, ObsDate, PlateNr, PlateID, SampleID, Date, Date_count, Time_count, media_inocul_L, culture_inocul_L, CapAreaPercentage, Run, Strain, ExpDate, Par_ue, Photoperiod, PARPhotonDose_day, Tube, O2, WL, LightShape, ExpEndDate, CellmL_MDPico, meanCellmL_MDPico = mean(CellmL_MDPico), sdCellmL_MDPico = sd(CellmL_MDPico)) %>%

ungroup() %>%
  
group_by(SampleID) %>%
  arrange(Date_count) %>%
  mutate(E_days = as.numeric((Date_count - ExpDate[1]))) %>%
ungroup() %>% 
  rename(Cell_Count=Cell.Count) %>% 
  rename(Well_Name=Well.Name) %>% 
  rename(MeasDate = ObsDate) %>% 
  rename(ObsDateTime = Date) %>% 
  rename(ObsDate_count = Date_count) %>% 
  rename(ObsTime_count = Time_count) %>% 
  rename(FilenameMDPico=Filename)  
```

# Create Preliminary plot

```{r preliminary plot}
MDPicoAll %>%
  ggplot() +
  geom_point(aes(x = E_days, y = meanCellmL_MDPico)) +
  ggh4x::facet_nested(rows = vars(Par_ue), cols = vars(Strain, Photoperiod), labeller = labeller(Ex_WL = label_both, strain = label_value, Par_ue = label_both, WL = label_both, Photoperiod = label_value)) +
  theme_bw()

MDPicoAll %>%
  filter(WL!=405 & WL!= 730 & WL!= 450 & WL!= 470) %>% 
  ggplot() +
  geom_point(aes(x = E_days, y = meanCellmL_MDPico)) +
  ggh4x::facet_nested(rows = vars(Par_ue), cols = vars(Strain, Photoperiod), labeller = labeller(Ex_WL = label_both, strain = label_value, Par_ue = label_both, WL = label_both, Photoperiod = label_value)) +
  theme_bw()
```

# Removing unrevelant column

```{r}
#colnames(MDPicoAll)
MDPicoAll <- MDPicoAll %>%
  select(-c(MeasDate, PlateNr, PlateID, Well_Name, media_inocul_L, culture_inocul_L, CapAreaPercentage)) %>% 
  drop_na(Cell_Count)
```

# Cleaning the environment

```{r}
rm(CultureCatalog, MDPicoMeta, MDPicoMetaData, MDPicoTidy)
```

# Save rds for further analysis if needed

```{r save rds}
# saveRDS(MDPicoAll, file.path(DataOut, paste(Project, "Imported_MDPicoData.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```


-------------------------------------# MD Pico vs. MC OD (Growth Curve) correlation ---------------------------------------

# Prepare ObsTime_count to match with MC ToD data

```{r}
MDPicoAll<-MDPicoAll %>% 
  mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA77G"~"PC-rich_077")) %>% 
  mutate(ObsTime_count=as.character(ObsTime_count))
  
MDPicoAll$ToD<-gsub("([0-9]+):.*", "\\1", MDPicoAll$ObsTime_count)

MDPicoAll<-MDPicoAll %>% 
  mutate(ToD=as.double(ToD))
```

# Merge MD Pico and MC OD (Growth Curve) data

```{r, warning = FALSE, echo=FALSE}
MCMDPicoCorr <- GrowthCurve %>%
  full_join(., MDPicoAll, by = c("ToD" = "ToD", "SampleID" = "SampleID", "E_days"="E_days", "Strain"="Strain","Par_ue" = "Par_ue", "Photoperiod" = "Photoperiod", "Run" = "Run", "Tube" = "Tube", "O2" = "O2", "WL" = "WL", "LightShape" = "LightShape", "ExpDate" = "ExpDate", "ExpEndDate" = "ExpEndDate"))  %>% 
  drop_na(meanOD680_h) %>% 
  drop_na(Cell_Count)
```

# Create preliminary plots

```{r preliminary plots}

MCMDPicoCorr %>%
  ggplot() +
  geom_point(aes(x = meanOD680_h, y = CellmL_MDPico)) +
  #labs(y = "Number of cells (N/mL)", x = "Absorbance" ~ "("~OD[750]~")") +
  ggh4x::facet_nested(rows = vars(Strain), labeller = labeller(Ex_WL = label_both, strain = label_value, Par_ue = label_both, WL = label_both, Photoperiod = label_value)) +
  theme_bw()

MCMDPicoCorr %>%
  ggplot() +
  geom_point(aes(x = meanOD720_h, y = CellmL_MDPico)) +
  #labs(y = "Number of cells (N/mL)", x = "Absorbance" ~ "("~OD[750]~")") +
  ggh4x::facet_nested(rows = vars(Strain), labeller = labeller(Ex_WL = label_both, strain = label_value, Par_ue = label_both, WL = label_both, Photoperiod = label_value)) +
  theme_bw()

MCMDPicoCorr %>%
  ggplot() +
  geom_point(aes(x = meanDeltaOD_h, y = CellmL_MDPico)) +
  #labs(y = "Number of cells (N/mL)", x = "Absorbance" ~ "("~OD[750]~")") +
  ggh4x::facet_nested(rows = vars(Strain), labeller = labeller(Ex_WL = label_both, strain = label_value, Par_ue = label_both, WL = label_both, Photoperiod = label_value)) +
  theme_bw()
```
Pearson Correlation Coefficient and Linear Regression and coefficient of determination or R²
https://www.datacamp.com/tutorial/linear-regression-R

# Calculate Pearson correlation for cell count (MD Pico) vs OD720 (MC)

```{r}

CorrCleanOD720 <- MCMDPicoCorr %>% 
  filter(Strain == "PC-rich_077")
my_dataOD720<- CorrCleanOD720
ggscatter(my_dataOD720, x = "meanOD720_h", y = "CellmL_MDPico", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson")
my_dataOD720
lmOD720 = lm(CellmL_MDPico~meanOD720_h, data = my_dataOD720)
summary(lmOD720)
# NmL = (OD720*235186505)+6189673
# Adjusted R-squared: 0.9291
# R=0.96; p<2.2e-16


CorrCleanOD720 <- MCMDPicoCorr %>% 
  filter(Strain == "PE-rich_127") 
my_dataOD720<- CorrCleanOD720
ggscatter(my_dataOD720, x = "meanOD720_h", y = "CellmL_MDPico", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson")
my_dataOD720
lmOD720 = lm(CellmL_MDPico~meanOD720_h, data = my_dataOD720)
summary(lmOD720)
# NmL = (OD720*306469787)+9429269
# Adjusted R-squared: 0.7691
# R=0.88; p < 2.2e-16

```

# Calculate Pearson correlation for cell count (MD Pico) vs OD680 (MC)

```{r}

CorrCleanOD680 <- MCMDPicoCorr %>% 
  filter(Strain == "PC-rich_077")
my_dataOD680<- CorrCleanOD680
ggscatter(my_dataOD680, x = "meanOD680_h", y = "CellmL_MDPico", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson")
my_dataOD680
lmOD680 = lm(CellmL_MDPico~meanOD680_h, data = my_dataOD680)
summary(lmOD680)
# NmL = (OD680*180449619)+4614995
# Adjusted R-squared: 0.9458
# R=0.97; p<2.2e-16


CorrCleanOD680 <- MCMDPicoCorr %>% 
  filter(Strain == "PE-rich_127") 
my_dataOD680<- CorrCleanOD680
ggscatter(my_dataOD680, x = "meanOD680_h", y = "CellmL_MDPico", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson")
my_dataOD680
lmOD680 = lm(CellmL_MDPico~meanOD680_h, data = my_dataOD680)
summary(lmOD680)
# NmL = (OD680*237967540)+9721218
# Adjusted R-squared: 0.7711
# R=0.88; p < 2.2e-16

```

# Create table with Pearson correlation and preliminary plot (MD Pico vs MC OD720)

```{r}

data_textPaersonBA77G_720 <- data.frame(Linear_regression = c('N/mL = (OD720*235186505)+6189673'), Strain = c("PC-rich_077"), OD = c("720"), R_square = c(0.9291), R = c(0.96), p_value = c(0))

data_textPaersonBA127R_720 <- data.frame(Linear_regression = c('N/mL = (OD720*306469787)+9429269'), Strain = c("PE-rich_127"), OD = c("720"), R_square = c(0.7691), R = c(0.88), p_value = c(0))

MDPicoGrowthCorrelation_720<-rbind(data_textPaersonBA77G_720, data_textPaersonBA127R_720)


MCMDPicoCorr %>% 
  filter(Strain == "PC-rich_077") %>% 
  ggplot(aes(x = meanOD720_h, y = CellmL_MDPico)) +
  geom_point(aes(x = meanOD720_h, y = CellmL_MDPico), show.legend = "none", colour = "midnightblue", size = 3, alpha = 0.4) +
  geom_text(data=data_textPaersonBA77G_720, aes(x=0.06, y=20000, label=Linear_regression), size=4) +
  geom_smooth(method=lm, se=FALSE, colour = "gray22") +
  stat_cor(method="pearson") +
  labs(y = "Number of cells (N" ~mL^-1 ~")", x = "Absorbance (720 nm)") +
  theme_bw() 

MCMDPicoCorr %>% 
  filter(Strain == "PE-rich_127") %>% 
  ggplot(aes(x = meanOD720_h, y = CellmL_MDPico)) +
  geom_point(aes(x = meanOD720_h, y = CellmL_MDPico), show.legend = "none", colour = "midnightblue", size = 3, alpha = 0.4) +
  geom_text(data=data_textPaersonBA127R_720, aes(x=0.06, y=20000, label=Linear_regression), size=4) +
  geom_smooth(method=lm, se=FALSE, colour = "gray22") +
  stat_cor(method="pearson") +
  labs(y = "Number of cells (N" ~mL^-1 ~")", x = "Absorbance (720 nm)") +
  theme_bw() 

rm(data_textPaersonBA77G_720, data_textPaersonBA127R_720)
```

# Create table with Pearson correlation and preliminary plot (MD Pico vs MC OD680)

```{r}

data_textPaersonBA77G_680 <- data.frame(Linear_regression = c('N/mL = (OD680*180449619)+4614995'), Strain = c("PC-rich_077"), OD = c("680"), R_square = c(0.9458), R = c(0.971), p_value = c(0))

data_textPaersonBA127R_680 <- data.frame(Linear_regression = c('N/mL = (OD680*237967540)+9721218'), Strain = c("PE-rich_127"), OD = c("680"), R_square = c(0.7711), R = c(0.88), p_value = c(0))

MDPicoGrowthCorrelation_680<-rbind(data_textPaersonBA77G_680, data_textPaersonBA127R_680)


MCMDPicoCorr %>% 
  filter(Strain == "PC-rich_077") %>% 
  ggplot(aes(x = meanOD680_h, y = CellmL_MDPico)) +
  geom_point(aes(x = meanOD680_h, y = CellmL_MDPico), show.legend = "none", colour = "midnightblue", size = 3, alpha = 0.4) +
  geom_text(data=data_textPaersonBA77G_680, aes(x=0.06, y=20000, label=Linear_regression), size=4) +
  geom_smooth(method=lm, se=FALSE, colour = "gray22") +
  stat_cor(method="pearson") +
  labs(y = "Number of cells (N" ~mL^-1 ~")", x = "Absorbance (OD680 nm)") +
  theme_bw()


MCMDPicoCorr %>% 
  filter(Strain == "PE-rich_127") %>% 
  ggplot(aes(x = meanOD680_h, y = CellmL_MDPico)) +
  geom_point(aes(x = meanOD680_h, y = CellmL_MDPico), show.legend = "none", colour = "midnightblue", size = 3, alpha = 0.4) +
  geom_text(data=data_textPaersonBA127R_680, aes(x=0.06, y=20000, label=Linear_regression), size=4) +
  geom_smooth(method=lm, se=FALSE, colour = "gray22") +
  stat_cor(method="pearson") +
  labs(y = "Number of cells (N" ~mL^-1 ~")", x = "Absorbance (OD680 nm)") +
  theme_bw() 

rm(data_textPaersonBA77G_680, data_textPaersonBA127R_680)
```
# Create table with equations obtained from Pearson correlation (for calculate number of cells based on OD)

```{r}
MDPicoGrowthCorrelation<-rbind(MDPicoGrowthCorrelation_680, MDPicoGrowthCorrelation_720)

rm(MDPicoGrowthCorrelation_680, MDPicoGrowthCorrelation_720)
```

# Save RDS that create stats and tables

```{r save rds}
saveRDS(MDPicoGrowthCorrelation, file.path(TableRdsPath, paste(Project, "Tab_MDPicoMCODCorrelation.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Cleaning the environment

```{r}
rm(lmOD680, lmOD720, CorrCleanOD720, CorrCleanOD680, my_dataOD680, my_dataOD720)
```




---------------------------------------------- Olis-pigments correlation --------------------------------

# IMPORT OLIS DATA FOR PIGMENTS CORRELATION

```{r set project variables}
Project <- "BalticO2"
DataIn <- file.path("..", "Data", "ProcessedData", "ProcessedOlisJazData")
```

# List OlisJaz Rds

```{r Exported Rmd}
list.files(path = DataIn, pattern = Project, full.names = TRUE)
```
# Read OlisJaz Rds

```{r read ProcessFile}
OlisFile <- "../Data/ProcessedData/ProcessedOlisJazData/BalticO2_Processed_OlisSpectraAll.Rds"  

OlisFileName <- str_split(string = OlisFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")
Olis <- readRDS(OlisFile)  %>%
  ungroup()
```

# CORRELATION OLIS VS PIGMENTS (FILTERS) DATA

# Calculate pigments correlation - to get raw spectra (without dilution factor from Olis, I multipied Absorbance *4; 4mL culture and 4 mL of f2 media from Olis)

665 - chl
480 - car
565	- PE
620	- PC
650 - APC

```{r}
Olis <- Olis %>% 
  mutate(Absorbance = Absorbance*4)

Absorbance665 <- Olis %>% 
  filter(nm == 665) %>%
  mutate(Abs665 = Absorbance) %>%
  select(SampleID, Strain, Abs665, Par_ue, Photoperiod, E_days)
OLISSpectraMeta665 <- Olis %>%
  left_join(., Absorbance665) 

Absorbance480 <- OLISSpectraMeta665 %>% 
  filter(nm == 480) %>%
  mutate(Abs480 = Absorbance) %>%
  select(SampleID, Strain, Abs480, Par_ue, Photoperiod, E_days)
OLISSpectraMeta480 <- OLISSpectraMeta665 %>%
  left_join(., Absorbance480) 

Absorbance565 <- OLISSpectraMeta480 %>% 
  filter(nm == 565) %>%
  mutate(Abs565 = Absorbance) %>%
  select(SampleID, Strain, Abs565, Par_ue, Photoperiod, E_days)
OLISSpectraMeta565 <- OLISSpectraMeta480 %>%
  left_join(., Absorbance565) 

Absorbance620 <- OLISSpectraMeta565 %>% 
  filter(nm == 620) %>%
  mutate(Abs620 = Absorbance) %>%
  select(SampleID, Strain, Abs620, Par_ue, Photoperiod, E_days)
OLISSpectraMeta620 <- OLISSpectraMeta565 %>%
  left_join(., Absorbance620) 

Absorbance650 <- OLISSpectraMeta620 %>% 
  filter(nm == 650) %>%
  mutate(Abs650 = Absorbance) %>%
  select(SampleID, Strain, Abs650, Par_ue, Photoperiod, E_days)
OLISSpectraMeta650 <- OLISSpectraMeta620 %>%
  left_join(., Absorbance650) 

OLISSpectraMeta<-OLISSpectraMeta650
```

# Preparing OLISSpectraMeta for correlation

```{r}
#colnames(OLISSpectraMeta)

OLISSpectraMeta <- OLISSpectraMeta %>%
  select(-c(SumAb, SumAbNorm, AbsNorm440, nm, Absorbance, Abs440, EmJaz722, EmJaz612, EmJaz441, EmNormJaz722, EmNormJaz441, EmNormJaz612, EmJaz600, EmJaz521, EmJaz393, EmNormJaz521, EmNormJaz600, EmNormJaz393, EmJaz647, EmJaz469, PURNorm, EmNormJaz647, EmNormJaz469, PURNormSum, EmMax_nm)) %>% 
  unique()

rm(Absorbance650, Absorbance620, Absorbance565, Absorbance480, Absorbance665, OLISSpectraMeta650, OLISSpectraMeta620, OLISSpectraMeta565, OLISSpectraMeta480, OLISSpectraMeta665)
```

# Estimated pigment content (ug/mL) based on Olis calibration (from BalticPhotoperiod project)

```{r}
OLISSpectraMeta <- OLISSpectraMeta %>% 

  mutate(ChlaugmL = (Abs665*13.411029)+0.154793) %>% 
  mutate(CarugmL = (Abs480*5.469880)+0.089971) %>% 
  mutate(PEugmL = (Abs565*26.760737)-0.143872) %>% 
  mutate(PCugmL = (Abs620*29.979866)-0.182611) %>% 
  mutate(APCugmL = (Abs650*3.873803)+0.021964) %>% 

  mutate(PhycougmL = PEugmL+PCugmL+APCugmL) %>% 
  mutate(CarChlaRatio = CarugmL/ChlaugmL) %>% 
  mutate(PhycoChlaRatio = PhycougmL/ChlaugmL) %>% 
  mutate(PEPCRatio = PEugmL/PCugmL)
```


# Save Rds for further analysis if needed

```{r save rds}
# saveRDS(PigmentsClarioOlisCorr, file.path(DataOut, paste(Project, "Imported_PigmentsClarioOlisCorrData.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```


------------------------------------------------------ESTIMATIONS --------------------------------------------------

-------------------------- Estimated ug Chl ug/L every h based on correlation from Turner -----------------------------

# Estimated number of ug Chl ug/L every h based on correlation from Turner


```{r}
# based on MDPico correlation

MCBA77G <- GrowthCurve %>% 
filter(Strain == "PC-rich_077") %>% 
mutate(Chla_ugL_Tur = 5281.07*meanDeltaOD_h+278.01) 

MCBA127R <- GrowthCurve %>% 
filter(Strain == "PE-rich_127") %>% 
mutate(Chla_ugL_Tur = 9502.4*meanDeltaOD_h+107.4)

GrowthCurve_Turner <- rbind(MCBA127R, MCBA77G)

rm(MCBA127R, MCBA77G)
```


-------------------------- Estimated number of cells/mL every h based on correlation from MDPico -----------------------------


# Estimated number of cells/mL every h based on correlation from MDPico (MDPicoGrowthCorrelation)




```{r}
# based on MDPico correlation

MCBA77G <- GrowthCurve %>% 
filter(Strain == "PC-rich_077") %>% 
mutate(cellmL_OD680_MDPico = 180449619*meanOD680_h+4614995) %>% 
mutate(cellmL_OD720_MDPico = 235186505*meanOD680_h+6189673) 

MCBA127R <- GrowthCurve %>% 
filter(Strain == "PE-rich_127") %>% 
mutate(cellmL_OD680_MDPico = 237967540*meanOD680_h+9721218) %>% 
mutate(cellmL_OD720_MDPico = 306469787*meanOD680_h+9429269) 

GrowthCurve_cellmL <- rbind(MCBA127R, MCBA77G)

rm(MCBA127R, MCBA77G)
```

----------------------------------------------------------------------------------------------------------------------
----------------------------------- Final Turner and MDPIco vs Growt Curve ----------------------------------------------
------------------------------------------------------------------------------------------------------------------------

```{r}
# based on MDPico correlation

  
MCBA77G <- GrowthCurve %>% 
filter(Strain == "PC-rich_077") %>% 
mutate(cellmL_OD680_MDPico = 180449619*meanOD680_h+4614995) %>% 
mutate(cellmL_OD720_MDPico = 235186505*meanOD680_h+6189673) %>% 
mutate(Chla_ugL_Tur = 5281.07*meanDeltaOD_h+278.01) 
  

MCBA127R <- GrowthCurve %>% 
filter(Strain == "PE-rich_127") %>% 
mutate(cellmL_OD680_MDPico = 237967540*meanOD680_h+9721218) %>% 
mutate(cellmL_OD720_MDPico = 306469787*meanOD680_h+9429269) %>% 
mutate(Chla_ugL_Tur = 9502.4*meanDeltaOD_h+107.4)

GrowthCurve_All <- rbind(MCBA127R, MCBA77G)

rm(MCBA127R, MCBA77G)
```


-----------------------------------------------PIGMENTS PER CELL -------------------------------------------------

------------------------# Estimated Pigments content per cell (pg/cell) - based on MDPico correlations-----------------------


# Merge growth curve with cell/mL (MDPico) with pigments content based on Olis

```{r, warning = FALSE, echo = FALSE}
MC_cellmLPigment_MDPico <- GrowthCurve_All %>%
  left_join(., OLISSpectraMeta, by = c("SampleID"="SampleID", "Run" = "Run", "Strain" = "Strain", "ExpDate" = "ExpDate", "Par_ue" = "Par_ue", "Photoperiod" = "Photoperiod", "Tube" = "Tube", "O2" = "O2", "WL" = "WL", "LightShape" = "LightShape", "ExpEndDate"="ExpEndDate","E_days" = "E_days")) 
```

# Estimated Pigments content per cell (pg/cell) - based on MDPico correlations

I got a NA in some places b/c I do not measure Olis every day (MC df contain OD for every day and every h. 
I got the same value of pigments (ug/mL) throught the day however, not the same value for pg/cell b/c number of cells changed through the day)

```{r}
MC_cellmLPigment_MDPico <- MC_cellmLPigment_MDPico %>%
  mutate(Chlapgcell = (ChlaugmL/cellmL_OD680_MDPico)*1000000) %>% 
  mutate(Carpgcell = (CarugmL/cellmL_OD680_MDPico)*1000000) %>% 
  mutate(PEpgcell = (PEugmL/cellmL_OD680_MDPico)*1000000) %>% 
  mutate(PCpgcell = (PCugmL/cellmL_OD680_MDPico)*1000000) %>% 
  mutate(APCpgcell = (APCugmL/cellmL_OD680_MDPico)*1000000) %>% 
  mutate(Phycopgcell = (PhycougmL/cellmL_OD680_MDPico)*1000000)
```

# Create preliminary plot

```{r preliminary plot}
lab1=c(expression("PC-rich_077"), expression("PE-rich_127"))

MC_cellmLPigment_MDPico %>%
  filter(Par_ue !=30) %>% 
  filter(WL!= "WW") %>% 
  ggplot() +
  geom_point(aes(x = E_days, y = PhycoChlaRatio, colour = as.factor(Strain)),  alpha = 0.9, size = 3, show.legend = T) +
  scale_colour_discrete(type=c("palegreen3", "brown4"), name="", labels = lab1) +
  scale_y_continuous(breaks=seq(0, 15, by = 3)) +
  coord_cartesian(ylim = c(-0.5, 15.5)) +
  #labs(y = "Chl" ~italic(a)~ "content ( pg " ~ cell^-1~")", x = "Elapsed time (h)") +
  #ggh4x::facet_nested(cols = vars(WL, Photoperiod), rows = vars(O2, Par_ue), labeller = labeller(Strain = label_value)) +
    ggh4x::facet_nested(cols = vars(WL), rows = vars(factor(O2, levels=c("21","0"))), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        panel.spacing.x = unit(0.4, 'cm'),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.title = element_blank(),
        legend.position = c(0.09,0.90),
        legend.text = element_text(size=10))
```

# Save plot 

```{r save plot}
ggsave(file = file.path(FigPath, paste("Fig_PhycoChlaRatio",".png",sep = "")), height=4, width= 6,  dpi = 300, limitsize = TRUE)
```


# Save rds for further analysis

```{r save rds}
saveRDS(MC_cellmLPigment_MDPico, file.path(DataOut, paste(Project, "Imported_PigmentsData.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```




# Removed unneccessary df from the environment

```{r}
# rm(MCBA127R, MCBA48R, MCBA56G, MCBA77G, MC_cellmL, CultureCatalog, GrowthCurve, PamasTidy, PigmentsClario, ClarioGrowth, PigmentsClarioOlisCorr, ClarioPamasCorr)
```


# Variable names used in Data Dictionary

```{r}
colnames(MC_cellmLPigment_MDPico)
```

# Correlations from Polish flowcytometer (BD Accuri) and Polish Spec if needed

```{r}
# GrowthClarioN <- GrowthClario %>%
#   mutate(OD750N = case_when(
#           Strain == 'BA77G' ~ 5766620.03*OD750+5146.44,
#          Strain == 'BA56G' ~ 815627.77*OD750-6499.89, 
#          Strain == 'BA48R' ~ 110516351.55*OD750-568505.87,
#          Strain == 'BA127R' ~ 124271003.22*OD750-1691760.02))
```


