---
title: "Process_OlisJazEmData"
author:
- Sylwia Sliwinska-Wilczewska
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: BalticPhotoperiod.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

Process_OlisJazEmData.Rmd processes and combines BalticPhotoperiod_Imported_JazEmData.Rds from Data/ImportedData/ImportedJazEmData folder and BalticPhotoperiod_Imported_OlisData.Rds from Data/ImportedData/ImportedOlisData folder. This .Rmd generates BalticPhotoperiod_Processed_OlisSpectraAll.Rds and BalticPhotoperiod_Processed_OlisSpectraTidy.Rds (both stored in Data/ProcessedData/ProcessedOlisJazData folder) and 1 plot (stored in Output/Figures folder).

# Load Libraries and set Project Variables

```{r load libraries, warning = FALSE, echo=FALSE} 


library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(strucchange)
library(ggspectra)
library(ggpubr)
library(caret)
library(photobiologyWavebands)
library(reshape2)
library(photobiology)
library(gcookbook)

library(googledrive)
library(googlesheets4)
library(readxl)
library(tidyverse)
library(lubridate)
```

```{r set project variables}
Project <- "BalticO2"
DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedOlisJazData")
DataInOlis <- file.path("..", "Data", "ImportedData", "ImportedOlisData", fsep = .Platform$file.sep)
DataInJaz <- file.path("..", "Data", "ImportedData", "ImportedJazEmData", fsep = .Platform$file.sep)

FigPath <- file.path("..", "Output", "Figures")
FigRdsPath <- file.path("..", "Output", "FiguresRds")
TableRdsPath <- file.path("..", "Output", "TablesRDS")

FileEncode <- "UTF-8" 
Delimiter <- ""
HeaderRows <- 0
```

# List and read imported Olis and Jaz files

```{r exported Rmd only first time in session}
list.files(path = DataInOlis, pattern = Project, full.names = TRUE)
list.files(path = DataInJaz, pattern = Project, full.names = TRUE)
```

```{r read imported Olis file}
OLISSpectraFile <- "../Data/ImportedData/ImportedOlisData/BalticO2_Imported_OlisData.Rds"
OLISSpectraFileName <- str_split(string = OLISSpectraFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")
OLISSpectra <- readRDS(OLISSpectraFile)  %>%
  ungroup()

JazFile <- "../Data/ImportedData/ImportedJazEmData/BalticO2_Imported_JazEmData.Rds"
JazFileName <- str_split(string = JazFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")
JazData <- readRDS(JazFile)  %>%
  ungroup()
```

# Preparing df for further analysis

```{r}
JazData<-JazData %>% 
  #filter(WL != "WW") %>% 
  select(-c(MCMeasuredPar_uE, MCSetPar_uE))
```

# Normalize Jaz emission to 405 nm

```{r Normalization Jaz emission at 405}
EmissionJaz405 <- JazData %>%
  filter(WL==405) %>% 
  filter(MCEm_nm == 393) %>%
  mutate(EmJaz393 = Emission) %>%
  select(EmJaz393) 

JazDataRoundMeta405 <- JazData %>%
  filter(WL==405) %>% 
  cross_join(., EmissionJaz405) %>%
  mutate(EmNormJaz393 = Emission / EmJaz393)

rm(EmissionJaz405)
```

# Normalize Jaz emission to 450 nm

```{r Normalization Jaz emission at 450}
EmissionJaz450 <- JazData %>%
  filter(WL==450) %>% 
  filter(MCEm_nm == 441) %>%
  mutate(EmJaz441 = Emission) %>%
  select(EmJaz441)

JazDataRoundMeta450 <- JazData %>%
  filter(WL==450) %>% 
  cross_join(., EmissionJaz450) %>%
  mutate(EmNormJaz441 = Emission / EmJaz441)

rm(EmissionJaz450)
```

# Normalize Jaz emission to 470 nm

```{r Normalization Jaz emission at 470}
EmissionJaz470 <- JazData %>%
  filter(WL==470) %>% 
  filter(MCEm_nm == 469) %>%
  mutate(EmJaz469 = Emission) %>%
  select(EmJaz469) 

JazDataRoundMeta470 <- JazData %>%
  filter(WL==470) %>% 
  cross_join(., EmissionJaz470) %>%
  mutate(EmNormJaz469 = Emission / EmJaz469)

rm(EmissionJaz470)
```

# Normalize Jaz emission to 530 nm

```{r Normalization Jaz emission at 530}
EmissionJaz530 <- JazData %>%
  filter(WL==530) %>% 
  filter(MCEm_nm == 521) %>%
  mutate(EmJaz521 = Emission) %>%
  select(EmJaz521)

JazDataRoundMeta530 <- JazData %>%
  filter(WL==530) %>% 
  cross_join(., EmissionJaz530) %>%
  mutate(EmNormJaz521 = Emission / EmJaz521)

rm(EmissionJaz530)
```

# Normalize Jaz emission to 620 nm

```{r Normalization Jaz emission at 620}
EmissionJaz620 <- JazData %>%
  filter(WL==620) %>% 
  filter(MCEm_nm == 612) %>%
  mutate(EmJaz612 = Emission) %>%
  select(EmJaz612) 

JazDataRoundMeta620 <- JazData %>%
  filter(WL==620) %>% 
  cross_join(., EmissionJaz620) %>%
  mutate(EmNormJaz612 = Emission / EmJaz612)

rm(EmissionJaz620)
```

# Normalize Jaz emission to 660 nm

```{r Normalization Jaz emission at 660}
EmissionJaz660 <- JazData %>%
  filter(WL==660) %>% 
  filter(MCEm_nm == 647) %>%
  mutate(EmJaz647 = Emission) %>%
  select(EmJaz647)

JazDataRoundMeta660 <- JazData %>%
  filter(WL==660) %>% 
  cross_join(., EmissionJaz660) %>%
  mutate(EmNormJaz647 = Emission / EmJaz647)

rm(EmissionJaz660)
```

# Normalize Jaz emission to 730 nm

```{r Normalization Jaz emission at 730}
EmissionJaz730 <- JazData %>%
  filter(WL==730) %>% 
  filter(MCEm_nm == 722) %>%
  mutate(EmJaz722 = Emission) %>%
  select(EmJaz722) 

JazDataRoundMeta730 <- JazData %>%
  filter(WL==730) %>% 
  cross_join(., EmissionJaz730) %>%
  mutate(EmNormJaz722 = Emission / EmJaz722)

rm(EmissionJaz730)
```

# Normalize Jaz emission to WW

```{r Normalization Jaz emission at WW}
EmissionJazWW <- JazData %>%
  filter(WL== "WW") %>%
  filter(MCEm_nm == 600) %>%
  mutate(EmJaz600 = Emission) %>%
  select(EmJaz600) 

JazDataRoundMetaWW <- JazData %>%
  filter(WL== "WW") %>%
  cross_join(., EmissionJazWW) %>%
  mutate(EmNormJaz600 = Emission / EmJaz600)

rm(EmissionJazWW)
```
# Merge df to have all WL

```{r}
JazDataRoundMeta1 <- JazDataRoundMeta730 %>%
  full_join(., JazDataRoundMetaWW, by = c("FilenameJaz"= "FilenameJaz", "WL" = "WL", "MCEm_nm" = "MCEm_nm", "Emission" = "Emission", "MC"="MC", "EmMax_nm"="EmMax_nm", "ObsDateJaz"="ObsDateJaz"))
 
JazDataRoundMeta2 <- JazDataRoundMeta1 %>%
  full_join(., JazDataRoundMeta660, by = c("FilenameJaz"= "FilenameJaz", "WL" = "WL", "MCEm_nm" = "MCEm_nm", "Emission" = "Emission", "MC"="MC", "EmMax_nm"="EmMax_nm", "ObsDateJaz"="ObsDateJaz")) 

JazDataRoundMeta3 <- JazDataRoundMeta2 %>%
  full_join(., JazDataRoundMeta620, by = c("FilenameJaz"= "FilenameJaz", "WL" = "WL", "MCEm_nm" = "MCEm_nm", "Emission" = "Emission", "MC"="MC", "EmMax_nm"="EmMax_nm", "ObsDateJaz"="ObsDateJaz")) 

JazDataRoundMeta4 <- JazDataRoundMeta3 %>%
  full_join(., JazDataRoundMeta530, by = c("FilenameJaz"= "FilenameJaz", "WL" = "WL", "MCEm_nm" = "MCEm_nm", "Emission" = "Emission", "MC"="MC", "EmMax_nm"="EmMax_nm", "ObsDateJaz"="ObsDateJaz")) 

JazDataRoundMeta5 <- JazDataRoundMeta4 %>%
  full_join(., JazDataRoundMeta470, by = c("FilenameJaz"= "FilenameJaz", "WL" = "WL", "MCEm_nm" = "MCEm_nm", "Emission" = "Emission", "MC"="MC", "EmMax_nm"="EmMax_nm", "ObsDateJaz"="ObsDateJaz")) 

JazDataRoundMeta6 <- JazDataRoundMeta5 %>%
  full_join(., JazDataRoundMeta450, by = c("FilenameJaz"= "FilenameJaz", "WL" = "WL", "MCEm_nm" = "MCEm_nm", "Emission" = "Emission", "MC"="MC", "EmMax_nm"="EmMax_nm", "ObsDateJaz"="ObsDateJaz")) 

JazDataRoundMeta <- JazDataRoundMeta6 %>%
  full_join(., JazDataRoundMeta405, by = c("FilenameJaz"= "FilenameJaz", "WL" = "WL", "MCEm_nm" = "MCEm_nm", "Emission" = "Emission", "MC"="MC", "EmMax_nm"="EmMax_nm", "ObsDateJaz"="ObsDateJaz")) 


rm(JazDataRoundMeta1, JazDataRoundMeta2, JazDataRoundMeta3, JazDataRoundMeta4, JazDataRoundMeta5, JazDataRoundMeta6, JazDataRoundMeta405, JazDataRoundMeta450, JazDataRoundMeta470, JazDataRoundMeta530, JazDataRoundMeta620, JazDataRoundMeta660, JazDataRoundMeta730, JazDataRoundMetaWW)
```

# Prepare O;isSpectra

```{r}
OLISSpectra<-OLISSpectra %>% 
  filter(Par_ue != 30)
```

```{r}
JazDataRoundMeta<-JazDataRoundMeta %>% 
  select(-c(MC, Emission))
```


# Merge Olis and Jaz data

```{r combine Olis spectra and Jaz data}
OLISSpectraMeta <- OLISSpectra %>%
  left_join(., JazDataRoundMeta, by = c("nm" = "MCEm_nm", "WL" = "WL")) %>%
  unique()
```

# Estimate PUR

```{r estimate PUR}
OLISSpectraMetaPUR405 <- OLISSpectraMeta %>%
  filter(WL==405) %>% 
  mutate(PURNorm = (AbsNorm440*EmNormJaz393)) %>% 
  group_by(WL, Strain, Par_ue, Photoperiod, E_days, O2) %>%
  mutate(PURNormSum = sum(PURNorm)) %>% 
  mutate(SumEmNormJaz = sum(EmNormJaz393)) %>% 
  mutate(PUR = Par_ue*(PURNormSum/SumEmNormJaz)) %>% 
  ungroup() 

OLISSpectraMetaPUR450 <- OLISSpectraMeta %>%
  filter(WL==450) %>% 
  mutate(PURNorm = (AbsNorm440*EmNormJaz441)) %>% 
  group_by(WL, Strain, Par_ue, Photoperiod, E_days, O2) %>%
  mutate(PURNormSum = sum(PURNorm)) %>% 
  mutate(SumEmNormJaz = sum(EmNormJaz441)) %>% 
  mutate(PUR = Par_ue*(PURNormSum/SumEmNormJaz)) %>% 
  ungroup() 

OLISSpectraMetaPUR470 <- OLISSpectraMeta %>%
  filter(WL==470) %>% 
  mutate(PURNorm = (AbsNorm440*EmNormJaz469)) %>% 
  group_by(WL, Strain, Par_ue, Photoperiod, E_days, O2) %>%
  mutate(PURNormSum = sum(PURNorm)) %>% 
  mutate(SumEmNormJaz = sum(EmNormJaz469)) %>% 
  mutate(PUR = Par_ue*(PURNormSum/SumEmNormJaz)) %>% 
  ungroup() 

OLISSpectraMetaPUR530 <- OLISSpectraMeta %>%
  filter(WL==530) %>% 
  mutate(PURNorm = (AbsNorm440*EmNormJaz521)) %>% 
  group_by(WL, Strain, Par_ue, Photoperiod, E_days, O2) %>%
  mutate(PURNormSum = sum(PURNorm)) %>% 
  mutate(SumEmNormJaz = sum(EmNormJaz521)) %>% 
  mutate(PUR = Par_ue*(PURNormSum/SumEmNormJaz)) %>% 
  ungroup() 

OLISSpectraMetaPUR620 <- OLISSpectraMeta %>%
  filter(WL==620) %>% 
  mutate(PURNorm = (AbsNorm440*EmNormJaz612)) %>% 
  group_by(WL, Strain, Par_ue, Photoperiod, E_days, O2) %>%
  mutate(PURNormSum = sum(PURNorm)) %>% 
  mutate(SumEmNormJaz = sum(EmNormJaz612)) %>% 
  mutate(PUR = Par_ue*(PURNormSum/SumEmNormJaz)) %>% 
  ungroup() 

OLISSpectraMetaPUR660 <- OLISSpectraMeta %>%
  filter(WL==660) %>% 
  mutate(PURNorm = (AbsNorm440*EmNormJaz647)) %>% 
  group_by(WL, Strain, Par_ue, Photoperiod, E_days, O2) %>%
  mutate(PURNormSum = sum(PURNorm)) %>% 
  mutate(SumEmNormJaz = sum(EmNormJaz647)) %>% 
  mutate(PUR = Par_ue*(PURNormSum/SumEmNormJaz)) %>% 
  ungroup() 

OLISSpectraMetaPUR730 <- OLISSpectraMeta %>%
  filter(WL==730) %>% 
  mutate(PURNorm = (AbsNorm440*EmNormJaz722)) %>% 
  group_by(WL, Strain, Par_ue, Photoperiod, E_days, O2) %>%
  mutate(PURNormSum = sum(PURNorm)) %>% 
  mutate(SumEmNormJaz = sum(EmNormJaz722)) %>% 
  mutate(PUR = Par_ue*(PURNormSum/SumEmNormJaz)) %>% 
  ungroup() 

OLISSpectraMetaPURWW <- OLISSpectraMeta %>%
  filter(WL=="WW") %>% 
  mutate(PURNorm = (AbsNorm440*EmNormJaz600)) %>% 
  group_by(WL, Strain, Par_ue, Photoperiod, E_days, O2) %>%
  mutate(PURNormSum = sum(PURNorm)) %>% 
  mutate(SumEmNormJaz = sum(EmNormJaz600)) %>% 
  mutate(PUR = Par_ue*(PURNormSum/SumEmNormJaz)) %>% 
  ungroup() 

OLISSpectraMetaPUR<-rbind(OLISSpectraMetaPUR405, OLISSpectraMetaPUR450, OLISSpectraMetaPUR470, OLISSpectraMetaPUR530, OLISSpectraMetaPUR620, OLISSpectraMetaPUR660, OLISSpectraMetaPUR730, OLISSpectraMetaPURWW)

rm(OLISSpectraMetaPUR405, OLISSpectraMetaPUR450, OLISSpectraMetaPUR470, OLISSpectraMetaPUR530, OLISSpectraMetaPUR620, OLISSpectraMetaPUR660, OLISSpectraMetaPUR730, OLISSpectraMetaPURWW)
```

# Filter unrevelant data

```{r filter unrevelant data}
OLISSpectraMetaPUR<-OLISSpectraMetaPUR %>% 
  filter(PUR>=0) %>% 
  filter(PUR<=180)
```

# Calculate daily PUR photon dose

```{r calculate PUR Photon dose}
OLISSpectraMetaPUR <- OLISSpectraMetaPUR %>%
  mutate(PURPhotonDose_day =(PUR/2)*Photoperiod*3600)

```


```{r Changes strain names}
OLISSpectraMetaPUR <- OLISSpectraMetaPUR %>%
      mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA77G"~"PC-rich_077"))
```

```{r}
OLISSpectraMetaPUR<-OLISSpectraMetaPUR %>% 
    filter(WL!="WW") 
```


# Create plot

```{r Create plot}

OLISSpectraMetaPUR %>%
  #filter(Par_ue!=30) %>% 
  # filter(E_days == 4 | E_days == 7 | E_days == 6) %>% 
  ggplot() +
  geom_area(aes(x = nm, y = EmNormJaz722, fill = "gray84"), alpha = 0.6, show.legend = F) +
  #geom_area(aes(x = nm, y = EmNormJaz600, fill = "gray84"), alpha = 0.6, show.legend = F) +
  geom_area(aes(x = nm, y = EmNormJaz647, fill = "gray84"), alpha = 0.6, show.legend = F) +
  geom_area(aes(x = nm, y = EmNormJaz612, fill = "gray84"), alpha = 0.6, show.legend = F) +
  geom_area(aes(x = nm, y = EmNormJaz521, fill = "gray84"), alpha = 0.6, show.legend = F) +
  geom_area(aes(x = nm, y = EmNormJaz469, fill = "gray84"), alpha = 0.6, show.legend = F) +
  geom_area(aes(x = nm, y = EmNormJaz441, fill = "gray84"), alpha = 0.6, show.legend = F) +
  geom_area(aes(x = nm, y = EmNormJaz393, fill = "gray84"), alpha = 0.6, show.legend = F) +
  
  # geom_area(aes(x = nm, y = PURNorm, fill = "gray20"), alpha = 0.5, show.legend = F) +
  # geom_area(aes(x = nm, y = PURNormBA77G, fill = "palegreen3"), alpha = 0.5, show.legend = F) +
  geom_line(aes(x = nm, y = AbsNorm440, colour = as.factor(Strain)), show.legend = T, size = 0.4) +

  scale_color_manual(values = c("PC-rich_077" ="palegreen3", "PE-rich_127" ="brown4")) +
  # scale_linetype_manual(values = c("PC-rich_077" ="solid", "PE-rich_127" ="longdash")) +
  stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = -0.025, alpha = 0.5) +
  scale_fill_identity() +
  labs(y = "Normalized absorbance", x = "Wavelength (nm)") +
  scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  coord_cartesian(ylim = c (-0.01, 1.6)) +
  ggh4x::facet_nested(cols = vars(WL),   rows = vars(factor(O2, levels=c("21","0"))),labeller = labeller(Ex_WL = label_value, WL = label_value)) +
  theme_bw() 
```



```{r Create plot}

OLISSpectraMetaPUR %>%
  filter(E_days == 7 | E_days == 8) %>% 
  # filter(E_days == 4 | E_days == 7 | E_days == 6) %>% 
  ggplot() +
  geom_area(aes(x = nm, y = EmNormJaz722, fill = "gray84"), alpha = 0.6, show.legend = F) +
  #geom_area(aes(x = nm, y = EmNormJaz600, fill = "gray84"), alpha = 0.6, show.legend = F) +
  geom_area(aes(x = nm, y = EmNormJaz647, fill = "gray84"), alpha = 0.6, show.legend = F) +
  geom_area(aes(x = nm, y = EmNormJaz612, fill = "gray84"), alpha = 0.6, show.legend = F) +
  geom_area(aes(x = nm, y = EmNormJaz521, fill = "gray84"), alpha = 0.6, show.legend = F) +
  geom_area(aes(x = nm, y = EmNormJaz469, fill = "gray84"), alpha = 0.6, show.legend = F) +
  geom_area(aes(x = nm, y = EmNormJaz441, fill = "gray84"), alpha = 0.6, show.legend = F) +
  geom_area(aes(x = nm, y = EmNormJaz393, fill = "gray84"), alpha = 0.6, show.legend = F) +
  
  # geom_area(aes(x = nm, y = PURNorm, fill = "gray20"), alpha = 0.5, show.legend = F) +
  # geom_area(aes(x = nm, y = PURNormBA77G, fill = "palegreen3"), alpha = 0.5, show.legend = F) +
  geom_line(aes(x = nm, y = AbsNorm440, colour = as.factor(Strain)), show.legend = T, size = 0.4) +

  scale_color_manual(values = c("PC-rich_077" ="palegreen3", "PE-rich_127" ="brown4")) +
  # scale_linetype_manual(values = c("PC-rich_077" ="solid", "PE-rich_127" ="longdash")) +
  stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = -0.025, alpha = 0.5) +
  scale_fill_identity() +
  labs(y = "Normalized absorbance", x = "Wavelength (nm)") +
  scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  coord_cartesian(ylim = c (-0.01, 1.6)) +
  ggh4x::facet_nested(cols = vars(WL),   rows = vars(factor(O2, levels=c("21","0"))),labeller = labeller(Ex_WL = label_value, WL = label_value)) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        panel.spacing.x = unit(0.4, 'cm'),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.title = element_blank(),
        legend.direction="horizontal",
        legend.position = c(0.08,0.97),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text.align = 0,
        legend.key.width= unit(0.3, 'cm'),
        legend.text = element_text(size=10))
```

# Save plot 

```{r save plot}
ggsave(file = file.path(FigPath, paste("Fig_OlisSpectra",".png",sep = "")), height=5, width= 8,  dpi = 300, limitsize = TRUE)
```





---------------------------------------------------------------------------------------------------------



# Create plot

```{r Create plot, fig.height = 10, fig.width = 8}
# Par_ue.labs <- c("30 µE", "90 µE", "180 µE", "Phase of growth", "900 µE")
# names(Par_ue.labs) <- c("30", "90", "180", "300", "900")
# 
# Photoperiod.labs <- c("8 h", "Photoperiod: 12 h", "16 h", "24 h")
# names(Photoperiod.labs) <- c("8", "12", "16", "24")
# 
# E_days.labs <- c("Exponential", "Pre-stationary")
# names(E_days.labs) <- c("3", "7")
# 
# Strain.labs <- c("PC-rich", "PE-rich")
# names(Strain.labs) <- c("PC-rich_077", "PE-rich_127")
# 
# O2.labs <- c("Strain")
# names(O2.labs) <- c(21)
# 
# data_textPUR0 <- data.frame(Par_ue = c(300, 300), E_days = c(3, 7), Strain  = c("PE-rich_127", "PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('PAR = 300 µE', 'PAR = 300 µE'))
# data_textPUR00 <- data.frame(Par_ue = c(300, 300), E_days = c(3, 7), Strain  = c("PC-rich_077", "PC-rich_077"), Photoperiod = c(12), O2 = c(21), label = c('PAR = 300 µE', 'PAR = 300 µE'))
# data_textPUR1 <- data.frame(Par_ue = c(300, 300), E_days = c(3, 7), Strain  = c("PE-rich_127", "PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('PUR = 176 µE', 'PUR = 129 µE'))
# data_textPUR2 <- data.frame(Par_ue = c(300, 300), E_days = c(3, 7), Strain  = c("PC-rich_077", "PC-rich_077"), Photoperiod = c(12), O2 = c(21), label = c('PUR = 139 µE', 'PUR = 128 µE'))
# 
# data_textpigment1 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PC-rich_077"), Photoperiod = c(12), O2 = c(21), label = c('Chl a 440 nm'))
# data_textpigment3 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PC-rich_077"), Photoperiod = c(12), O2 = c(21), label = c('Chl a 680 nm'))
# data_textpigment4 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PC-rich_077"), Photoperiod = c(12), O2 = c(21), label = c('PC 620 nm'))
# data_textpigment5 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PC-rich_077"), Photoperiod = c(12), O2 = c(21), label = c('Car 480 nm'))
# data_textpigment6 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PC-rich_077"), Photoperiod = c(12), O2 = c(21), label = c('PUB 500 nm'))
# 
# arrowdf1 <- tibble(Strain = "PC-rich_077", E_days = 3, Par_ue = 300, O2 = c(21))
# arrowdf3 <- tibble(Strain = "PC-rich_077", E_days = 3, Par_ue = 300, O2 = c(21))
# arrowdf4 <- tibble(Strain = "PC-rich_077", E_days = 3, Par_ue = 300, O2 = c(21))
# arrowdf5 <- tibble(Strain = "PC-rich_077", E_days = 3, Par_ue = 300, O2 = c(21))
# arrowdf6 <- tibble(Strain = "PC-rich_077", E_days = 3, Par_ue = 300, O2 = c(21))
# 
# data_textpigment7 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('Chl a 440 nm'))
# data_textpigment8 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('Car 480 nm'))
# data_textpigment9 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('PE 570 nm'))
# data_textpigment10 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('Chl a 680 nm'))
# data_textpigment11 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('PC 620 nm'))
# data_textpigment12 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('PUB 500 nm'))
# 
# arrowdf7 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300, O2 = c(21))
# arrowdf8 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300, O2 = c(21))
# arrowdf9 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300, O2 = c(21))
# arrowdf10 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300, O2 = c(21))
# arrowdf11 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300, O2 = c(21))
# arrowdf12 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300, O2 = c(21))
# 
# OLISSpectraMetaPURShort %>%
#   filter(Photoperiod == "12") %>%
#   filter(Strain == "PC-rich_077" | Strain == "PE-rich_127") %>%
#   filter(Par_ue == 300) %>%
#   filter(E_days == "3" | E_days == "7") %>%
#   ggplot() +
# 
#   geom_area(aes(x = nm, y = EmNormJaz439, fill = "gray84"), alpha = 0.6, show.legend = F) +
#   geom_area(aes(x = nm, y = PURNormBA127R, fill = "brown4"), alpha = 0.5, show.legend = F) +
#   geom_area(aes(x = nm, y = PURNormBA77G, fill = "palegreen3"), alpha = 0.5, show.legend = F) +
#   geom_line(aes(x = nm, y = AbsNorm440, colour = as.factor(Strain), linetype = as.factor(Strain)), show.legend = F, linewidth = 0.4) +
# 
#   geom_text(data=data_textPUR0, aes(x=450, y=1.26, label=label), size=3.7) +
#   geom_text(data=data_textPUR00, aes(x=450, y=1.26, label=label), size=3.7) +
#   geom_text(data=data_textPUR1, aes(x=450, y=1.21, label=label), size=3.7) +
#   geom_text(data=data_textPUR2, aes(x=450, y=1.21, label=label), size=3.7) +
# 
#   geom_text(data=data_textpigment1, aes(x=500, y=1.1, label=label), size=4, colour = "darkgreen") + #chla440
#   geom_text(data=data_textpigment5, aes(x=500, y=0.8, label=label), size=4, colour = "orange") + #Car
#   geom_text(data=data_textpigment3, aes(x=650, y=1.2, label=label), size=4, colour = "darkgreen") +#chla680
#   geom_text(data=data_textpigment4, aes(x=590, y=0.95, label=label), size=4, colour = "deepskyblue4") + #PC
#   geom_text(data=data_textpigment6, aes(x=485, y=0.25, label=label), size=4, colour = "sienna4") + #PUB
#   geom_segment(data = arrowdf1,
#                aes(x = 480, xend = 445, y = 1.05, yend = 1),
#                colour = "darkgreen", size = 0.5, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #chla440
#   geom_segment(data = arrowdf5,
#                aes(x = 480, xend = 475, y = 0.75, yend = 0.54),
#                colour = "orange", size = 0.5, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #Car
#   geom_segment(data = arrowdf3,
#                aes(x = 660, xend = 680, y = 1.14, yend = 0.95),
#                colour = "darkgreen", size = 0.5, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #chla680
#   geom_segment(data = arrowdf4,
#                aes(x = 610, xend = 630, y = 0.90, yend = 0.82),
#                colour = "deepskyblue4", size = 0.5, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PC
#   geom_segment(data = arrowdf4,
#                aes(x = 480, xend = 494, y = 0.30, yend = 0.41),
#                colour = "sienna4", size = 0.5, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PUB
#   geom_text(data=data_textpigment7, aes(x=500, y=1.1, label=label), size=4, colour = "darkgreen") + #chla440
#   geom_text(data=data_textpigment8, aes(x=500, y=0.8, label=label), size=4, colour = "orange") + #Car
#   geom_text(data=data_textpigment9, aes(x=580, y=1.0, label=label), size=4, colour = "darkmagenta") + #PE
#   geom_text(data=data_textpigment10, aes(x=650, y=1.2, label=label), size=4, colour = "darkgreen") +#chla680
#   geom_text(data=data_textpigment11, aes(x=600, y=0.17, label=label), size=4, colour = "deepskyblue4") + #PC
#   geom_text(data=data_textpigment12, aes(x=495, y=0.30, label=label), size=4, colour = "sienna4") + #PUB
#   geom_segment(data = arrowdf7,
#                aes(x = 480, xend = 445, y = 1.05, yend = 1),
#                colour = "darkgreen", size = 0.5, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #chla440
#   geom_segment(data = arrowdf8,
#                aes(x = 480, xend = 475, y = 0.75, yend = 0.55),
#                colour = "orange", size = 0.5, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #Car
#   geom_segment(data = arrowdf9,
#                aes(x = 590, xend = 575, y = 0.95, yend = 0.85),
#                colour = "darkmagenta", size = 0.5, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PE
#   geom_segment(data = arrowdf10,
#                aes(x = 660, xend = 680, y = 1.14, yend = 0.85),
#                colour = "darkgreen", size = 0.5, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #chla680
#   geom_segment(data = arrowdf11,
#                aes(x = 610, xend = 630, y = 0.2, yend = 0.3),
#                colour = "deepskyblue4", size = 0.5, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PC
#   geom_segment(data = arrowdf12,
#                aes(x = 490, xend = 500, y = 0.35, yend = 0.52),
#                colour = "sienna4", size = 0.5, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PUB
#   scale_color_manual(values = c("PC-rich_077" ="palegreen3", "PE-rich_127" ="brown4")) +
#   scale_linetype_manual(values = c("PC-rich_077" ="solid", "PE-rich_127" ="longdash")) +
#   stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = -0.025, alpha = 0.5) +
#   scale_fill_identity() +
#   labs(y = "Normalized whole-cell absorbance, lamp emission, and PUR", x = "Wavelength (nm)") +
#   scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
#   coord_cartesian(ylim = c (-0.01, 1.25)) +
#   ggh4x::facet_nested(cols = vars(Par_ue, E_days), rows = vars(O2, Strain),labeller = labeller(Ex_WL = label_both, WL = label_both, E_days = E_days.labs, Photoperiod = Photoperiod.labs, Par_ue = Par_ue.labs, Strain = Strain.labs, O2 = O2.labs, )) +
#   theme_bw() +
#   theme(panel.grid.minor = element_blank(),
#         panel.grid.major = element_blank(),
#         panel.spacing.x = unit(0.4, 'cm'),
#         axis.text = element_text(size=12),
#         axis.text.x = element_text(size=12),
#         axis.title = element_text(size=16),
#         strip.background = element_rect(fill="white"),
#         strip.text = element_text(size=12),
#         axis.title.y = element_text(margin=margin(r=10)),
#         axis.title.x = element_text(margin=margin(t=10)),
#         legend.background = element_rect(fill="transparent"),
#         legend.title = element_blank(),
#         legend.direction="horizontal",
#         legend.position = c(0.08,0.97),
#         legend.spacing.x = unit(0.01, 'cm'),
#         legend.text.align = 0,
#         legend.key.width= unit(0.3, 'cm'),
#         legend.text = element_text(size=10))
```

# Save plot 

```{r save plot}
# ggsave(file = file.path(FigPath, paste("Fig_OlisSpectra",".png",sep = "")), height=9, width= 9,  dpi = 300, limitsize = TRUE)
```

```{r Create plot, fig.height = 6, fig.width = 8}

# Par_ue.labs <- c("30 µE", "90 µE", "180 µE", "Phase of growth", "900 µE")
# names(Par_ue.labs) <- c("30", "90", "180", "300", "900")
# 
# Photoperiod.labs <- c("8 h", "Photoperiod: 12 h", "16 h", "24 h")
# names(Photoperiod.labs) <- c("8", "12", "16", "24")
# 
# E_days.labs <- c("Exponential", "Pre-stationary")
# names(E_days.labs) <- c("3", "7")
# 
# Strain.labs <- c("PE-rich_127", "PC-rich_077")
# names(Strain.labs) <- c("PE-rich_127", "PC-rich_077")
# 
# data_textPUR0 <- data.frame(Par_ue = c(300, 300), E_days = c(3, 7), Strain  = c("PE-rich_127", "PE-rich_127"), Photoperiod = c(12), label = c('PAR = 300 µE', 'PAR = 300 µE'))
# 
# data_textPUR1 <- data.frame(Par_ue = c(300, 300), E_days = c(3, 7), Strain  = c("PE-rich_127", "PE-rich_127"), Photoperiod = c(12), label = c('PUR (PE-rich) = 176 µE', 'PUR (PE-rich) = 129 µE'))
# 
# data_textPUR2 <- data.frame(Par_ue = c(300, 300), E_days = c(3, 7), Strain  = c("PE-rich_127", "PE-rich_127"), Photoperiod = c(12), label = c('PUR (PC-rich) = 139 µE', 'PUR (PC-rich) = 128 µE'))
# 
# data_textpigment1 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), label = c('Chl a 440 nm'))
# data_textpigment2 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), label = c('PE 570 nm'))
# data_textpigment3 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), label = c('Chl a 680 nm'))
# data_textpigment4 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), label = c('PC 620 nm'))
# data_textpigment5 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), label = c('Car 480 nm'))
# data_textpigment6 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), label = c('PUB 500 nm'))
# 
# arrowdf1 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300)
# arrowdf2 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300)
# arrowdf3 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300)
# arrowdf4 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300)
# arrowdf5 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300)
# arrowdf6 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300)
# 
# 
# OLISSpectraMetaPURShort %>%
#   filter(Photoperiod == "12") %>%
#   filter(Strain == "PE-rich_127" | Strain == "PC-rich_077") %>%
#   filter(Par_ue == 300) %>%
#   filter(E_days == "3" | E_days == "7") %>%
#   ggplot() +
#   geom_area(aes(x = nm, y = EmNormJaz439, fill = "gray84"), alpha = 0.6, show.legend = F) +
#   geom_area(aes(x = nm, y = PURNormBA127R, fill = "brown4"), alpha = 0.5, show.legend = F) +
#   geom_area(aes(x = nm, y = PURNormBA77G, fill = "palegreen3"), alpha = 0.5, show.legend = F) +
#   geom_line(aes(x = nm, y = AbsNorm440, colour = as.factor(Strain), linetype = as.factor(Strain)), show.legend = F, linewidth = 0.5) +
# 
#   geom_text(data=data_textPUR0, aes(x=437, y=1.26, label=label), size=3.5) +
#   geom_text(data=data_textPUR1, aes(x=465, y=1.21, label=label), size=3.5) +
#   geom_text(data=data_textPUR2, aes(x=465, y=1.16, label=label), size=3.5) +
# 
#   geom_text(data=data_textpigment1, aes(x=450, y=1.07, label=label), size=4, colour = "darkgreen") + #chla440
#   geom_text(data=data_textpigment5, aes(x=430, y=0.36, label=label), size=4, colour = "coral3") + #Car
#   geom_text(data=data_textpigment2, aes(x=520, y=0.92, label=label), size=4, colour = "darkmagenta") + #PE
#   geom_text(data=data_textpigment3, aes(x=660, y=1.08, label=label), size=4, colour = "darkgreen") +#chla680
#   geom_text(data=data_textpigment4, aes(x=605, y=1.0, label=label), size=4, colour = "deepskyblue4") + #PC
#   geom_text(data=data_textpigment6, aes(x=485, y=0.08, label=label), size=4, colour = "sienna4") + #PUB
# 
#   geom_segment(data = arrowdf1,
#                aes(x = 470, xend = 440, y = 1.04, yend = 1.02),
#                colour = "darkgreen", size = 0.7, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #chla440
#   geom_segment(data = arrowdf5,
#                aes(x = 450, xend = 470, y = 0.4, yend = 0.5),
#                colour = "coral3", size = 0.7, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #Car
#   geom_segment(data = arrowdf2,
#                aes(x = 538, xend = 568, y = 0.88, yend = 0.86),
#                colour = "darkmagenta", size = 0.7, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PE
#   geom_segment(data = arrowdf3,
#                aes(x = 697, xend = 680, y = 1.05, yend = 0.92),
#                colour = "darkgreen", size = 0.7, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #chla680
#   geom_segment(data = arrowdf4,
#                aes(x = 632, xend = 630, y = 0.95, yend = 0.82),
#                colour = "deepskyblue4", size = 0.7, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PC
#   geom_segment(data = arrowdf4,
#                aes(x = 465, xend = 500, y = 0.12, yend = 0.52),
#                colour = "sienna4", size = 0.7, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PUB
#   scale_color_manual(values = c("PE-rich_127" ="brown4", "PC-rich_077" ="palegreen3")) +
#   scale_linetype_manual(values = c("PE-rich_127" ="longdash", "PC-rich_077" ="solid")) +
#   stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = -0.025, alpha = 0.5) + 
#   scale_fill_identity() +
#   labs(y = "Normalized whole-cell absorbance, lamp emission, and PUR", x = "Wavelength (nm)") +
#   scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
#   coord_cartesian(ylim = c (-0.01, 1.25)) +
#   ggh4x::facet_nested(cols = vars(Par_ue, E_days), labeller = labeller(Ex_WL = label_both, WL = label_both, E_days = E_days.labs, Photoperiod = Photoperiod.labs, Par_ue = Par_ue.labs, Strain = Strain.labs)) +
#   theme_bw() +
#   theme(panel.grid.minor = element_blank(),
#         panel.grid.major = element_blank(),
#         panel.spacing.x = unit(0.4, 'cm'),
#         axis.text = element_text(size=12),
#         axis.text.x = element_text(size=12),
#         axis.title = element_text(size=16),
#         strip.background = element_rect(fill="white"),
#         strip.text = element_text(size=12),
#         axis.title.y = element_text(margin=margin(r=10)),
#         axis.title.x = element_text(margin=margin(t=10)),
#         legend.background = element_rect(fill="transparent"),
#         legend.title = element_blank(),
#         legend.direction="horizontal",
#         legend.position = c(0.08,0.97),
#         legend.spacing.x = unit(0.01, 'cm'),
#         legend.text.align = 0,
#         legend.key.width= unit(0.3, 'cm'),
#         legend.text = element_text(size=10))
```

```{r save plot}
#ggsave(file = file.path(FigPath, paste("Fig_OlisSpectra2",".png",sep = "")), height=6, width= 8,  dpi = 300, limitsize = TRUE)
```

------------------------------------------ new idea for merging plot together with PUR/PAR ratio

# Preparing df for creating representative plot

```{r preparing selected data for creating representative plot}
# OLISSpectraMetaPURSS<-OLISSpectraMetaPUR %>% 
#   select(-c(ExpDate, Run, Tube, MC, LightShape, ExpEndDate, FilenameOlis, FilenameJaz, ObsDate)) %>% 
#   filter(PARPhotonDose_day == 432000 | PARPhotonDose_day == 17280000) 
#     
# OLISExp056<- OLISSpectraMetaPURSS %>%
#   filter(Strain == "BA56G")  %>% 
#   filter(E_days ==3)
# OLISExp056$Phase <-"Exponential"
# OLISExp056$Photon <-"Low"
# 
# OLISSt056<- OLISSpectraMetaPURSS %>%
#   filter(Strain == "BA56G")  %>% 
#   filter(E_days ==5 | E_days == 12)
# OLISSt056$Phase <-"Pre-stationary"
# OLISSt056$Photon <-"High"
# 
# OLIS056<-rbind(OLISExp056, OLISSt056)  
#     #mutate(PURNormBA56G = PURNorm)
# 
# 
# OLISExp077<- OLISSpectraMetaPURSS %>%
#   filter(Strain == "BA77G")  %>% 
#   filter(E_days ==3)
# OLISExp077$Phase <-"Exponential"
# OLISExp077$Photon <-"Low"
# 
# OLISSt077<- OLISSpectraMetaPURSS %>%
#   filter(Strain == "BA77G")  %>% 
#   filter(E_days ==5 | E_days == 12)
# OLISSt077$Phase <-"Pre-stationary"
# OLISSt077$Photon <-"High"
# 
# OLIS077<-rbind(OLISExp077, OLISSt077) 
#   #mutate(PURNormBA77G = PURNorm)
# 
# 
# OLISExp048<- OLISSpectraMetaPURSS %>%
#   filter(Strain == "BA48R")  %>% 
#   filter(E_days ==4)
# OLISExp048$Phase <-"Exponential"
# OLISExp048$Photon <-"Low"
# 
# OLISSt048<- OLISSpectraMetaPURSS %>%
#   filter(Strain == "BA48R")  %>% 
#   filter(E_days ==5 | E_days == 14)
# OLISSt048$Phase <-"Pre-stationary"
# OLISSt048$Photon <-"High"
# 
# OLIS048<-rbind(OLISExp048, OLISSt048)  
#     #mutate(PURNormBA48R = PURNorm)
# 
# 
# OLISExp127<- OLISSpectraMetaPURSS %>%
#   filter(Strain == "BA127R")  %>% 
#   filter(E_days ==4)
# OLISExp127$Phase <-"Exponential"
# OLISExp127$Photon <-"Low"
# 
# OLISSt127<- OLISSpectraMetaPURSS %>%
#   filter(Strain == "BA127R")  %>% 
#   filter(E_days ==5 | E_days == 14)
# OLISSt127$Phase <-"Pre-stationary"
# OLISSt127$Photon <-"High"
# 
# OLIS127<-rbind(OLISExp127, OLISSt127) 
#     #mutate(PURNormBA127R = PURNorm)
# 
# 
# OLIS<-rbind(OLIS056, OLIS077, OLIS048, OLIS127) 


```

```{r Changes strain names}
# OLISSpectraMetaPURShort <- OLIS %>%
#     mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
#          Strain=="BA48R"~"PE-rich_048",
#         Strain=="BA56G"~"PC-rich_056",
#          Strain=="BA77G"~"PC-rich_077")) %>% 
#     mutate(Phase2=case_when(Par_ue==30~"Exponential",
#          Par_ue==600~"Pre-stationary"))
# OLISSpectraMetaPURShort$facetsPhase<-"Phase~of~growth"
# OLISSpectraMetaPURShort$facetsStrain<-"Strain"
# 
# OLISSpectraMetaPURShort56<-OLISSpectraMetaPURShort %>% 
#   filter(Strain=="PC-rich_056") %>% 
#   filter(Photon=="Low") %>% 
#   mutate(PURNorm56 = PURNorm) %>% 
#   mutate(Phase2=case_when(Par_ue==30~"Exponential",
#          Par_ue==600~"Pre-stationary"))
# OLISSpectraMetaPURShort56$facetsPhase<-"Phase~of~growth"
# OLISSpectraMetaPURShort56$facetsStrain<-"Strain"
# 
# OLISSpectraMetaPURShort77<-OLISSpectraMetaPURShort %>% 
#   filter(Strain=="PC-rich_077") %>% 
#   filter(Photon=="Low") %>% 
#   mutate(PURNorm77 = PURNorm) %>% 
#   mutate(Phase2=case_when(Par_ue==30~"Exponential",
#          Par_ue==600~"Pre-stationary"))
# OLISSpectraMetaPURShort77$facetsPhase<-"Phase~of~growth"
# OLISSpectraMetaPURShort77$facetsStrain<-"Strain"
# 
# OLISSpectraMetaPURShort48<-OLISSpectraMetaPURShort %>% 
#   filter(Strain=="PE-rich_048") %>% 
#   filter(Photon=="Low") %>% 
#   mutate(PURNorm48 = PURNorm) %>% 
#   mutate(Phase2=case_when(Par_ue==30~"Exponential",
#          Par_ue==600~"Pre-stationary"))
# OLISSpectraMetaPURShort48$facetsPhase<-"Phase~of~growth"
# OLISSpectraMetaPURShort48$facetsStrain<-"Strain"
# 
# OLISSpectraMetaPURShort127<-OLISSpectraMetaPURShort %>% 
#   filter(Strain=="PE-rich_127") %>% 
#   filter(Photon=="Low") %>% 
#   mutate(PURNorm127 = PURNorm) %>% 
#   mutate(Phase2=case_when(Par_ue==30~"Exponential",
#          Par_ue==600~"Pre-stationary"))
# OLISSpectraMetaPURShort127$facetsPhase<-"Phase~of~growth"
# OLISSpectraMetaPURShort127$facetsStrain<-"Strain"
```





# Create plot

```{r Create plot, fig.height = 8, fig.width = 8, warning = FALSE}
# data_textB <- data.frame(facetsPhase = c("Phase~of~growth"), Phase2 = c("Exponential"), facetsStrain  = c("Strain"), Strain  = c("PC-rich_056"), label = c('B'))
# 
# # k_data056 = data.frame(WL = c("WW", "WW"), Phase = c("Pre-stationary"), O2=c(21, 21, 21, 21), Strain  = c("PC-rich_056"))
# # k_data077 = data.frame(WL = c("WW", "WW"), Phase = c("Pre-stationary"), O2=c(21, 21, 21, 21), Strain  = c("PC-rich_077"))
# # k_data048 = data.frame(WL = c("WW", "WW"), Phase = c("Pre-stationary"), O2=c(21, 21, 21, 21), Strain  = c("PE-rich_048"))
# # k_data127 = data.frame(WL = c("WW", "WW"), Phase = c("Pre-stationary"), O2=c(21, 21, 21, 21), Strain  = c("PE-rich_127"))
# 
# 
# Spectra<-OLISSpectraMetaPURShort %>%
#     filter(Photon=="Low") %>% 
#   ggplot() +
#   geom_area(aes(x = nm, y = EmNormJaz439, fill = "gray84"), alpha = 0.6, show.legend = F) +
#   geom_area(aes(x = nm, y = PURNorm56, fill = "seagreen4"), alpha = 0.5, show.legend = F, OLISSpectraMetaPURShort56) +
#   geom_area(aes(x = nm, y = PURNorm77, fill = "palegreen3"), alpha = 0.5, show.legend = F, OLISSpectraMetaPURShort77) +
#   geom_area(aes(x = nm, y = PURNorm48, fill = "brown1"), alpha = 0.5, show.legend = F, OLISSpectraMetaPURShort48) +
#   geom_area(aes(x = nm, y = PURNorm127, fill = "brown4"), alpha = 0.5, show.legend = F, OLISSpectraMetaPURShort127) +
#   
#   geom_line(aes(x = nm, y = AbsNorm440, colour = as.factor(Strain)), show.legend = F, linewidth = 0.4) +
#   
#   geom_text(data=data_textB, aes(x=410, y=1.5, label=label), size=6) +
#   
#   # geom_segment(data = k_data056, aes(x =9e07, y = -Inf, xend = 9e07, yend = Inf), color = "seagreen4", size = 6, alpha = 0.3) +
#   # geom_segment(data = k_data077, aes(x =9e07, y = -Inf, xend = 9e07, yend = Inf), color = "palegreen3", size = 6, alpha = 0.3) +
#   # geom_segment(data = k_data048, aes(x =9e07, y = -Inf, xend = 9e07, yend = Inf), color = "brown1", size = 6, alpha = 0.3) +
#   # geom_segment(data = k_data127, aes(x =9e07, y = -Inf, xend = 9e07, yend = Inf), color = "brown4", size = 6, alpha = 0.3) +
#   
#   scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="") +
#   # scale_linetype_manual(values = c("PC-rich_077" ="solid", "PE-rich_127" ="longdash")) +
#   stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = -0.025, alpha = 0.5) +
#   scale_fill_identity() +
#   labs(y = "Normalized whole-cell absorbance, lamp emission, and PUR", x = "Wavelength (nm)") +
#   # scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
#   # coord_cartesian(ylim = c (-0.01, 1.25)) +
#   ggh4x::facet_nested(cols = vars(facetsPhase, Phase2), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
#     #ggh4x::facet_nested(cols = vars(Photon), rows = vars(Strain)) +
#   theme_bw() +
#   theme(panel.grid.minor = element_blank(),
#         panel.grid.major = element_blank(),
#         axis.text = element_text(size=12),
#         axis.text.x = element_text(vjust = -1), 
#         axis.title = element_text(size=16),
#         strip.background = element_rect(fill="white"),
#         strip.text = element_text(size=12),
#         axis.title.y = element_text(margin=margin(r=10)),
#         axis.title.x = element_text(margin=margin(t=10), vjust = -1),
#         legend.background = element_rect(fill="transparent"),
#         legend.position = c(0.85,0.88),
#         legend.key.height= unit(0.003, 'cm'),
#         legend.spacing.y = unit(-0.1, "cm"),
#         legend.spacing.x = unit(-0.1, 'cm'),
#         legend.title = element_blank(),
#         legend.text = element_text(size=11))
# Spectra
```


# Cleaning df before saving as Rds and removed unnecessary files from the environment

```{r delete unused df from the environment}
# rm(data_textpigment1,data_textpigment2,data_textpigment3,data_textpigment4,data_textpigment5,data_textpigment6, data_textpigment7, data_textpigment8, data_textpigment9, data_textpigment10, data_textpigment11, data_textpigment12, arrowdf1,arrowdf2,arrowdf3,arrowdf4,arrowdf5,arrowdf6, arrowdf7, arrowdf8, arrowdf9, arrowdf10, arrowdf11, arrowdf12, data_textPUR0, data_textPUR00, data_textPUR1,data_textPUR2, JazData, JazDataRoundMeta, OLISSpectraMetaPURShortBA127R, OLISSpectraMetaPURShortBA77G, OLISSpectraMeta, OLISSpectra)
```

# Preparing df for creating plot - added proper strain names and facet labels

```{r create tidy PAR photon dose and facets for plot}

# OLISSpectraMetaPUR$facetsPar_ue = factor(OLISSpectraMetaPUR$O2, labels = c("PAR~(µmol~photons~m^{-2}~s^{-1})"))
# OLISSpectraMetaPUR$facetsPhotoperiod = factor(OLISSpectraMetaPUR$WL, labels = c("Photoperiod~(h)"))
# OLISSpectraMetaPUR$facetsStrain = factor(OLISSpectraMetaPUR$WL, labels = c("Strain"))
# OLISSpectraMetaPUR$facetsPhase = factor(OLISSpectraMetaPUR$WL, labels = c("Phase~of~growth"))
```




# Create tidy df without all nm

```{r clean df, create smaller df - without absorbance and all nm}
#colnames(OLISSpectraMetaPUR)

OLISAllPURTidy<-OLISSpectraMetaPUR %>% 
  select(c(SampleID, Run, Strain, ExpDate, Par_ue, Photoperiod, Tube, O2, WL, LightShape, PARPhotonDose_day, PUR, PURPhotonDose_day, E_days)) %>% 
  unique() %>% 
  mutate(PURPARRatio = PUR/Par_ue) 

OLISAllPURTidy <- OLISAllPURTidy %>% 
  filter(PURPARRatio<=1) %>% 
  filter(PURPARRatio>0)
```

# Preparing df for creating plot

```{r create tidy PAR photon dose and facets for plot}
# OLISAllPURTidy <- OLISAllPURTidy %>%
#     mutate(PARPhotonDoseTidy=PARPhotonDose_day/100000) 
# 
# OLISAllPURTidy$facetsPARPhotonDose_day = factor(OLISAllPURTidy$WL, labels = c("PAR~photon~dose~(10^{5}~µmol~photons~m^{-2}~d^{-1})"))
```


# Create preliminary plot

```{r Create final PUR/PAR ratio plot}
lab1=c(expression("PC-rich_077"), expression("PE-rich_127"))


OLISAllPURTidy %>%
  ggplot() +
  geom_point(aes(x = E_days, y = PURPARRatio, colour = as.factor(Strain)), alpha = 0.9, size = 3, show.legend = F) +
  scale_colour_discrete(type=c("palegreen3", "brown4")) +
  labs(y = "PUR/PAR ratio", x = "Elapsed time (h)") +
  scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  coord_cartesian(ylim = c(0, 1.5)) +
  ggh4x::facet_nested(cols = vars(WL), rows = vars(factor(O2, levels=c("21","0"))), labeller = label_parsed) +
  theme_bw()

OLISAllPURTidy %>%
  filter(E_days == 7 | E_days == 8) %>% 
  ggplot() +
  geom_point(aes(x = E_days, y = PURPARRatio, colour = as.factor(Strain)), alpha = 0.9, size = 3, show.legend = F) +
  scale_colour_discrete(type=c("palegreen3", "brown4")) +
  labs(y = "PUR/PAR ratio", x = "Elapsed time (h)") +
  scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  coord_cartesian(ylim = c(0, 1.5)) +
  ggh4x::facet_nested(cols = vars(WL), rows = vars(factor(O2, levels=c("21","0"))), labeller = label_parsed) +
  theme_bw()
```
# Save plot 

```{r save plot}
#ggsave(file = file.path(FigPath, paste("Fig_PURPARRatio",".png",sep = "")), height=5, width= 8,  dpi = 300, limitsize = TRUE)
```


```{r Create final PUR/PAR ratio plot}
lab1=c(expression("PC-rich_077"), expression("PE-rich_127"))

OLISAllPURTidy %>%
  filter(E_days == 7 | E_days == 8) %>% 
  mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(WL != "WW") %>%
  ggplot() +
  
  geom_point(aes(x = WLNum, y = PURPARRatio, colour = as.factor(Strain)), size = 3, show.legend = T) +
  geom_line(aes(x = WLNum, y = PURPARRatio, colour = as.factor(Strain)), show.legend = F) +
  stat_wl_strip(aes(x = WLNum), ymin = -Inf, ymax = -0.025, alpha = 0.5) +
  scale_fill_identity() +
  
  #geom_point(aes(x = E_days, y = PURPARRatio, colour = as.factor(Strain)), alpha = 0.9, size = 3, show.legend = T) +

  scale_colour_discrete(type=c("palegreen3", "brown4")) +
  #labs(y = "PUR/PAR ratio", x = "Elapsed time (h)") +
  scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  coord_cartesian(ylim = c(0, 1.5)) +
    ggh4x::facet_nested(rows = vars(factor(O2, levels=c("21","0"))), labeller = label_parsed) +
 #ggh4x::facet_nested(cols = vars(Strain), rows = vars(factor(O2, levels=c("21","0"))), labeller = label_parsed) +
  #ggh4x::facet_nested(cols = vars(WL), rows = vars(factor(O2, levels=c("21","0"))), labeller = label_parsed) +

  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        panel.spacing.x = unit(0.4, 'cm'),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.title = element_blank(),
        legend.position = c(0.08,0.97),
        legend.text = element_text(size=10))
```

# Save plot 

```{r save plot}
ggsave(file = file.path(FigPath, paste("Fig_PURPARRatio2",".png",sep = "")), height=5, width= 8,  dpi = 300, limitsize = TRUE)
```



# Save Rds for further analysis

```{r save Rds}
saveRDS(OLISSpectraMetaPUR, file.path(DataOut, paste(Project, "Processed_OlisSpectraAll.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

saveRDS(OLISAllPURTidy, file.path(DataOut, paste(Project, "Processed_OlisSpectraTidy.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Variable names used in Data Dictionary

```{r}
colnames(OLISSpectraMetaPUR)
```

# Variable names used in Data Dictionary

```{r}
colnames(OLISAllPURTidy)
```

