---
title: "Process_SolisenseLRCData"
author:
- Sylwia Sliwinska-Wilczewska
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: BalticPhotoperiod.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

Process_SolisenseDataLRC.Rmd process BalticPhotoperiod_Imported_SolisenseLight_LRC.Rds from BalticPhotoperiod/Data/ImportedData/ImportedSolisenseData folder and stored in Data/ProcessedData/ProcessedSolisenseData folder as: BalticPhotoperiod_Processed_SolisenseJVPSII.Rds.

# Load Libraries

```{r load libraries, warning = FALSE, echo=FALSE} 
library(ggspectra)
library(photobiologyWavebands)
library(ggtext)
library(tidyverse)
library(broom)
library(OneR)
library(zoo)
library(ggpubr)
library(googledrive)
library(googlesheets4)
library(readxl)
library(Cairo) #for greek symbols
library(data.table)
library(minpack.lm) #Standard 'nls' framework that uses 'nls.lm' for fitting
library("patchwork") # merging plots
```

# Set Project Variables 

```{r set project variables, read zipped files, list available files, warning = FALSE, echo=FALSE}
Project <- "BalticO2"
DataOut <- file.path("..", "Data", "ImportedData", "ImportedSolisenseData")
DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedSolisenseData")

FigPath <- file.path("..", "Output", "Figures")
FigRdsPath <- file.path("..", "Output", "FiguresRds")
TableRdsPath <- file.path("..", "Output", "TablesRDS")
# FileID <- "fit"
# FileEncode <- "UTF-8"
# Delimiter <- ","
# HeaderRows <- 0
```

# Read MetaData

```{r read locally stored metadata from rds}
CultureCatalog <- readRDS(file = file.path("..", "Data", "ImportedData", "ImportedMetaData", "CultureCatalog.Rds"))

CultureCatalog<-CultureCatalog %>% 
  select(-c(PrimaryOperator, Temp_c, ExpCul, ExpStartTime, O2_Category, Optode, OptodeCh, OptodeMeasure))
```


# Read Imported Solisense

```{r read locally stored metadata from rds}
SolFitsMeta <- readRDS(file = file.path("..", "Data", "ImportedData", "ImportedSolisenseData", "BalticO2_Imported_SolisenseLight_LRC.Rds"))

SolFitsMeta <- SolFitsMeta |>
  select(-c(nm445,nm470,nm505,nm535,nm590,IR, nm445Corr,nm470Corr, nm505Corr,nm535Corr,nm590Corr,IRCorr,JVPSII_aLHIIOxbomax, JVPSII_ETRtauav_FoSig, JVPSII_ETRtauav_aLHII_Sig, JVPSII_ETRqpOxbo_aLHII_Sig)) |>
  rename(JVPSII_ETRqpOxbo_FoSigmax_m2psii = JVPSII_ETRqpOxbo_FoSig) |>
  rename(FilenameSolisense=Filename) %>% 
  mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA77G"~"PC-rich_077")) 
```

# Create preliminary plots 

```{r preliminary plot}
lab1=c(expression("PC-rich_077"), expression("PE-rich_127"))

SolFitsMeta %>%
  filter(Run!=118 & Run!= 119) %>% 
  filter(Par_ue!=30) %>% 
  mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(WL != "WW") %>%
  filter(ActPAR== 80) %>% 
  filter(E_days>=4) %>% 
  filter(E_days<=10) %>% 
  ggplot() +
  geom_point(aes(x = WLNum, y = JVPSII_ETRqpOxbo_FoSigmax_m2psii, colour = as.factor(Strain)), size = 3.5, show.legend = T) +
  scale_colour_discrete(type=c("palegreen3", "brown4"), name="", labels = lab1) +
  # stat_wl_strip(aes(x = WLNum), ymin = -Inf, ymax = -0.025, alpha = 0.5) +
  # scale_fill_identity() +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(factor(O2, levels=c("21","0"))), labeller = label_parsed) +
  theme_bw() 
```



To get the Platt fits to work I plotted:
JVPSII_umole_eLs vs. ActPAR

so I had to convert JVPSII_eLs by dividing by 6.022E-17.
If you want to go back to JVPSII_eLs just multiple back up.

# Calibrate JVPSII to e L-1 s-1

```{r JVPSII calib}
JVPSII_eLs_ModelTerms <- read_rds(file.path("..","Data", "CleanedData", "JVPSIIO2Calib", "JVPSII_eLs_ModelTerms.Rds"))

#smarter way to code this with 'which' in [] and map through Ex_WL
SolFitsMeta <- left_join(SolFitsMeta, JVPSII_eLs_ModelTerms, by = join_by(Ex_WL)) |>
  select(-c(Slope_P)) |>
  mutate(JVPSII_eLs = JVPSII_ETRqpOxbo_FoSigmax_m2psii/Slope) |>
  mutate(JVPSII_umol_eLs = JVPSII_eLs/6.022e17)

```

# Filter unrevelant data

```{r}
SolFitsMeta<-SolFitsMeta %>%
  filter(Par_ue!= 30) %>% 
    filter(E_days>=4) %>% 
    #filter(E_days<=10) %>% 
    filter(WL != "WW") %>%
    filter(Run!=118 & Run!= 119) 
```


# Create preliminary plots 

```{r preliminary plot}
# lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
# lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
# lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

SolFitsMeta %>%
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = JVPSII_umol_eLs, colour = as.factor(Strain)), size = 3.5, show.legend = T) +
  scale_colour_discrete(type=c("palegreen3", "brown4"), name="", labels = lab1) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(factor(O2, levels=c("21","0"))), labeller = label_parsed) +
  #facet_grid(cols = vars(Ex_WL), rows = vars(O2)) +
  theme_bw()

```
# Save plot 

```{r save plot}
#ggsave(file = file.path(FigPath, paste("Fig_JVPSII_ActPAR",".png",sep = "")), height=4, width= 6,  dpi = 300, limitsize = TRUE)
```

# Fit LRC for JVPSII to allow selection of specific JVPSII for different growth light levels.

```{r}
lrcplatt <- function(I, a, b, Pmax){Pmax * (1-exp(-a*I/Pmax)) * exp(-b*I/Pmax)}


SolFitsMetaLRC <- SolFitsMeta %>%
  nest(data = -c("SampleID", "Run", "Strain" ,"ExpDate","Par_ue", "Photoperiod", "O2", "WL", "MC", "Tube","Ex_WL","LightShape", "ExpEndDate", "PARPhotonDose_day", "ObsDate", "E_days")) %>% #head(50) %>% 
  mutate(lrcplatt_Model = map(data, possibly(~nlsLM(JVPSII_umol_eLs ~ lrcplatt(I = ActPARCorr, a, b, Pmax),
         data = .x,
         control = list(maxiter = 100),
         start = list(a = 0.1, b = 0.01, Pmax = 3), lower = c(0, 0, 0))))) %>%
  mutate(lrcplatt_Param = map(lrcplatt_Model, tidy),
         lrcplatt_Predict = map(lrcplatt_Model, possibly(augment)),
         lrcplatt_Glance = map(lrcplatt_Model, possibly(glance)))

```

# Create preliminary plot - Example

```{r prelim plot}
SolFitsMetaLRC %>%  
  unnest(lrcplatt_Predict) %>% 
  #filter(Strain == "BA127R") %>% 
ggplot() +
  geom_point(aes(ActPARCorr, JVPSII_umol_eLs, colour = as.factor(Strain)), alpha = 0.8, size = 3.5, show.legend = T, SolFitsMeta) +
  geom_line(aes(ActPARCorr, .fitted), colour = "black", linetype = "dotted") +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(O2, Strain, E_days), labeller = label_parsed) +
  theme_bw()

```

Use Peak Par_ue and 1/2 Peak Par_ue to estimate growth JVPSII for each combination
-use 'Pluck' to reach into lrcplatt_Predict to get a, b, Pmax; or
-unnest, pivot wider to get a, b, Pmax

```{r growth light JVPSII}

SolFitsMetaLRCGrowth <- SolFitsMetaLRC |>
  unnest(lrcplatt_Param) |>
  select(-c(statistic, p.value, lrcplatt_Predict, lrcplatt_Glance)) |> #remove (temporarily) to make pivot_wider easier
  pivot_wider(names_from = term, values_from = c(estimate, std.error)) |>
  mutate(JVPSII_umol_eLs_Par_ue = lrcplatt(I = Par_ue, a = estimate_a, estimate_b, estimate_Pmax),
         JVPSII_umol_eLs_HalfPar_ue = lrcplatt(I = (0.5*Par_ue), a = estimate_a, estimate_b, estimate_Pmax))

 
head(SolFitsMetaLRCGrowth) 
```

# Test plots of Growth Par_ue and 1/2 Growth Par_ue estimates for JVPSII
```{r growth JVPSII}
SolFitsMetaLRCGrowth |>
  ggplot() +
  geom_point(aes(x = E_days, y = JVPSII_umol_eLs_Par_ue, colour = Ex_WL)) +
  facet_grid(cols = vars(Ex_WL, Photoperiod, Strain), rows = vars(Par_ue)) +
  theme_bw()

SolFitsMetaLRCGrowth |>
  filter(Strain == "PE-rich_127") |>
  ggplot() +
  geom_point(aes(x = E_days, y = JVPSII_umol_eLs_Par_ue, colour = Ex_WL)) +
  facet_grid(cols = vars(Ex_WL, Photoperiod, Strain), rows = vars(Par_ue)) +
  theme_bw()

SolFitsMetaLRCGrowth |>
  filter(Strain == "PC-rich_077") |>
  ggplot() +
  geom_point(aes(x = E_days, y = JVPSII_umol_eLs_Par_ue, colour = Ex_WL)) +
  facet_grid(cols = vars(Ex_WL, Photoperiod, Strain), rows = vars(Par_ue)) +
  theme_bw()
```
# Variable names used in Data Dictionary

```{r}
# colnames(SolFitsMeta)
```


# Save Rds for further analysis

```{r save rds}
saveRDS(SolFitsMetaLRCGrowth, file.path(DataOut, paste(Project, "SolFitsMetaLRCGrowth.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

# saveRDS(SolFitsMetaLRC, file.path("..", "..", "PicoDiel", "Data", "CleanedData",  "SolFitsMetaLRC.Rds", fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```


XXXXDoug Stopped JVPSII_umol_eLs calibratedXXX

c


# Choosen corresponding Ex_WL

```{r}
SolFitsMetaLightCorr1<-SolFitsMetaLRCGrowth %>% 
  filter(WL== 405 | WL == 450) %>% 
  filter(Ex_WL == 445)

SolFitsMetaLightCorr2<-SolFitsMetaLRCGrowth %>% 
  filter(WL== 470) %>% 
  filter(Ex_WL == 470)
  
SolFitsMetaLightCorr3<-SolFitsMetaLRCGrowth %>% 
  filter(WL== 530) %>% 
  filter(Ex_WL == 535)

SolFitsMetaLightCorr4<-SolFitsMetaLRCGrowth %>% 
  filter(WL== 620 | WL== 660 | WL == 730) %>% 
  filter(Ex_WL == 590)

SolFitsMetaLRCGrowthCorr<-rbind(SolFitsMetaLightCorr1, SolFitsMetaLightCorr2, SolFitsMetaLightCorr3, SolFitsMetaLightCorr4)
  rm(SolFitsMetaLightCorr1, SolFitsMetaLightCorr2, SolFitsMetaLightCorr3, SolFitsMetaLightCorr4)
```


------------------------------------------------------# Add Turner Catalog--------------------------------------------------

# Load Turner catalog

```{r load turner catalog, message = FALSE, warning = FALSE, echo=FALSE}
gs4_deauth()
Turnercatalog<- read_sheet("https://docs.google.com/spreadsheets/d/13mQm0B3siS65UuGjNdzvpHFomfuwn6aAg7dBoq1IqrM/edit#gid=0")

as.data.frame(Turnercatalog)
ChlData <- Turnercatalog 

ChlData <- ChlData %>%  
  mutate(TurChl_ugL = as.numeric(Reading_rfu) * as.numeric(Chl_slope) + as.numeric(Chl_intercept)) %>% 
  mutate(DATE = ymd(`DATE`)) %>% 
  rename(SampleID=CultureID) %>% 
  rename(ObsDate=DATE) %>% 
  select(c(SampleID, ObsDate, TurChl_ugL)) %>% 
  filter(TurChl_ugL<212354.754)  #outliers

```

# Merge Turner with CultureCatalog

```{r}
ChlDataMeta <- CultureCatalog %>% 
  left_join(., ChlData, by = c("SampleID"="SampleID")) %>% 
    mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA77G"~"PC-rich_077")) 
```


# Calculate Chl mean from 3 technical replica - wierd issue with ObsDate - probably I need to use Turner correlation

```{r}
colnames(ChlDataMeta)

ChlDataMeta <- ChlDataMeta %>%
  group_by(Strain, WL, O2) %>%
  summarize(SampleID, Run, Strain, ExpDate, Par_ue, Photoperiod, O2, WL, PARPhotonDose_day, ObsDate, TurChl_ugL,
            meanTurChl_ugL = mean(TurChl_ugL),
            sdTurChl_ugL = sd(TurChl_ugL)) %>%
  ungroup() %>% 
  select(-c(ObsDate))
```
# Create Preliminary plot

```{r preliminary plot}
ChlDataMeta %>%
  ggplot() +
  geom_point(aes(x = WL, y = meanTurChl_ugL)) +
  ggh4x::facet_nested(rows = vars(Par_ue, O2), cols = vars(Strain), labeller = labeller(Ex_WL = label_both, strain = label_value, Par_ue = label_both, WL = label_both, Photoperiod = label_value)) +
  theme_bw()

```


# Merge JVPSII with chlorophyll Turner data 
It is "bigger" df b/c I have 3 replica for Turner

#SolFitsMetaLRCGrowthCorr or SolFitsMetaLRCGrowth

```{r}
SolFitsExpStTurner <- ChlDataMeta %>%
  full_join(., SolFitsMetaLRCGrowthCorr, by = c("SampleID"="SampleID", "Run"="Run", "Strain"="Strain", "ExpDate"="ExpDate", "Par_ue"="Par_ue", "Photoperiod"="Photoperiod", 'O2'="O2", "WL"="WL", "PARPhotonDose_day"="PARPhotonDose_day")) 

#"ObsDate"="ObsDate"
```

# Removed TurChl_ugL b/c I have already mean from 3 technical replica - smaller df

```{r}
SolFitsExpStTurner<-SolFitsExpStTurner %>% 
  select(-c(TurChl_ugL)) %>% 
  unique()
```

# Create Preliminary plot

```{r preliminary plot}
#colnames(SolFitsExpStTurner)

SolFitsExpStTurner %>%
  ggplot() +
  geom_point(aes(x = WL, y = meanTurChl_ugL)) +
  ggh4x::facet_nested(rows = vars(Par_ue, O2), cols = vars(Strain), labeller = labeller(Ex_WL = label_both, strain = label_value, Par_ue = label_both, WL = label_both, Photoperiod = label_value)) +
  theme_bw()

SolFitsExpStTurner %>%
  filter(WL!= "WW") %>% 
  ggplot() +
  geom_point(aes(y = JVPSII_umol_eLs_Par_ue, x = meanTurChl_ugL)) +
  ggh4x::facet_nested(rows = vars(Par_ue, O2), cols = vars(Strain, WL), labeller = labeller(Ex_WL = label_both, strain = label_value, Par_ue = label_both, WL = label_both, Photoperiod = label_value)) +
  theme_bw()



```


```{r}
lab1=c(expression("PC-rich_077"), expression("PE-rich_127"))

SolFitsExpStTurner %>% 
  ggplot() +
  geom_point(aes(x = WL, y = meanTurChl_ugL, colour = as.factor(Strain)), size = 3.5, show.legend = T) +
  scale_colour_discrete(type=c("palegreen3", "brown4"), name="", labels = lab1) +
    ggh4x::facet_nested(rows = vars(factor(O2, levels=c("21","0"))), labeller = label_parsed) +
  #ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw()

SolFitsExpStTurner %>% 
  ggplot() +
  geom_point(aes(x = E_days, y = JVPSII_umol_eLs_Par_ue, colour = as.factor(Strain)), size = 3.5, show.legend = T) +
  scale_colour_discrete(type=c("palegreen3", "brown4"), name="", labels = lab1) +
    ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(factor(O2, levels=c("21","0"))), labeller = label_parsed) +
  #ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw()


SolFitsExpStTurner %>% 
  ggplot() +
  geom_point(aes(x = meanTurChl_ugL, y = JVPSII_umol_eLs_Par_ue, colour = as.factor(Strain)), size = 3.5, show.legend = T) +
  scale_colour_discrete(type=c("palegreen3", "brown4"), name="", labels = lab1) +
    ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(factor(O2, levels=c("21","0"))), labeller = label_parsed) +
  #ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw()

SolFitsExpStTurner %>% 
  ggplot() +
  geom_point(aes(x = meanTurChl_ugL, y = JVPSII_umol_eLs_HalfPar_ue, colour = as.factor(Strain)), size = 3.5, show.legend = T) +
  scale_colour_discrete(type=c("palegreen3", "brown4"), name="", labels = lab1) +
    ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(factor(O2, levels=c("21","0"))), labeller = label_parsed) +
  theme_bw()
```


--------------------------------------------------- MD Pico --------------------------------------

# IMPORT MD PICO CORRELATION DATA

```{r set project variables, warning = FALSE, echo = FALSE}
Project <- "BalticO2"
zip_file <- file.path("..", "Data", "RawData", "MDPico.zip")

# List files in the extracted folder with a ".txt" extension
CountFiles <- unzip(zip_file, list = TRUE)
CountFiles <- CountFiles[grepl(".csv$", CountFiles$Name), "Name"]
print(CountFiles)

FileID <- "ExperimentSummaryData"
FileEncode <- "UTF-8" 
HeaderRows <- 0
DelimCS <- ","
```

# Read fread_plus function

```{r data read adds filename and cdate, warning=FALSE, message=FALSE, echo=FALSE}
# Define function to read and process each file
fread_plus <- function(Flnm, FileEncode, Delim) {
  con <- unz(zip_file, Flnm)
  
  # Read the file using read.table
  data <- read.table(con, skip = HeaderRows, encoding = FileEncode, sep = Delim, header = TRUE)
  
  # Use tryCatch to handle errors during the closing of the connection
  tryCatch(
    close(con),
    error = function(e) {
      warning("Error closing connection: ", e$message)
    })
  
  data <- data %>%
    mutate(Filename = Flnm, CDateTime = ymd_hms(file.info(zip_file)$ctime)) 
  return(data)
}

# Use map_df to read and process all files in CountFiles
MDPicoTidy <- CountFiles %>%
  map_df(~fread_plus(Flnm = ., FileEncode = FileEncode, Delim = DelimCS))
```

```{r tidy CountTidy}

MDPicoTidy <- MDPicoTidy %>% 
  select(-c("Concentration", "Group", "Compound", "CDateTime")) %>% # remove superfluous columns
  mutate(Filename = str_remove(string = Filename, pattern = ".csv")) %>%
  mutate(Filename = str_remove(string = Filename, pattern = "../MDPico/")) %>%
  separate(Filename, into = c("ObsDate", "Project", "Initials",  "PlateNr", "IndStud", "Organism", "Count"), sep = "([\\/\\/\\_\\_\\_\\_\\_])", remove = FALSE) %>%
  select(-c("IndStud", "Organism", "Count")) %>% 
  mutate(ObsDate = ymd_hm(ObsDate)) 

```

Load MDPicoMetaData catalog
```{r load local metadatacatalog, message = FALSE, warning = FALSE, echo=FALSE}
gs4_deauth()

# this is the URL or ID of a Sheet readable by anyone (with a link)

MDPicoMetaData <- read_sheet("https://docs.google.com/spreadsheets/d/1Lerp5u25kzBtaBbnOYElYqUP59cn68gJpxxayhnGdkw/edit#gid=0") %>%
  #mutate(Date = as.numeric(Date)) %>%
  mutate(Date = ymd_hm(`Date`)) %>%
  separate(Date, into = c("Date_count", "Time_count"), sep = " ", remove = FALSE) %>%
  mutate(Date_count = ymd(`Date_count`)) 
```


# Merge MD Pico and Culture catalog

```{r}
MDPicoMeta <- MDPicoMetaData %>%
  left_join(., CultureCatalog, by = c("SampleID" = "SampleID")) %>% 
      mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA77G"~"PC-rich_077")) 
```


# Merge

```{r}
MDPicoAll <- MDPicoTidy %>%
  mutate(PlateNr = as.double(PlateNr)) %>%
  left_join(., MDPicoMeta, by = c("Well.Name" = "WellNumber", "PlateNr" = "PlateNumber")) %>% 
  drop_na(Strain)
```

```{r, warning = FALSE}
MDPicoAll <- MDPicoAll %>%
  mutate(culture_inocul_L = as.double(culture_inocul_L)) %>%
  mutate(CapAreaPercentage = as.double(CapAreaPercentage)) %>%

  mutate(CellmL_MDPico = (`Cell.Count` * (0.001/culture_inocul_L)) /(CapAreaPercentage/100)) %>%
  # mutate(cellsml = `cellsmlwithoutpercentage`/(CapAreaPercentage/100))
group_by(SampleID) %>%
  arrange(Date_count) %>%
  mutate(E_days = as.numeric((Date_count - ExpDate[1]))) %>%
ungroup() 
  
```


# Create Preliminary plot

```{r preliminary plot}
MDPicoAll %>%
  ggplot() +
  geom_point(aes(x = E_days, y = CellmL_MDPico)) +
  ggh4x::facet_nested(rows = vars(Par_ue, O2), cols = vars(Strain, WL), labeller = labeller(Ex_WL = label_both, strain = label_value, Par_ue = label_both, WL = label_both, Photoperiod = label_value)) +
  theme_bw()

```

# Calculate "Big" cell count mean from 3 technical replica - wierd issue with ObsDate_Count - probably I need to use MDPico correlation

```{r}
#Date_count

MDPicoAll <- MDPicoAll %>%
  filter(E_days>4) %>% 
group_by(Strain, WL, O2) %>%

summarize(Well.Name, Cell.Count, Filename, ObsDate, PlateNr, PlateID, SampleID, Date, Date_count, Time_count, media_inocul_L, culture_inocul_L, CapAreaPercentage, Run, Strain, ExpDate, Par_ue, Photoperiod, PARPhotonDose_day, Tube, O2, WL, LightShape, ExpEndDate, E_days, CellmL_MDPico, 
          meanCellmL_MDPico = mean(CellmL_MDPico), 
          sdCellmL_MDPico = sd(CellmL_MDPico)) %>%
ungroup() %>%
  
  rename(Cell_Count=Cell.Count) %>% 
  rename(Well_Name=Well.Name) %>% 
  rename(MeasDate = ObsDate) %>% 
  rename(ObsDateTime = Date) %>% 
  rename(ObsDate_count = Date_count) %>% 
  rename(ObsTime_count = Time_count) %>% 
  rename(FilenameMDPico=Filename) 
```

```{r}
#colnames(MDPicoAll)

MDPicoAll <- MDPicoAll %>%
  select(c(Strain, WL, SampleID, Run, ExpDate, Par_ue, Photoperiod, PARPhotonDose_day, O2, meanCellmL_MDPico, sdCellmL_MDPico))
```

# Create Preliminary plot

```{r preliminary plot}
MDPicoAll %>%
  ggplot() +
  geom_point(aes(x = WL, y = meanCellmL_MDPico)) +
  ggh4x::facet_nested(rows = vars(Par_ue, O2), cols = vars(Strain), labeller = labeller(Ex_WL = label_both, strain = label_value, Par_ue = label_both, WL = label_both, Photoperiod = label_value)) +
  theme_bw()

```


# Merge Sigma-Turner with MDPicoData data 

```{r}
SolFitsExpStTurnerMD <- MDPicoAll %>%
  full_join(., SolFitsExpStTurner, by = c("SampleID"="SampleID", "Run"="Run", "Strain"="Strain", "ExpDate"="ExpDate", "Par_ue"="Par_ue", "Photoperiod"="Photoperiod", 'O2'="O2", "WL"="WL", "PARPhotonDose_day"="PARPhotonDose_day")) %>% 
  drop_na(Ex_WL) %>% 
  unique()

```

```{r preliminary plot}
#colnames(SolFitsExpStTurner)

SolFitsExpStTurnerMD %>%
  ggplot() +
  geom_point(aes(x = WL, y = meanCellmL_MDPico)) +
  ggh4x::facet_nested(rows = vars(Par_ue, O2), cols = vars(Strain), labeller = labeller(Ex_WL = label_both, strain = label_value, Par_ue = label_both, WL = label_both, Photoperiod = label_value)) +
  theme_bw()


SolFitsExpStTurnerMD %>%
  filter(WL!= "WW") %>% 
  ggplot() +
  geom_point(aes(y = JVPSII_umol_eLs_Par_ue, x = meanCellmL_MDPico)) +
  ggh4x::facet_nested(rows = vars(Par_ue, O2), cols = vars(Strain, WL), labeller = labeller(Ex_WL = label_both, strain = label_value, Par_ue = label_both, WL = label_both, Photoperiod = label_value)) +
  theme_bw()

```

# Calculate cell per L - for JVPSII

```{r}
SolFitsExpStTurnerMD<-SolFitsExpStTurnerMD %>% 
  mutate(meanCellL_MDPico=meanCellmL_MDPico*1000) %>% 
  mutate(sdCellL_MDPico=sdCellmL_MDPico*1000)
```



# Create Preliminary plot

```{r preliminary plot}

lab1=c(expression("PC-rich_077"), expression("PE-rich_127"))

SolFitsExpStTurnerMD %>% 
  ggplot() +
  geom_point(aes(x = E_days, y = meanCellmL_MDPico, colour = as.factor(Strain)), size = 3.5, show.legend = T) +
  scale_colour_discrete(type=c("palegreen3", "brown4"), name="", labels = lab1) +
    ggh4x::facet_nested(cols = vars(WL), rows = vars(factor(O2, levels=c("21","0"))), labeller = label_parsed) +
  #ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw()

SolFitsExpStTurnerMD %>% 
  filter(WL!= "WW") %>% 
  ggplot() +
  geom_point(aes(y = JVPSII_umol_eLs_Par_ue, x = meanCellmL_MDPico, colour = as.factor(Strain)), size = 3.5, show.legend = T) +
  scale_colour_discrete(type=c("palegreen3", "brown4"), name="", labels = lab1) +
    ggh4x::facet_nested(cols = vars(WL), rows = vars(factor(O2, levels=c("21","0"))), labeller = label_parsed) +
  #ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw()

SolFitsExpStTurnerMD %>%
  filter(WL!= "WW") %>% 
  ggplot() +
  geom_point(aes(x = E_days, y = JVPSII_umol_eLs_Par_ue, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  scale_colour_discrete(type=c("palegreen3", "brown4"), name="", labels = lab1) +
  ggh4x::facet_nested(cols = vars(WL), rows = vars(factor(O2, levels=c("21","0"))), labeller = label_parsed) +
  theme_bw() 

SolFitsExpStTurnerMD %>%
  filter(WL!= "WW") %>% 
  ggplot() +
  geom_point(aes(x = meanTurChl_ugL, y = JVPSII_umol_eLs_Par_ue, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  scale_colour_discrete(type=c("palegreen3", "brown4"), name="", labels = lab1) +
  ggh4x::facet_nested(cols = vars(WL), rows = vars(factor(O2, levels=c("21","0"))), labeller = label_parsed) +
  theme_bw() 

SolFitsExpStTurnerMD %>%
  filter(WL!= "WW") %>% 
  ggplot() +
  geom_point(aes(x = meanCellmL_MDPico, y = JVPSII_umol_eLs_Par_ue, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  scale_colour_discrete(type=c("palegreen3", "brown4"), name="", labels = lab1) +
  ggh4x::facet_nested(cols = vars(WL), rows = vars(factor(O2, levels=c("21","0"))), labeller = label_parsed) +
  theme_bw() 
```


-------------------------------------------------------------------------------------------------------------------------
------------------------------------------------ Chl and Phyco 445 and 590 ------------------------------------------
--------------------------------------------------------------------------------------------------------------------


```{r}
SolFitsMetaLRCGrowthCorr1<-SolFitsMetaLRCGrowth %>% 
  filter(Ex_WL == 445)

SolFitsMetaLRCGrowthCorr2<-SolFitsMetaLRCGrowth %>% 
  filter(Ex_WL == 590)

SolFitsMetaLRCGrowthCorr3<-SolFitsMetaLRCGrowth %>% 
  filter(Ex_WL == 535)

SolFitsMetaLRCGrowth445590<-rbind(SolFitsMetaLRCGrowthCorr1, SolFitsMetaLRCGrowthCorr2, SolFitsMetaLRCGrowthCorr3)
  rm(SolFitsMetaLRCGrowthCorr1, SolFitsMetaLRCGrowthCorr2, SolFitsMetaLRCGrowthCorr3)
  
```


```{r}
SolFitsMetaLRCGrowth445590<-SolFitsMetaLRCGrowth445590 %>% 
  mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(WL != "WW") %>% 
  mutate(Oxygen=case_when(O2==21~"250~µM",
         O2==0~"2.5~µM"))

SolFitsMetaLRCGrowth445590<-SolFitsMetaLRCGrowth445590 %>% 
  mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(WL != "WW") %>% 
  mutate(Oxygen=case_when(O2==21~"250~µM",
         O2==0~"2.5~µM"))
```

```{r}
SolFitsMetaLRCGrowth445590<-SolFitsMetaLRCGrowth445590 %>% 
  mutate(Strain=case_when(Strain=="PE-rich_127"~"PE-rich",
         Strain=="PC-rich_077"~"PC-rich"))
```


-------------------------------------------- Turner ---------------------------------------------------

# Merge JVPSII with chlorophyll Turner data 
It is "bigger" df b/c I have 3 replica for Turner

#SolFitsMetaLRCGrowthCorr or SolFitsMetaLRCGrowth

```{r}
ChlDataMeta<-ChlDataMeta %>% 
  mutate(Strain=case_when(Strain=="PE-rich_127"~"PE-rich",
         Strain=="PC-rich_077"~"PC-rich"))

SolFitsExpStTurner445590 <- ChlDataMeta %>%
  full_join(., SolFitsMetaLRCGrowth445590, by = c("SampleID"="SampleID", "Run"="Run", "Strain"="Strain", "ExpDate"="ExpDate", "Par_ue"="Par_ue", "Photoperiod"="Photoperiod", 'O2'="O2", "WL"="WL", "PARPhotonDose_day"="PARPhotonDose_day")) 

#"ObsDate"="ObsDate"
```

# Removed TurChl_ugL b/c I have already mean from 3 technical replica - smaller df

```{r}
SolFitsExpStTurner445590<-SolFitsExpStTurner445590 %>% 
  select(-c(TurChl_ugL)) %>% 
  unique()
```

# Create Preliminary plot

```{r preliminary plot}
#colnames(SolFitsExpStTurner)

SolFitsExpStTurner445590 %>%
  ggplot() +
  geom_point(aes(x = WL, y = meanTurChl_ugL)) +
  ggh4x::facet_nested(rows = vars(Par_ue, O2), cols = vars(Strain), labeller = labeller(Ex_WL = label_both, strain = label_value, Par_ue = label_both, WL = label_both, Photoperiod = label_value)) +
  theme_bw()

SolFitsExpStTurner445590 %>%
  filter(WL!= "WW") %>% 
  ggplot() +
  geom_point(aes(y = JVPSII_umol_eLs_Par_ue, x = meanTurChl_ugL)) +
  ggh4x::facet_nested(rows = vars(Par_ue, O2), cols = vars(Strain, WL), labeller = labeller(Ex_WL = label_both, strain = label_value, Par_ue = label_both, WL = label_both, Photoperiod = label_value)) +
  theme_bw()

```

-------------------------------------- MD Pico -------------------------------------


# Merge Sigma-Turner with MDPicoData data 

```{r}
MDPicoAll<-MDPicoAll %>% 
  mutate(Strain=case_when(Strain=="PE-rich_127"~"PE-rich",
         Strain=="PC-rich_077"~"PC-rich"))

SolFitsExpStTurnerMD445590 <- MDPicoAll %>%
  full_join(., SolFitsExpStTurner445590, by = c("SampleID"="SampleID", "Run"="Run", "Strain"="Strain", "ExpDate"="ExpDate", "Par_ue"="Par_ue", "Photoperiod"="Photoperiod", 'O2'="O2", "WL"="WL", "PARPhotonDose_day"="PARPhotonDose_day")) %>% 
  drop_na(Ex_WL) %>% 
  unique()

```

```{r preliminary plot}
#colnames(SolFitsExpStTurner)

SolFitsExpStTurnerMD445590 %>%
  ggplot() +
  geom_point(aes(x = WL, y = meanCellmL_MDPico)) +
  ggh4x::facet_nested(rows = vars(Par_ue, O2), cols = vars(Strain), labeller = labeller(Ex_WL = label_both, strain = label_value, Par_ue = label_both, WL = label_both, Photoperiod = label_value)) +
  theme_bw()


SolFitsExpStTurnerMD445590 %>%
  filter(WL!= "WW") %>% 
  ggplot() +
  geom_point(aes(y = JVPSII_umol_eLs_Par_ue, x = meanCellmL_MDPico)) +
  ggh4x::facet_nested(rows = vars(Par_ue, O2), cols = vars(Strain, WL), labeller = labeller(Ex_WL = label_both, strain = label_value, Par_ue = label_both, WL = label_both, Photoperiod = label_value)) +
  theme_bw()

```

# Calculate cell per L - for JVPSII

```{r}
SolFitsExpStTurnerMD445590<-SolFitsExpStTurnerMD445590 %>% 
  mutate(meanCellL_MDPico=meanCellmL_MDPico*1000) %>% 
  mutate(sdCellL_MDPico=sdCellmL_MDPico*1000)
```



# Create Preliminary plot

```{r preliminary plot}

lab1=c(expression("PC-rich_077"), expression("PE-rich_127"))

SolFitsExpStTurnerMD445590 %>% 
  ggplot() +
  geom_point(aes(x = E_days, y = meanCellmL_MDPico, colour = as.factor(Strain)), size = 3.5, show.legend = T) +
  scale_colour_discrete(type=c("palegreen3", "brown4"), name="", labels = lab1) +
    ggh4x::facet_nested(cols = vars(WL), rows = vars(factor(O2, levels=c("21","0"))), labeller = label_parsed) +
  #ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw()

SolFitsExpStTurnerMD445590 %>% 
  filter(WL!= "WW") %>% 
  ggplot() +
  geom_point(aes(y = JVPSII_umol_eLs_Par_ue, x = meanCellmL_MDPico, colour = as.factor(Strain)), size = 3.5, show.legend = T) +
  scale_colour_discrete(type=c("palegreen3", "brown4"), name="", labels = lab1) +
    ggh4x::facet_nested(cols = vars(WL), rows = vars(factor(O2, levels=c("21","0"))), labeller = label_parsed) +
  #ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw()

SolFitsExpStTurnerMD445590 %>%
  filter(WL!= "WW") %>% 
  ggplot() +
  geom_point(aes(x = E_days, y = JVPSII_umol_eLs_Par_ue, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  scale_colour_discrete(type=c("palegreen3", "brown4"), name="", labels = lab1) +
  ggh4x::facet_nested(cols = vars(WL), rows = vars(factor(O2, levels=c("21","0"))), labeller = label_parsed) +
  theme_bw() 

SolFitsExpStTurnerMD445590 %>%
  filter(WL!= "WW") %>% 
  ggplot() +
  geom_point(aes(x = meanTurChl_ugL, y = JVPSII_umol_eLs_Par_ue, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  scale_colour_discrete(type=c("palegreen3", "brown4"), name="", labels = lab1) +
  ggh4x::facet_nested(cols = vars(WL), rows = vars(factor(O2, levels=c("21","0"))), labeller = label_parsed) +
  theme_bw() 

SolFitsExpStTurnerMD445590 %>%
  filter(WL!= "WW") %>% 
  ggplot() +
  geom_point(aes(x = meanCellmL_MDPico, y = JVPSII_umol_eLs_Par_ue, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  scale_colour_discrete(type=c("palegreen3", "brown4"), name="", labels = lab1) +
  ggh4x::facet_nested(cols = vars(WL), rows = vars(factor(O2, levels=c("21","0"))), labeller = label_parsed) +
  theme_bw() 
```







-------------------------------------------------------------------------------------------------------

# Save rds for further analysis

```{r save rds}
saveRDS(SolFitsExpStTurnerMD, file.path(DataOut, paste(Project, "Processed_SolisenseJVPSIICorr.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)


saveRDS(SolFitsExpStTurnerMD445590, file.path(DataOut, paste(Project, "Processed_SolisenseJVPSII445590.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```




















--------------------------------- Adding cell_L from calibration ---------------------------------

```{r set project variables}
# Project <- "BalticPhotoperiod"
# DataIn <- file.path("..", "Data", "ProcessedData", "ProcessedPigmentsData", fsep = .Platform$file.sep)
```

```{r Exported Rmd}
# list.files(path = DataIn, pattern = Project, full.names = TRUE)
```

```{r read pigments File}
#df ontained mean OD per day from Multiculti and Abs from Olis spectra for selected nm. Based on this I calculated pigments per mL and per cell (pg/cell)

# MCPigmentAllFile <- "../Data/ProcessedData/ProcessedPigmentsData/BalticPhotoperiod_Processed_PigmentsAll.Rds"
# MCPigmentAllFileName <- str_split(string = MCPigmentAllFile, "/")[[1]][3] %>%
#   str_remove(pattern = ".Rds")
# MCPigmentAll <- readRDS(MCPigmentAllFile)  %>%
#   ungroup()
```

```{r}
# colnames(MCPigmentAll)
# 
# MCPigmentAll<-MCPigmentAll %>% 
#   select(-c(Phase, ChlaugmL, CarugmL, PEugmL, PCugmL, APCugmL, PhycougmL, CarChlaRatio, PhycoChlaRatio, PEPCRatio, Chlapgcell, Carpgcell, PEpgcell, PCpgcell, APCpgcell, Phycopgcell, meanOD720_h, meanDeltaOD_h, AchivePreStationary, dayRound_tmaxAG, MaxAG, MaxDG, MC))

```

```{r}
# MCPigmentAll <- MCPigmentAll %>%
#   filter(ToD==12) # When I choose 12 (peak) then I loose a few data point from 12h and 900UE
```

```{r}
# SolFitsAll <- MCPigmentAll %>%
#   full_join(., SolFitsExpStTurner, by = c("SampleID"="SampleID", "Strain"="Strain", "Run"="Run", "Tube"="Tube", "Par_ue" = "Par_ue", "Photoperiod"="Photoperiod", "O2"="O2", "WL"="WL", "LightShape"="LightShape", "ExpDate"="ExpDate", "ExpEndDate"="ExpEndDate", "PARPhotonDose_day"="PARPhotonDose_day","E_days"="E_days"))
```

```{r}
# SolFitsAll<-SolFitsAll %>% 
#   drop_na(JVPSII_umol_eLs_Par_ue)
```

# Create preliminary plot

```{r preliminary plot}
# lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
# lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
# lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))
# 
# SolFitsAll %>%
#   filter(Ex_WL == 445) %>% 
#   ggplot() +
#   geom_point(aes(x = E_days, y = JVPSII_umol_eLs_Par_ue, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
#   scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
#   ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
#   theme_bw() 
# 
# SolFitsAll %>%
#   filter(Ex_WL == 445) %>% 
#   ggplot() +
#   geom_point(aes(x = TurChl_ugL, y = JVPSII_umol_eLs_Par_ue, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
#   scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
#   ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
#   theme_bw() 
# 
# SolFitsAll %>%
#   filter(Ex_WL == 445) %>% 
#   ggplot() +
#   geom_point(aes(x = cellL_OD680, y = JVPSII_umol_eLs_Par_ue, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
#   scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
#   ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
#   theme_bw() 
```



# Calculate Turner per umol chl

```{r}
# SolTurner<-SolTurner %>% 
#   mutate(meanTurChl_umolL=meanTurChl_ugL*0.00112)
```



# Adding facet labels

```{r}
#SolTurnerMDPico$facetsExcitation = factor(SolTurnerMDPico$WL, labels = c("Excitation~(nm)"))
```





--------------------------------------------------------------------------------------------------------------------------

Oxborough & Baker 1997 for Fo'

Oxborough, K., & Baker, N. R. (1997). Resolving chlorophyll a fluorescence images of photosynthetic efficiency into photochemical and non-photochemical components–calculation of qP and Fv-/Fm-; without measuring Fo. Photosynthesis research, 54, 135-142.

Oxborough, K., & Baker, N. R. (1997). An instrument capable of imaging chlorophyll a fluorescence from intact leaves at very low irradiance and at cellular and subcellular levels of organization. Plant, Cell & Environment, 20(12), 1473-1483.

Oxborough, K., Moore, C. M., Suggett, D. J., Lawson, T., Chan, H. G., & Geider, R. J. (2012). Direct estimation of functional PSII reaction center concentration and PSII electron flux on a volume basis: a new approach to the analysis of Fast Repetition Rate fluorometry (FRRf) data. Limnology and Oceanography: Methods, 10(3), 142-154.

Suggett, D. J., Moore, C. M., Oxborough, K., & Geider, R. J. (2006). Fast repetition rate (FRR) chlorophyll a fluorescence induction measurements. West Molesey: Chelsea Technologies Group, 1-53.




Berge, J., Grant, S., Bjørgum, R., Cohen, J. H., McKee, D., Johnsen, G., Zolich, A., Kopec, T. P., Vogedes, D. L., UiT The Arctic University of Norway (2021).Time series (2017) of irradiance in the PAR (photosynthetically active radiation) region measured under the dome of a light observatory in the Arctic  (Ny-Ålesund, Svalbard, Norway) derived from an USSIMO spectroradiometer [Data set]. Norstore. https://doi.org/10.11582/2021.00040

https://archive.norstore.no/pages/public/datasetDetail.jsf?id=10.11582/2021.00040

PAR is approximated as an integral of micromolespersec=(uirr/(h*c/(lambda*1e-9)))/microavo for wavelengths(lambda) in range from 400 to 700nm, where: uirr = USSIMO irradiance for wavelength equal to lambda, h=6.63e-34 [Js], c=3.00e+08 [m/s], microavo=6.022e17.





Fast Repetition Rate fluorometry (FRRf, Kolber et al. 1998) 

σPSII - Effective absorption cross section of PSII photochemistry in darkness -> A2 (quanta)-1 or m2
ρ - Connectivity between PSII reaction centres in darkness

σPSII′ - Effective absorption cross section of PSII photochemistry under actinic light -> A2 (quanta)-1 or m2
ρ′ - Connectivity between PSII reaction centres under actinic light

TauPSII - Minimum turnover time of PSII photochemistry -> s-1

F0 or F0’ (Minimum fluorescence in darkness or Minimum fluorescence under actinic light)
Fm or Fm’ (Maximum fluorescence in darkness or Maximum fluorescence under actinic light)
F’ (or Fs; Steady state fluorescence at any point)
Fv = Fm-F0 (Variable fluorescence in darkness)
Fv’ = Fm’-F0’ (Variable fluorescence under actinic light)
Fq′ = (Fm′ - F′) (Difference between Fm′ and F′)

Fv/Fm = (Fm-F0)/Fm (The maximum PSII quantum yield/Maximum photochemical efficiency)
Fv’/Fm’ = (Fm’- F0’)/Fm’ (Maximum PSII efficiency under actinic light)

ΦPSII = (Fm’- F’)/Fm’ = Fq′/Fm′ (Photochemical efficiency under actinic light)

qP = (Fm’- F’)/(Fm’-F0’) = (Fm′ - F′)/Fv′ = Fq′/Fv′ (PSII efficiency factor under actinic light; photochemical quenching coefficient) 

NPQ =(Fm-Fm’)/Fm’ (Non-photochemical quenching coefficien)


ETR = PPFD * aPSII * PSII photochemical efficiency (ΦPSII)

ETR^RCII = PPFD * σPSII * Fq′/Fm′ (or ΦPSII) * 21.683

ETR^chl = PPFD * σPSII * n PSII * Fq′/Fm′ (or ΦPSII) * 21.683


FRR fluorescence provides a direct measure of light absorption per unit PSII reaction centres (σPSII).

ETR, called the relative electron transport rate, is the product of the effective photochemical yield of
PSII (ΦPSII) and photosynthetic photon flux density

ETR^RCII(chl) - RCII (Chlorophyll a)-normalised rate of electron transfer by PSII -> mol e- g chla-1 h-1

ETR^chl is the chlorophylla-specific rate of electron transfer (mol e- mol chla-1 h-1 ).

PPFD (=E) - Photosynthetically active photon flux density -> μmol m-2 s-1

a^chlPSII - a^chl only used for PSII photochemistry -> m2 mg chla-1

(factor 21.683 converts seconds to hours, μmol e- to mol e- and A2 quanta-1 to m2 mol RCII-1)

nPSII - photosynthetic unit size of PSII

JVPSII - PSII flux per unit volume -> electrons m–3 s–1

[RCII] - concentration of functional PS II reaction centers -> m-3

aLHII - LHII (light harvesting complex II) absorption coefficient -> m-1


```{r example of different labels on plot}

# data_textF0 <- data.frame(facetsActinicPAR  = c("Actinic~PAR~(µmol~photons~m^{-2}~s^{-1})"), facetsExcitation  = c("Excitation~(nm)"), PAR  = c(0), Ex_WL  = c(445), Strain  = c("PE-rich_048"), label = c("italic(F)[0]^{-1}"))

# data_textF0 <- data.frame(facetsActinicPAR = c("Actinic~PAR~(µmol~photons~m^{-2}~s^{-1})"),
#                           facetsExcitation = c("Excitation~(nm)"),
#                           PAR = c(0),
#                           Ex_WL = c(445),
#                           Strain = c("PE-rich_048"),
#                           label = c("~\"''\""))
# 
# LIFTMeta %>%
#   filter(Time_us < 1000) %>%
#   ggplot() +
#   geom_point(aes(x = Time_us, y = EM), colour = "brown1", alpha = 0.8, size = 2, show.legend = FALSE) +
#   geom_text(data = data_textF0, aes(x = 50, y = 100, label = label), size = 3.5, parse = TRUE) +
#   ggh4x::facet_nested(cols = vars(facetsActinicPAR, PAR), rows = vars(facetsExcitation, Ex_WL), labeller = label_parsed, scales = "free_y") +
#   theme_bw()

```
