---
title: "Process_GrowthCurveData"
author:
- Sylwia Sliwinska-Wilczewska
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: BalticPhotoperiod.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

Process_GrowthCurveData.Rmd separately processes and combines all .Rds from Data/ImportedData/ImportedMCData folder. This .Rmd generates Baltic_Photoperiod_Processed_GrowthCurve.Rds (stored in Data/ProcessedData/ProcessedGrowthCurveData folder) and GrowthCurve_SupPlot.png (stored in Output/Plots folder).

# Load Libraries and set Project Variables

```{r load libraries} 
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(ggpubr)
library(data.table)
library(googledrive)
library(googlesheets4)
```

```{r set project variables}
Project <- "BalticCCA"
DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedGrowthCurveData")
DataIn <- file.path("..", "Data", "ImportedData", "ImportedMCData", fsep = .Platform$file.sep)

PlotsPath <- file.path("..", "Output", "Plots")
RDSPlotPath <- file.path("..", "Output", "PlotsRDS")

FileEncode <- "UTF-8" 
Delimiter <- ""
HeaderRows <- 0
```

# List and read imported MC files

```{r Exported Rmd only first time in session}
list.files(path = DataIn, full.names = TRUE)
```

# Import selected Rds and calculate mean OD from every hour based on ToD and time

## Import Run56

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}
MultiCultiFile <- "../Data/ImportedData/ImportedMCData/20220323_PICO_MCMIX004_RUN56_TargetDataMetaFilter.Rds"
MultiCultiFileName <- str_split(string = MultiCultiFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 
MultiCultiData <- readRDS(MultiCultiFile)  

MultiCultiData$ToD = sub("\\..*", "", MultiCultiData$ToD)
MultiCultiData$time = sub("\\..*", "", MultiCultiData$time)

MultiCultiData <- MultiCultiData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time) %>% 
  mutate(DeltaOD = OD680-OD720) 
  
MultiCultiData56 <- MultiCultiData %>%   
  group_by(SampleID, Day, ToD, time_h) %>% 
  summarize(Run, SampleID, Strain, ExpDate, Filename, Tube, time_h, ToD, Day, ExpDate, Actinic_par, OD680, OD720, DeltaOD, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par_h = mean(Actinic_par), meanOD680_h = mean(OD680), meanOD720_h = mean(OD720), meanDeltaOD_h = mean(DeltaOD)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720, DeltaOD)) %>% 
  unique()
```

## Import Run59

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}
MultiCultiFile <- "../Data/ImportedData/ImportedMCData/20220402_PICO_MCMIX004_RUN59_TargetDataMetaFilter.Rds"
MultiCultiFileName <- str_split(string = MultiCultiFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 
MultiCultiData <- readRDS(MultiCultiFile)  

MultiCultiData$ToD = sub("\\..*", "", MultiCultiData$ToD)
MultiCultiData$time = sub("\\..*", "", MultiCultiData$time)

MultiCultiData <- MultiCultiData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time) %>% 
  mutate(DeltaOD = OD680-OD720) 
  
MultiCultiData59 <- MultiCultiData %>%   
  group_by(SampleID, Day, ToD, time_h) %>% 
  summarize(Run, SampleID, Strain, ExpDate, Filename, Tube, time_h, ToD, Day, ExpDate, Actinic_par, OD680, OD720, DeltaOD, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par_h = mean(Actinic_par), meanOD680_h = mean(OD680), meanOD720_h = mean(OD720), meanDeltaOD_h = mean(DeltaOD)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720, DeltaOD)) %>% 
  unique()
```

## Import Run63

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}
MultiCultiFile <- "../Data/ImportedData/ImportedMCData/20220413_PICO_MCMIX004_RUN63_TargetDataMetaFilter.Rds"
MultiCultiFileName <- str_split(string = MultiCultiFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 
MultiCultiData <- readRDS(MultiCultiFile)  

MultiCultiData$ToD = sub("\\..*", "", MultiCultiData$ToD)
MultiCultiData$time = sub("\\..*", "", MultiCultiData$time)

MultiCultiData <- MultiCultiData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time) %>% 
  mutate(DeltaOD = OD680-OD720) 
  
MultiCultiData63 <- MultiCultiData %>%   
  group_by(SampleID, Day, ToD, time_h) %>% 
  summarize(Run, SampleID, Strain, ExpDate, Filename, Tube, time_h, ToD, Day, ExpDate, Actinic_par, OD680, OD720, DeltaOD, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par_h = mean(Actinic_par), meanOD680_h = mean(OD680), meanOD720_h = mean(OD720), meanDeltaOD_h = mean(DeltaOD)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720, DeltaOD)) %>% 
  unique()
```

## Import Run68

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}
MultiCultiFile <- "../Data/ImportedData/ImportedMCData/20220429_PICO_MCMIX004_RUN68_TargetDataMetaFilter.Rds"
MultiCultiFileName <- str_split(string = MultiCultiFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 
MultiCultiData <- readRDS(MultiCultiFile)  

MultiCultiData$ToD = sub("\\..*", "", MultiCultiData$ToD)
MultiCultiData$time = sub("\\..*", "", MultiCultiData$time)

MultiCultiData <- MultiCultiData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time) %>% 
  mutate(DeltaOD = OD680-OD720) 
  
MultiCultiData68 <- MultiCultiData %>%   
  group_by(SampleID, Day, ToD, time_h) %>% 
  summarize(Run, SampleID, Strain, ExpDate, Filename, Tube, time_h, ToD, Day, ExpDate, Actinic_par, OD680, OD720, DeltaOD, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par_h = mean(Actinic_par), meanOD680_h = mean(OD680), meanOD720_h = mean(OD720), meanDeltaOD_h = mean(DeltaOD)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720, DeltaOD)) %>% 
  unique()
```

## Import Run70

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}
MultiCultiFile <- "../Data/ImportedData/ImportedMCData/20220507_PICO_MCMIX004_RUN70_TargetDataMetaFilter.Rds"
MultiCultiFileName <- str_split(string = MultiCultiFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 
MultiCultiData <- readRDS(MultiCultiFile)  

MultiCultiData$ToD = sub("\\..*", "", MultiCultiData$ToD)
MultiCultiData$time = sub("\\..*", "", MultiCultiData$time)

MultiCultiData <- MultiCultiData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time) %>% 
  mutate(DeltaOD = OD680-OD720) 
  
MultiCultiData70 <- MultiCultiData %>%   
  group_by(SampleID, Day, ToD, time_h) %>% 
  summarize(Run, SampleID, Strain, ExpDate, Filename, Tube, time_h, ToD, Day, ExpDate, Actinic_par, OD680, OD720, DeltaOD, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par_h = mean(Actinic_par), meanOD680_h = mean(OD680), meanOD720_h = mean(OD720), meanDeltaOD_h = mean(DeltaOD)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720, DeltaOD)) %>% 
  unique()
```


# Merge selected Runs

```{r Mere selected Runs}
MultiCultiDataAll<-rbind(MultiCultiData56, MultiCultiData59, MultiCultiData63, MultiCultiData68, MultiCultiData70)

rm(MultiCultiData56, MultiCultiData59, MultiCultiData63, MultiCultiData68, MultiCultiData70)
```

# Rename column names for consistency

```{r}
MultiCultiDataAll<-MultiCultiDataAll %>% 
  rename(E_days=Day) %>% 
  rename(FilenameMC=Filename) %>% 
  rename(Time_h=time_h)
```

# Add facets labels and change strain name to create plot

```{r add facets labels and change strain names}
MultiCultiDataAll$facetsPar_ue = factor(MultiCultiDataAll$O2, labels = c("PAR~(µmol~photons~m^{-2}~s^{-1})"))
MultiCultiDataAll$facetsPhotoperiod = factor(MultiCultiDataAll$WL, labels = c("Photoperiod~(h)"))

MultiCultiDataAll <- MultiCultiDataAll %>% 
    mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA77G"~"PC-rich_077")) 
```

# Create GrowthCurve plot

```{r create GrowthCurve plot, fig.height = 8, fig.width = 8, warning = FALSE}
MultiCultiDataAll %>%
  #Run== 56, 59, 63, 68, 70
  filter(Run==70) %>% 
  ggplot() +
  geom_area(aes(x = Time_h, y = meanActinic_par_h), size = 0.1, fill = "tan1", alpha = 0.6) +
  geom_line(aes(x = Time_h, y = meanOD680_h, colour = as.factor(Strain)), size = 0.5, show.legend = F) +
  scale_colour_discrete(type=c("palegreen3", "brown4"), name="") +
  labs(y = "Optical density ("~OD[680]~")", x = "Elapsed time (h)") +
  ggh4x::facet_nested(cols = vars(WL, Par_ue), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.1,0.95),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=10))
```

# Save plot 

```{r save plot}
ggsave(file = file.path(PlotsPath, paste("GrowthCurve_SupPlot",".png",sep = "")), height=10, width= 8,  dpi = 300, limitsize = TRUE)
```

# Create preliminary plot - loop

```{r create preliminary plot, warning = FALSE}
MultiCultiDataAll %>%
  filter(Run == 70) %>% 
  ggplot() +
  geom_line(aes(x = meanOD720_h, y = meanDeltaOD_h, colour = as.factor(Strain)), size = 0.7, show.legend = T) +
  scale_colour_discrete(type=c("palegreen3", "brown4"), name="") +
  ggh4x::facet_nested(cols = vars(WL, Par_ue), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 
```
# Save plot 

```{r save plot}
ggsave(file = file.path(PlotsPath, paste("GrowthCurve_SupPlot",".png",sep = "")), height=10, width= 8,  dpi = 300, limitsize = TRUE)
```

# Cleaning df before saving as rds and removed unnecessary files from the environment

```{r cleanifng d}
rm(MultiCultiData)
```

# Save Rds that create plots, stats and tables

```{r save rds}
saveRDS(MultiCultiDataAll, file.path(RDSPlotPath, paste(Project, "Plot_GrowthCurve.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Save Rds for further analysis

```{r save rds}
saveRDS(MultiCultiDataAll, file.path(DataOut, paste(Project, "Processed_GrowthCurve.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Variable names used in Data Dictionary

```{r}
colnames(MultiCultiDataAll)
```



