---
title: "Process_PigmentsData"
author:
- Sylwia Sliwinska-Wilczewska
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: BalticPhotoperiod.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

Process_PigmentsData.Rmd processes BalticPhotoperiod_Imported_PigmentsData.Rds from Data/ImportedData/ImportedPigmentsData. This .Rmd generates BalticPhotoperiod_Processed_PigmentAll.Rds and BalticPhotoperiod_Processed_PigmentsExp.Rds (both stored in Data/ProcessedData/ProcessedPigmentsData folder) and one plots (stored in Output/Figures folder).

# Load Libraries and set Project Variables

```{r load libraries} 
library(ggspectra)
library(photobiologyWavebands)
#library(photobiology)
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(strucchange)
library(ggpubr)
library(caret)
library(googledrive)
library(googlesheets4)
library(readxl)
library("patchwork") # merging plots
```

```{r set project variables}
Project <- "BalticO2"
DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedPigmentsData")
DataIn <- file.path("..", "Data", "ImportedData", "ImportedPigmentsData", fsep = .Platform$file.sep)

FigPath <- file.path("..", "Output", "Figures")
FigRdsPath <- file.path("..", "Output", "FiguresRds")
TableRdsPath <- file.path("..", "Output", "TablesRDS")

FileEncode <- "UTF-8" 
Delimiter <- ""
HeaderRows <- 0
```

# List and read files

```{r Exported Rmd only first time in session}
list.files(path = DataIn, pattern = Project, full.names = TRUE)
```

```{r read pigments File}
#df ontained mean OD per day from Multiculti and Abs from Olis spectra for selected nm. Based on this I calculated pigments per mL and per cell (pg/cell)

MCPigmentFile <- "../Data/ImportedData/ImportedPigmentsData/BalticO2_Imported_PigmentsData.Rds"
MCPigmentFileName <- str_split(string = MCPigmentFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")
MCPigment <- readRDS(MCPigmentFile)  %>%
  ungroup()
```

I got a NA in some places b/c I do not measure Olis every day (MC df contain OD for every day and every h but I would like to keep all this data

# Preparing df for further analysis - selected unrevelant columns

```{r Preparing df for further analysis}
MCPigment<-MCPigment %>% 
  # drop_na(MC) %>%
  select(-c(Abs480, Abs565, Abs620, Abs650, Abs665)) %>% 
  unique()
```

# Replace negative values in df to zero when no pigments

```{r Replace negative values, warning=FALSE}
MCPigment <- MCPigment
MCPigment[MCPigment < 0] <- 0
```

# Calculate number of cells per L and PUR/PAR ratio

```{r Calculate pigments per L}
MCPigment <- MCPigment %>%
  mutate(cellL_OD680=cellmL_OD680_MDPico*1000) %>% 
  mutate(PURPARRatio = PUR/Par_ue) %>% 
  
  mutate(Oxygen=case_when(O2==21~"250~µM",
         O2==0~"2.5~µM"))
  # mutate(ChlaugL = ChlaugmL*1000) 
```

# Preparing df for plot

```{r Combine Chla, phyco, and Car in one column for final plot}
MCPigment1<-MCPigment %>% 
  select(-c(Chlapgcell, Carpgcell)) %>% 
  mutate(Pigmentspgcell=Phycopgcell*1) %>% 
  select(-c(Phycopgcell))
MCPigment1$PigmentsName = "Total~phycobilins"

MCPigment2<-MCPigment %>% 
  select(-c(Phycopgcell, Carpgcell)) %>% 
  mutate(Pigmentspgcell=Chlapgcell*1) %>% 
  select(-c(Chlapgcell))
MCPigment2$PigmentsName = "Chlorophyll~italic(a)"

MCPigment3<-MCPigment %>% 
  select(-c(Chlapgcell, Phycopgcell)) %>% 
  mutate(Pigmentspgcell=Carpgcell*1) %>% 
  select(-c(Carpgcell))
MCPigment3$PigmentsName = "Carotenoids"
  
MCPigmentPlot<-rbind(MCPigment1, MCPigment2, MCPigment3)

rm(MCPigment1, MCPigment2, MCPigment3)
```

# I have many measurements per pigment per day (b/c number of cells changes every h so pigments per cell changed as well)
# Choosen only ToD=12 to get only 1 value of pigment (b/c I measured Olis usually at 12pm). 

```{r}
MCPigmentPlot<-MCPigmentPlot %>%
  filter(ToD == 12) %>% 
  unique()
```


# Combine phyco/Chla ratio and car/chla ratio in one column for final plot

```{r Combine phyco/Chla ratio and car/chla ratio in one column for final plot}
MCPigmentRatio1<-MCPigmentPlot %>% 
  select(-c(PhycoChlaRatio)) %>% 
  mutate(PigmentsRatio=CarChlaRatio*1) %>% 
  select(-c(CarChlaRatio))
MCPigmentRatio1$PigmentsRatioName = "Car/Chl~italic(a)~ratio"

MCPigmentRatio2<-MCPigmentPlot %>% 
  select(-c(CarChlaRatio)) %>% 
  mutate(PigmentsRatio=PhycoChlaRatio*1) %>% 
  select(-c(PhycoChlaRatio))
MCPigmentRatio2$PigmentsRatioName = "Total~Phyco/Chl~italic(a)~ratio"

MCPigmentRatioPlot<-rbind(MCPigmentRatio1, MCPigmentRatio2)

rm(MCPigmentRatio1, MCPigmentRatio2)
```


```{r}
MCPigmentRatioPlot<-MCPigmentRatioPlot %>% 
  mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(WL != "WW") %>% 
  mutate(Oxygen=case_when(O2==21~"250~µM",
         O2==0~"2.5~µM"))

MCPigmentPlot<-MCPigmentPlot %>% 
  mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(WL != "WW") %>% 
  mutate(Oxygen=case_when(O2==21~"250~µM",
         O2==0~"2.5~µM"))
```

#Create preliminary plot

```{r preliminary plot}
lab1=c(expression("PC-rich_077"), expression("PE-rich_127"))

MCPigmentRatioPlot %>%
  filter(E_days == 7 | E_days == 8| E_days == 6 | E_days == 5| E_days == 10) %>% 
  ggplot() +
  geom_point(aes(x = WLNum, y = PigmentsRatio, colour = as.factor(Strain), shape = as.factor(Strain)), size = 4, show.legend = T) +
  #geom_line(aes(x = WLNum, y = PigmentsRatio, colour = as.factor(Strain), linetype = as.factor(Strain)), show.legend = F) +
  stat_wl_strip(aes(x = WLNum), ymin = -Inf, ymax = -0.025, alpha = 0.5) +
  scale_fill_identity() +
  scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab1) +
  scale_shape_manual(values = c(16, 18), name="", labels = lab1) +
  scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab1) +
  labs(y = "Pigment ratio", x = "Growth waveband (nm)") +
  ggh4x::facet_nested(cols = vars(factor(PigmentsRatioName, levels=c("Total~Phyco/Chl~italic(a)~ratio","Car/Chl~italic(a)~ratio"))), rows = vars(factor(Oxygen, levels=c("250~µM","2.5~µM"))), labeller = label_parsed) +
  theme_bw() 


MCPigmentPlot %>%
  filter(E_days == 7 | E_days == 8| E_days == 6 | E_days == 5| E_days == 10) %>% 
  ggplot() +
  geom_point(aes(x = WLNum, y = Pigmentspgcell, colour = as.factor(Strain), shape = as.factor(Strain)), size = 4, show.legend = T) +
  #geom_line(aes(x = WLNum, y = Pigmentspgcell, colour = as.factor(Strain), linetype = as.factor(Strain)), show.legend = F) +
  stat_wl_strip(aes(x = WLNum), ymin = -Inf, ymax = -0.025, alpha = 0.5) +
  scale_fill_identity() +
  scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab1) +
  scale_shape_manual(values = c(16, 18), name="", labels = lab1) +
  scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab1) +
  labs(y = "Pigment content " ~ "(pg"~cell^-1~")", x = "Growth waveband (nm)") +
  ggh4x::facet_nested(cols = vars(factor(PigmentsName, levels=c("Chlorophyll~italic(a)","Total~phycobilins", "Carotenoids"))), rows = vars(factor(Oxygen, levels=c("250~µM","2.5~µM"))), labeller = label_parsed) +
  theme_bw() 

```



# Make All big mean to combine all days (from mid exp) and all replica when samples were measured 
(This give me only one value of Phyco/Chla ratio JVPSII plot and sig plot as well)

# meanvalue contains max 5 measurements (5 different days)

```{r calculate Sigma mean from exp phase}
#E_days, Time_h, caused problem

MCPigmentChoosen<-MCPigment %>%
  filter(E_days == 7 | E_days == 8| E_days == 6 | E_days == 5| E_days == 10) %>% 
  #filter(E_days >=5) %>% 
  drop_na(PhycoChlaRatio) %>% 
  group_by(Strain, Par_ue, Photoperiod, WL, O2) %>%

  summarize(SampleID, ToD, Run, Strain, ExpDate, FilenameMC, Tube, Par_ue, Photoperiod, O2, WL, MC, LightShape, ExpEndDate, meanActinic_par_h, meanOD680_h, meanOD720_h, meanDeltaOD_h, facetsPar_ue, facetsPhotoperiod, cellmL_OD680_MDPico, PARPhotonDose_day, PUR, PURPhotonDose_day, ChlaugmL, CarugmL, PEugmL, PCugmL, APCugmL, Chlapgcell, Carpgcell, PEpgcell, PCpgcell, APCpgcell, Phycopgcell, CarChlaRatio, PhycoChlaRatio, PEPCRatio, cellL_OD680, PURPARRatio, E_days, Oxygen,

            
            meanPUR = mean(PUR),
            sdPUR = sd(PUR),
            
            meanChlapgcell = mean(Chlapgcell),
            sdChlapgcell = sd(Chlapgcell),
            meanCarpgcell = mean(Carpgcell),
            sdCarpgcell = sd(Carpgcell),
            meanPhycopgcell = mean(Phycopgcell),
            sdPhycopgcell = sd(Phycopgcell),
            
            meanPhycoChlaRatio = mean(PhycoChlaRatio),
            sdPhycoChlaRatio = sd(PhycoChlaRatio),
            meanCarChlaRatio = mean(CarChlaRatio),
            sdCarChlaRatio = sd(CarChlaRatio),
            
            meancellL_OD680 = mean(cellL_OD680),
            sdcellL_OD680 = sd(cellL_OD680),
            
            meanPURPARRatio = mean(PURPARRatio),
            sdPURPARRatio = sd(PURPARRatio)) %>%
  ungroup()
```

#Create preliminary plot

```{r preliminary plot}
lab1=c(expression("PC-rich_077"), expression("PE-rich_127"))

MCPigmentChoosen %>%
  mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(WL != "WW") %>%
  #filter(E_days == 7 | E_days == 8| E_days == 6 | E_days == 5| E_days == 10) %>% 
  ggplot() +
  geom_point(aes(x = WLNum, y = meanPhycoChlaRatio, colour = as.factor(Strain), shape = as.factor(Strain)),  alpha = 0.8, size = 4, show.legend = T) +
  geom_line(aes(x = WLNum, y = meanPhycoChlaRatio, colour = as.factor(Strain), linetype = as.factor(Strain)), show.legend = F) +
  geom_errorbar(aes(x = WLNum, ymin = meanPhycoChlaRatio - sdPhycoChlaRatio, ymax = meanPhycoChlaRatio + sdPhycoChlaRatio, colour = as.factor(Strain)), width=0, size=0.3, show.legend = F) +
  
  geom_hline(yintercept=1, linetype = "dotted", size = 0.3) +
  
  scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab1) +
  scale_shape_manual(values = c(16, 18), name="", labels = lab1) +
  scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab1) +
  
  stat_wl_strip(aes(x = WLNum), ymin = -Inf, ymax = -0.025, alpha = 0.5) +
  scale_fill_identity() +
  labs(y = "Phycobilin to Chl a ratio (µg:µg)", x = "Growth waveband (nm)") +
  ggh4x::facet_nested(rows = vars(factor(Oxygen, levels=c("250~µM","2.5~µM"))), labeller = label_parsed) +
  theme_bw() 
```
# Save plot 

```{r save plot}
#ggsave(file = file.path(FigPath, paste("Fig_PhycoChla",".png",sep = "")), height=5.5, width= 6,  dpi = 300, limitsize = TRUE)
```

---------------------------------

```{r}
MCPigmentChoosenPlot<-MCPigmentChoosen
```


# Preparing df for pigment per cell plot

```{r Combine Chla, phyco, and Car in one column for final plot}
MCPigment1<-MCPigmentChoosenPlot %>%
  select(-c(meanChlapgcell, meanCarpgcell, sdChlapgcell, sdCarpgcell)) %>%
  mutate(meanPigmentspgcell=meanPhycopgcell*1) %>%
  mutate(sdPigmentspgcell=sdPhycopgcell*1) %>%
  select(-c(meanPhycopgcell, sdPhycopgcell))
MCPigment1$PigmentsName = "Phycobiliproteins"
MCPigment1$PigmentsNamesd = "sdPhycobiliproteins"

MCPigment2<-MCPigmentChoosenPlot %>%
  select(-c(meanPhycopgcell, meanCarpgcell, sdPhycopgcell, sdCarpgcell)) %>%
  mutate(meanPigmentspgcell=meanChlapgcell*1) %>%
  mutate(sdPigmentspgcell=sdChlapgcell*1) %>%
  select(-c(meanChlapgcell, sdChlapgcell))
MCPigment2$PigmentsName = "Chlorophyll~italic(a)"
MCPigment2$PigmentsNamesd = "sdChlorophyll~italic(a)"

MCPigment3<-MCPigmentChoosenPlot %>%
  select(-c(meanChlapgcell, meanPhycopgcell, sdChlapgcell, sdPhycopgcell)) %>%
  mutate(meanPigmentspgcell=meanCarpgcell*1) %>%
  mutate(sdPigmentspgcell=sdCarpgcell*1) %>%
  select(-c(meanCarpgcell, sdCarpgcell))
MCPigment3$PigmentsName = "Carotenoids"
MCPigment3$PigmentsNamesd = "sdCarotenoids"

MCPigmentChoosenPlot<-rbind(MCPigment1, MCPigment2, MCPigment3)

rm(MCPigment1, MCPigment2, MCPigment3)
```


# Combine phyco/Chla ratio and car/chla ratio in one column for final plot

```{r Combine phyco/Chla ratio and car/chla ratio in one column for final plot}
MCPigmentRatio1<-MCPigmentChoosenPlot %>% 
  select(-c(meanPhycoChlaRatio, sdPhycoChlaRatio)) %>% 
  mutate(meanPigmentsRatio=meanCarChlaRatio*1) %>% 
  mutate(sdPigmentsRatio=sdCarChlaRatio*1) %>% 
  select(-c(meanCarChlaRatio, sdCarChlaRatio))
MCPigmentRatio1$PigmentsRatioName = "Carotenoids:Chlorophyll~italic(a)"
MCPigmentRatio1$PigmentsRatioNamesd = "sdCarotenoids:Chlorophyll~italic(a)"

MCPigmentRatio2<-MCPigmentChoosenPlot %>% 
  select(-c(meanCarChlaRatio, sdCarChlaRatio)) %>% 
  mutate(meanPigmentsRatio=meanPhycoChlaRatio*1) %>% 
  mutate(sdPigmentsRatio=sdPhycoChlaRatio*1) %>% 
  select(-c(meanPhycoChlaRatio, sdPhycoChlaRatio))
MCPigmentRatio2$PigmentsRatioName = "Phycobiliproteins:Chlorophyll~italic(a)"
MCPigmentRatio2$PigmentsRatioNamesd = "sdPhycobiliproteins:Chlorophyll~italic(a)"

MCPigmentChoosenPlot<-rbind(MCPigmentRatio1, MCPigmentRatio2)

rm(MCPigmentRatio1, MCPigmentRatio2)
```


```{r}
MCPigmentChoosenPlot<-MCPigmentChoosenPlot %>% 
  mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(WL != "WW") 

```

```{r}
# MCPigmentChoosenPlot<-MCPigmentChoosenPlot %>% 
#   mutate(Strain=case_when(Strain=="PE-rich_127"~"PE-rich",
#          Strain=="PC-rich_077"~"PC-rich"))
```


#Create preliminary plot

```{r preliminary plot}
lab1=c(expression("PC-rich_077"), expression("PE-rich_127"))

MCPigmentChoosenPlot %>%
  filter(E_days == 7 | E_days == 8| E_days == 6 | E_days == 5| E_days == 10) %>% 
  ggplot() +
  geom_point(aes(x = WLNum, y = meanPigmentsRatio, colour = as.factor(Strain), shape = as.factor(Strain)), size = 4, show.legend = T) +
  geom_line(aes(x = WLNum, y = meanPigmentsRatio, colour = as.factor(Strain), linetype = as.factor(Strain)), show.legend = F) +
  
  geom_errorbar(aes(x = WLNum, ymin = meanPigmentsRatio - sdPigmentsRatio, ymax = meanPigmentsRatio + sdPigmentsRatio, colour = as.factor(Strain)), width=0, size=0.3, show.legend = F) +
  
  stat_wl_strip(aes(x = WLNum), ymin = -Inf, ymax = -0.025, alpha = 0.5) +
  scale_fill_identity() +
  scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab1) +
  scale_shape_manual(values = c(16, 18), name="", labels = lab1) +
  scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab1) +
  labs(y = "Pigment ratio (µg:µg)", x = "Growth waveband (nm)") +
  ggh4x::facet_nested(cols = vars(factor(PigmentsRatioName, levels=c("Phycobiliproteins:Chlorophyll~italic(a)","Carotenoids:Chlorophyll~italic(a)"))), rows = vars(factor(Oxygen, levels=c("250~µM","2.5~µM"))), labeller = label_parsed) +
  theme_bw() 


MCPigmentChoosenPlot %>%
  filter(E_days == 7 | E_days == 8| E_days == 6 | E_days == 5| E_days == 10) %>% 
  ggplot() +
  geom_point(aes(x = WLNum, y = meanPigmentspgcell, colour = as.factor(Strain), shape = as.factor(Strain)), size = 4, show.legend = T) +
  geom_line(aes(x = WLNum, y = meanPigmentspgcell, colour = as.factor(Strain), linetype = as.factor(Strain)), show.legend = F) +
  
  geom_errorbar(aes(x = WLNum, ymin = meanPigmentspgcell - sdPigmentspgcell, ymax = meanPigmentspgcell + sdPigmentspgcell, colour = as.factor(Strain)), width=0, size=0.3, show.legend = F) +
  
  stat_wl_strip(aes(x = WLNum), ymin = -Inf, ymax = 0.000, alpha = 0.5) +
  scale_fill_identity() +
  scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab1) +
  scale_shape_manual(values = c(16, 18), name="", labels = lab1) +
  scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab1) +
  labs(y = "Pigment content " ~ "(pg"~cell^-1~")", x = "Growth waveband (nm)") +
  ggh4x::facet_nested(cols = vars(factor(PigmentsName, levels=c("Chlorophyll~italic(a)","Phycobiliproteins", "Carotenoids"))), rows = vars(factor(Oxygen, levels=c("250~µM","2.5~µM"))), labeller = label_parsed) +
  theme_bw() 

```
#Create preliminary plot

```{r preliminary plot}
lab1=c(expression("PC-rich"), expression("PE-rich"))
lab2=c(expression("2.5 µM"), expression("250 µM"))


A<-MCPigmentChoosenPlot %>%
  filter(E_days == 7 | E_days == 8| E_days == 6 | E_days == 5| E_days == 10) %>% 
  ggplot() +
  geom_point(aes(x = WLNum, y = meanPigmentsRatio, colour = as.factor(Strain)), size = 4, show.legend = F) +
  geom_line(aes(x = WLNum, y = meanPigmentsRatio, linetype = as.factor(O2)), show.legend = T) +
  
  geom_errorbar(aes(x = WLNum, ymin = meanPigmentsRatio - sdPigmentsRatio, ymax = meanPigmentsRatio + sdPigmentsRatio, colour = as.factor(Strain)), width=0, size=0.3, show.legend = F) +
  
  stat_wl_strip(aes(x = WLNum), ymin = -Inf, ymax = -0.025, alpha = 0.5) +
  scale_fill_identity() +
  scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab2) +
  scale_shape_manual(values = c(16, 18), name="", labels = lab2) +
  scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab2) +
  labs(y = "Pigment ratio (µg:µg)", x = "Growth waveband (nm)") +
  ggh4x::facet_nested(cols = vars(factor(PigmentsRatioName, levels=c("Phycobiliproteins:Chlorophyll~italic(a)","Carotenoids:Chlorophyll~italic(a)"))), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        panel.spacing.x = unit(0.4, 'cm'),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.position = c(0.10,0.90),
        legend.text = element_text(size=10))
A

B<-MCPigmentChoosenPlot %>%
  filter(E_days == 7 | E_days == 8| E_days == 6 | E_days == 5| E_days == 10) %>% 
  ggplot() +
  geom_point(aes(x = WLNum, y = meanPigmentspgcell, colour = as.factor(Strain)), size = 4, show.legend = F) +
  geom_line(aes(x = WLNum, y = meanPigmentspgcell, linetype = as.factor(O2)), show.legend = T) +
  
  geom_errorbar(aes(x = WLNum, ymin = meanPigmentspgcell - sdPigmentspgcell, ymax = meanPigmentspgcell + sdPigmentspgcell, colour = as.factor(Strain)), width=0, size=0.3, show.legend = F) +
  
  stat_wl_strip(aes(x = WLNum), ymin = -Inf, ymax = 0.000, alpha = 0.5) +
  scale_fill_identity() +
  scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab2) +
  scale_shape_manual(values = c(16, 18), name="", labels = lab2) +
  scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab2) +
  labs(y = "Pigment content " ~ "(pg"~cell^-1~")", x = "Growth waveband (nm)") +
  ggh4x::facet_nested(cols = vars(factor(PigmentsName, levels=c("Chlorophyll~italic(a)","Phycobiliproteins", "Carotenoids"))), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        panel.spacing.x = unit(0.4, 'cm'),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.position = c(0.10,0.90),
        legend.text = element_text(size=10))
B
```

```{r fig.height = 6, fig.width = 6, warning = FALSE}
ggp<- B/A
ggp  
```


# Save plot 

```{r save plot}
#ggsave(file = file.path(FigPath, paste("Fig_Pigment",".png",sep = "")), height=9, width= 7,  dpi = 300, limitsize = TRUE)
```


------------------------------# Support Vector regression---------------------------------------------------

https://www.geeksforgeeks.org/support-vector-regression-svr-using-linear-and-non-linear-kernels-in-scikit-learn/

https://minimatech.org/non-linear-regression-with-r/

# Support Vector regression

```{r libraries}

# library(zoo)
# library(e1071)
# library(gcookbook)  # Load gcookbook for the uspopage data set

```

```{r}
# MCDataHourSVRRatio <- MCPigmentChoosenPlot 
# 
# # Function to train an SVM model and make predictions
# train_and_predict_svm <- function(data) {
#   svr_model <- svm(meanPigmentsRatio ~ WLNum, data = data, kernel = 'radial',
#                    cost = 5, gamma = 0.5)
#   data$svr_pred <- predict(svr_model, data)
#   return(data)
# }
# 
# # Group by Tube, train SVM model, and make predictions within each group
# MCDataHourSVRRatio <- MCDataHourSVRRatio %>%
#   group_by(Strain, O2, Oxygen, PigmentsRatioName) %>%
#   nest() %>%
#   mutate(data = map(data, train_and_predict_svm)) %>%
#   unnest(data) %>%
#   ungroup()
# 
# # Calculate the root mean squared error for each group
# RMSE_by_TubeRatio <- MCDataHourSVRRatio %>%
#   group_by(Strain, O2, Oxygen, PigmentsRatioName) %>%
#   summarise(RMSE = sqrt(mean((meanPigmentsRatio - svr_pred)^2)))
# 
# 
# 
# 
# MCDataHourSVRPig <- MCPigmentChoosenPlot 
# 
# # Function to train an SVM model and make predictions
# train_and_predict_svm <- function(data) {
#   svr_model <- svm(meanPigmentspgcell ~ WLNum, data = data, kernel = 'radial',
#                    cost = 5, gamma = 0.5)
#   data$svr_pred <- predict(svr_model, data)
#   return(data)
# }
# 
# # Group by Tube, train SVM model, and make predictions within each group
# MCDataHourSVRPig <- MCDataHourSVRPig %>%
#   group_by(Strain, O2, Oxygen, PigmentsName) %>%
#   nest() %>%
#   mutate(data = map(data, train_and_predict_svm)) %>%
#   unnest(data) %>%
#   ungroup()
# 
# # Calculate the root mean squared error for each group
# RMSE_by_TubePig <- MCDataHourSVRPig %>%
#   group_by(Strain, O2, Oxygen, PigmentsName) %>%
#   summarise(RMSE = sqrt(mean((meanPigmentspgcell - svr_pred)^2)))


```


#Create preliminary plot

```{r preliminary plot}
# lab1=c(expression("PC-rich"), expression("PE-rich"))
# lab2=c(expression("2.5 µM"), expression("250 µM"))
# 
# data_textA <- data.frame(PigmentsName  = c("Carotenoids"), Strain  = c("PC-rich"), label = c('italic(a)'))
# data_textB <- data.frame(PigmentsRatioName  = c("Carotenoids:Chlorophyll~italic(a)"), Strain  = c("PC-rich"), label = c('italic(b)'))
# 
# MultiCultiGrowth1PC21<-MCPigmentChoosenPlot %>% 
#     mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
#   filter(WL != "WW") %>%
#   filter(E_days == 7 | E_days == 8| E_days == 6 | E_days == 5| E_days == 10) %>% 
#   filter(Strain == "PC-rich") %>% 
#   filter(O2 == 21)
# MultiCultiGrowth1PE21<-MCPigmentChoosenPlot %>% 
#     mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
#   filter(WL != "WW") %>%
#   filter(E_days == 7 | E_days == 8| E_days == 6 | E_days == 5| E_days == 10) %>% 
#   filter(Strain == "PE-rich") %>% 
#     filter(O2 == 21)
#   
# MultiCultiGrowth1PC0<-MCPigmentChoosenPlot %>% 
#     mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
#   filter(WL != "WW") %>%
#   filter(E_days == 7 | E_days == 8| E_days == 6 | E_days == 5| E_days == 10) %>% 
#   filter(Strain == "PC-rich") %>% 
#   filter(O2 == 0)
# MultiCultiGrowth1PE0<-MCPigmentChoosenPlot %>% 
#     mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
#   filter(WL != "WW") %>%
#   filter(E_days == 7 | E_days == 8| E_days == 6 | E_days == 5| E_days == 10) %>% 
#   filter(Strain == "PE-rich") %>% 
#     filter(O2 == 0)
# 
# 
# MCPigmentChoosenPlot %>%
#   filter(E_days == 7 | E_days == 8| E_days == 6 | E_days == 5| E_days == 10) %>% 
#   ggplot() +
#   geom_point(aes(x = WLNum, y = meanPigmentspgcell, shape = as.factor(O2)), size = 4, show.legend = T) +
#   #geom_line(aes(x = WLNum, y = meanPigmentspgcell, linetype = as.factor(O2)), show.legend = T) +
#   
#     geom_point(aes(x = WLNum, y = meanPigmentspgcell), colour = "palegreen3", shape = 1, size = 4, show.legend = F, MultiCultiGrowth1PC21) +
#     geom_point(aes(x = WLNum, y = meanPigmentspgcell), colour = "brown4", shape = 1, size = 4, show.legend = F, MultiCultiGrowth1PE21) +
#     geom_point(aes(x = WLNum, y = meanPigmentspgcell), colour = "palegreen3", shape = 16, size = 4, show.legend = F, MultiCultiGrowth1PC0) +
#     geom_point(aes(x = WLNum, y = meanPigmentspgcell), colour = "brown4", shape = 16, size = 4, show.legend = F, MultiCultiGrowth1PE0) +
#   
#   geom_line(aes(x = WLNum, y = svr_pred, linetype = as.factor(O2)), size = 0.6, show.legend = T, MCDataHourSVRPig) +
#   
#   geom_errorbar(aes(x = WLNum, ymin = meanPigmentspgcell - sdPigmentspgcell, ymax = meanPigmentspgcell + sdPigmentspgcell, colour = as.factor(Strain)), width=0, size=0.3, show.legend = F) +
#   geom_text(data=data_textA, aes(x=700, y=0.1, label=label), size=6, parse = TRUE) +
#   stat_wl_strip(aes(x = WLNum), ymin = -Inf, ymax = 0.000, alpha = 0.5) +
#   scale_fill_identity() +
#   scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab2) +
#   scale_shape_manual(values = c(16, 1), name="", labels = lab2) +
#   scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab2) +
#   labs(y = "Pigment content " ~ "(pg"~cell^-1~")", x = "Growth waveband (nm)") +
#   ggh4x::facet_nested(cols = vars(factor(PigmentsName, levels=c("Chlorophyll~italic(a)","Phycobiliproteins", "Carotenoids"))), rows = vars(Strain), labeller = label_parsed) +
#   theme_bw()
# 
# 
# 
# MCPigmentChoosenPlot %>%
#   filter(E_days == 7 | E_days == 8| E_days == 6 | E_days == 5| E_days == 10) %>% 
#   ggplot() +
#   geom_point(aes(x = WLNum, y = meanPigmentsRatio, shape = as.factor(O2)), size = 4, show.legend = F) +
#   #geom_line(aes(x = WLNum, y = meanPigmentsRatio, linetype = as.factor(O2)), show.legend = T) +
#   
#     geom_point(aes(x = WLNum, y = meanPigmentsRatio), colour = "palegreen3", shape = 1, size = 4, show.legend = F, MultiCultiGrowth1PC21) +
#     geom_point(aes(x = WLNum, y = meanPigmentsRatio), colour = "brown4", shape = 1, size = 4, show.legend = F, MultiCultiGrowth1PE21) +
#     geom_point(aes(x = WLNum, y = meanPigmentsRatio), colour = "palegreen3", shape = 16, size = 4, show.legend = F, MultiCultiGrowth1PC0) +
#     geom_point(aes(x = WLNum, y = meanPigmentsRatio), colour = "brown4", shape = 16, size = 4, show.legend = F, MultiCultiGrowth1PE0) +
#   
#   
#   geom_line(aes(x = WLNum, y = svr_pred, linetype = as.factor(O2)), size = 0.6, show.legend = F, MCDataHourSVRRatio) +
#   
#   geom_errorbar(aes(x = WLNum, ymin = meanPigmentsRatio - sdPigmentsRatio, ymax = meanPigmentsRatio + sdPigmentsRatio, colour = as.factor(Strain)), width=0, size=0.3, show.legend = F) +
#   geom_text(data=data_textB, aes(x=720, y=4, label=label), size=6, parse = TRUE) +
#   stat_wl_strip(aes(x = WLNum), ymin = -Inf, ymax = -0.025, alpha = 0.5) +
#   scale_fill_identity() +
#   scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab2) +
#   scale_shape_manual(values = c(16, 1), name="", labels = lab2) +
#   scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab2) +
#   labs(y = "Pigment ratio (µg:µg)", x = "Growth waveband (nm)") +
#   ggh4x::facet_nested(cols = vars(factor(PigmentsRatioName, levels=c("Phycobiliproteins:Chlorophyll~italic(a)","Carotenoids:Chlorophyll~italic(a)"))), rows = vars(Strain), labeller = label_parsed) +
#   theme_bw() 
# 

```



# Save plot 

```{r save plot}
#ggsave(file = file.path(FigPath, paste("Fig_Pigment",".png",sep = "")), height=9, width= 7,  dpi = 300, limitsize = TRUE)
```


```{r}
lab1=c(expression("PC-rich"), expression("PE-rich"))
lab2=c(expression("2.5 µM"), expression("250 µM"))
lab3=c(expression("405"), expression("450"), expression("470"), expression("530"), expression("620"), expression("660"), expression("730"))




MCPigmentChoosenPlot %>%
  filter(E_days == 7 | E_days == 8| E_days == 6 | E_days == 5| E_days == 10) %>% 
  ggplot() +
  geom_point(aes(x = meanPUR, y = meanPigmentsRatio, shape = as.factor(O2), colour = as.factor(WL)), size = 4, show.legend = T) +
  #geom_line(aes(x = PUR, y = meanPigmentsRatio, linetype = as.factor(O2)), show.legend = T) +
  
    # geom_point(aes(x = WLNum, y = meanPigmentsRatio), colour = "palegreen3", shape = 1, size = 4, show.legend = F, MultiCultiGrowth1PC21) +
    # geom_point(aes(x = WLNum, y = meanPigmentsRatio), colour = "brown4", shape = 1, size = 4, show.legend = F, MultiCultiGrowth1PE21) +
    # geom_point(aes(x = WLNum, y = meanPigmentsRatio), colour = "palegreen3", shape = 16, size = 4, show.legend = F, MultiCultiGrowth1PC0) +
    # geom_point(aes(x = WLNum, y = meanPigmentsRatio), colour = "brown4", shape = 16, size = 4, show.legend = F, MultiCultiGrowth1PE0) +
    # 
  
  #geom_line(aes(x = WLNum, y = svr_pred, linetype = as.factor(O2)), size = 0.6, show.legend = F, MCDataHourSVRRatio) +
  
  geom_errorbar(aes(x = meanPUR, ymin = meanPigmentsRatio - sdPigmentsRatio, ymax = meanPigmentsRatio + sdPigmentsRatio), width=0, size=0.3, show.legend = F) +
  #geom_text(data=data_textB, aes(x=720, y=4, label=label), size=6, parse = TRUE) +
  # stat_wl_strip(aes(x = WLNum), ymin = -Inf, ymax = -0.025, alpha = 0.5) +
  # scale_fill_identity() +
  
    scale_colour_manual(values = c("royalblue4", "steelblue3", "lightseagreen", "limegreen", "coral","brown1","indianred4"), name="", labels = lab3) +
  #scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab2) +
  
  
  scale_shape_manual(values = c(16, 1), name="", labels = lab2) +
  scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab2) +
  #labs(y = "Pigment ratio (µg:µg)", x = "Growth waveband (nm)") +
  ggh4x::facet_nested(cols = vars(factor(PigmentsRatioName, levels=c("Phycobiliproteins:Chlorophyll~italic(a)","Carotenoids:Chlorophyll~italic(a)"))), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 


```

# Save plot 

```{r save plot}
#ggsave(file = file.path(FigPath, paste("Fig_PigmentvsPUR",".png",sep = "")), height=5, width= 6,  dpi = 300, limitsize = TRUE)
```


------------------------------ Trim no growt data ------------------------------

# Filter condition where no growt

```{r}
SolFitsMetaLightCorr445590Trim1<-MCPigmentChoosenPlot %>% 
  filter(Strain == "PC-rich") %>% 
  filter(O2 == 21) %>% 
  filter(WL != 405) 

SolFitsMetaLightCorr445590Trim3<-MCPigmentChoosenPlot %>% 
  filter(Strain == "PC-rich") %>% 
  filter(O2 == 0) 

SolFitsMetaLightCorr445590Trim4<-MCPigmentChoosenPlot %>% 
  filter(Strain == "PE-rich") %>% 
  filter(O2 == 21) %>% 
  filter(WL != 405) %>% 
  filter(WL != 450) %>% 
  filter(WL != 730) 
  
SolFitsMetaLightCorr445590Trim5<-MCPigmentChoosenPlot %>% 
  filter(Strain == "PE-rich") %>% 
  filter(O2 == 0) 


MCPigmentChoosenPlotTrim<-rbind(SolFitsMetaLightCorr445590Trim1, SolFitsMetaLightCorr445590Trim3, SolFitsMetaLightCorr445590Trim4, SolFitsMetaLightCorr445590Trim5)

rm(SolFitsMetaLightCorr445590Trim1, SolFitsMetaLightCorr445590Trim3, SolFitsMetaLightCorr445590Trim4, SolFitsMetaLightCorr445590Trim5)
```

```{r}
lab1=c(expression("PC-rich"), expression("PE-rich"))
lab2=c(expression("2.5 µM"), expression("250 µM"))
lab3=c(expression("405"), expression("450"), expression("470"), expression("530"), expression("620"), expression("660"), expression("730"))

data_textA <- data.frame(Strain  = c("PC-rich"), label = c('italic(a)'))

MultiCultiGrowth1PC21<-MCPigmentChoosenPlotTrim %>% 
    filter(PigmentsRatioName!= "Carotenoids:Chlorophyll~italic(a)") %>% 
  filter(E_days == 7 | E_days == 8| E_days == 6 | E_days == 5| E_days == 10) %>% 
  filter(Strain == "PC-rich") %>% 
  filter(O2 == 21)
MultiCultiGrowth1PE21<-MCPigmentChoosenPlotTrim %>% 
    filter(PigmentsRatioName!= "Carotenoids:Chlorophyll~italic(a)") %>% 
  filter(E_days == 7 | E_days == 8| E_days == 6 | E_days == 5| E_days == 10) %>% 
  filter(Strain == "PE-rich") %>% 
    filter(O2 == 21)
  
MultiCultiGrowth1PC0<-MCPigmentChoosenPlotTrim %>% 
    filter(PigmentsRatioName!= "Carotenoids:Chlorophyll~italic(a)") %>% 
  filter(E_days == 7 | E_days == 8| E_days == 6 | E_days == 5| E_days == 10) %>% 
  filter(Strain == "PC-rich") %>% 
  filter(O2 == 0)
MultiCultiGrowth1PE0<-MCPigmentChoosenPlotTrim %>% 
    filter(PigmentsRatioName!= "Carotenoids:Chlorophyll~italic(a)") %>% 
  filter(E_days == 7 | E_days == 8| E_days == 6 | E_days == 5| E_days == 10) %>% 
  filter(Strain == "PE-rich") %>% 
    filter(O2 == 0)



PigRatioPUR<-MCPigmentChoosenPlotTrim %>%
  filter(PigmentsRatioName!= "Carotenoids:Chlorophyll~italic(a)") %>% 
  filter(E_days == 7 | E_days == 8| E_days == 6 | E_days == 5| E_days == 10) %>% 
  ggplot() +
  geom_point(aes(x = meanPUR, y = meanPigmentsRatio, shape = as.factor(O2)), size = 4, show.legend = T) +
  geom_smooth(aes(x = meanPUR, y = meanPigmentsRatio, linetype = as.factor(O2)), alpha = 0, size = 1, method = "lm", show.legend = F) +

    geom_point(aes(x = meanPUR, y = meanPigmentsRatio), colour = "palegreen3", shape = 1, size = 4, show.legend = F, MultiCultiGrowth1PC21) +
    geom_point(aes(x = meanPUR, y = meanPigmentsRatio), colour = "brown4", shape = 1, size = 4, show.legend = F, MultiCultiGrowth1PE21) +
    geom_point(aes(x = meanPUR, y = meanPigmentsRatio), colour = "palegreen3", shape = 16, size = 4, show.legend = F, MultiCultiGrowth1PC0) +
    geom_point(aes(x = meanPUR, y = meanPigmentsRatio), colour = "brown4", shape = 16, size = 4, show.legend = F, MultiCultiGrowth1PE0) +

  geom_errorbar(aes(x = meanPUR, ymin = meanPigmentsRatio - sdPigmentsRatio, ymax = meanPigmentsRatio + sdPigmentsRatio, colour = as.factor(Strain)), width=0, size=0.3, show.legend = F) +

  geom_text(data=data_textA, aes(x=180, y=5.5, label=label), size=6, parse = TRUE) +
  
  scale_x_continuous(breaks=seq(0, 180, by = 40)) +
  scale_y_continuous(breaks=seq(0, 6, by = 1)) +
  coord_cartesian(xlim = c (0, 180), ylim = c (0, 6)) +
  
  #scale_colour_manual(values = c("royalblue4", "steelblue3", "lightseagreen", "limegreen", "coral","brown1","indianred4"), name="", labels = lab3) +
  scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab1) +
  scale_shape_manual(values = c(16, 1), name="", labels = lab2) +
  scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab2) +
  labs(y = "Pigment ratio (µg:µg)", x = "PUR ( µmol photons "~m^-2~""~s^-1~")") +
  ggh4x::facet_nested(rows = vars(Strain), labeller = label_parsed) +

  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        panel.spacing.x = unit(0.4, 'cm'),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.position = c(0.10,0.99),
        legend.text = element_text(size=10))
PigRatioPUR

```
#Create preliminary plot

```{r preliminary plot}
lab1=c(expression("PC-rich"), expression("PE-rich"))
lab2=c(expression("2.5 µM"), expression("250 µM"))

data_textA <- data.frame(PigmentsName  = c("Carotenoids"), Strain  = c("PC-rich"), label = c('italic(a)'))

# data_textB <- data.frame(PigmentsRatioName  = c("Phycobilins:Chlorophyll~italic(a)"), Strain  = c("PC-rich"), label = c('italic(a)'))

MultiCultiGrowth1PC21<-MCPigmentChoosenPlotTrim %>% 
    mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(WL != "WW") %>%
  filter(E_days == 7 | E_days == 8| E_days == 6 | E_days == 5| E_days == 10) %>% 
  filter(Strain == "PC-rich") %>% 
  filter(O2 == 21)
MultiCultiGrowth1PE21<-MCPigmentChoosenPlotTrim %>% 
    mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(WL != "WW") %>%
  filter(E_days == 7 | E_days == 8| E_days == 6 | E_days == 5| E_days == 10) %>% 
  filter(Strain == "PE-rich") %>% 
    filter(O2 == 21)
  
MultiCultiGrowth1PC0<-MCPigmentChoosenPlotTrim %>% 
    mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(WL != "WW") %>%
  filter(E_days == 7 | E_days == 8| E_days == 6 | E_days == 5| E_days == 10) %>% 
  filter(Strain == "PC-rich") %>% 
  filter(O2 == 0)
MultiCultiGrowth1PE0<-MCPigmentChoosenPlotTrim %>% 
    mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(WL != "WW") %>%
  filter(E_days == 7 | E_days == 8| E_days == 6 | E_days == 5| E_days == 10) %>% 
  filter(Strain == "PE-rich") %>% 
    filter(O2 == 0)


PigPlot<-MCPigmentChoosenPlotTrim %>%
  filter(E_days == 7 | E_days == 8| E_days == 6 | E_days == 5| E_days == 10) %>% 
  ggplot() +
  geom_point(aes(x = WLNum, y = meanPigmentspgcell, shape = as.factor(O2)), size = 4, show.legend = T) +
  #geom_line(aes(x = WLNum, y = meanPigmentspgcell, linetype = as.factor(O2)), show.legend = T) +
  
    geom_point(aes(x = WLNum, y = meanPigmentspgcell), colour = "palegreen3", shape = 1, size = 4, show.legend = F, MultiCultiGrowth1PC21) +
    geom_point(aes(x = WLNum, y = meanPigmentspgcell), colour = "brown4", shape = 1, size = 4, show.legend = F, MultiCultiGrowth1PE21) +
    geom_point(aes(x = WLNum, y = meanPigmentspgcell), colour = "palegreen3", shape = 16, size = 4, show.legend = F, MultiCultiGrowth1PC0) +
    geom_point(aes(x = WLNum, y = meanPigmentspgcell), colour = "brown4", shape = 16, size = 4, show.legend = F, MultiCultiGrowth1PE0) +
  
  geom_line(aes(x = WLNum, y = meanPigmentspgcell, linetype = as.factor(O2)), size = 0.6, show.legend = T) +
  #geom_line(aes(x = WLNum, y = svr_pred, linetype = as.factor(O2)), size = 0.6, show.legend = T, MCDataHourSVRPig) +
  
  geom_errorbar(aes(x = WLNum, ymin = meanPigmentspgcell - sdPigmentspgcell, ymax = meanPigmentspgcell + sdPigmentspgcell, colour = as.factor(Strain)), width=0, size=0.3, show.legend = F) +
  geom_text(data=data_textA, aes(x=700, y=0.12, label=label), size=6, parse = TRUE) +
  stat_wl_strip(aes(x = WLNum), ymin = -Inf, ymax = 0.000, alpha = 0.5) +
  scale_fill_identity() +
  scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab2) +
  scale_shape_manual(values = c(16, 1), name="", labels = lab2) +
  scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab2) +
  labs(y = "Pigment content " ~ "(pg"~cell^-1~")", x = "Growth waveband (nm)") +
  ggh4x::facet_nested(cols = vars(factor(PigmentsName, levels=c("Chlorophyll~italic(a)","Phycobiliproteins", "Carotenoids"))), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        panel.spacing.x = unit(0.4, 'cm'),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.position = c(0.10,0.90),
        legend.text = element_text(size=10))
PigPlot


```
```{r}
lab1=c(expression("PC-rich"), expression("PE-rich"))
lab2=c(expression("2.5 µM"), expression("250 µM"))

data_textA <- data.frame(PigmentsName  = c("Carotenoids"), Strain  = c("PC-rich"), label = c('italic(a)'))

# data_textB <- data.frame(PigmentsRatioName  = c("Phycobilins:Chlorophyll~italic(a)"), Strain  = c("PC-rich"), label = c('italic(a)'))

MCPigmentChoosenPlotTrim %>%
  filter(E_days == 7 | E_days == 8| E_days == 6 | E_days == 5| E_days == 10) %>% 
  ggplot() +
  geom_point(aes(x = WLNum, y = meanPigmentsRatio, shape = as.factor(O2)), size = 4, show.legend = F) +
  #geom_line(aes(x = WLNum, y = meanPigmentsRatio, linetype = as.factor(O2)), show.legend = T) +
  
    geom_point(aes(x = WLNum, y = meanPigmentsRatio), colour = "palegreen3", shape = 1, size = 4, show.legend = F, MultiCultiGrowth1PC21) +
    geom_point(aes(x = WLNum, y = meanPigmentsRatio), colour = "brown4", shape = 1, size = 4, show.legend = F, MultiCultiGrowth1PE21) +
    geom_point(aes(x = WLNum, y = meanPigmentsRatio), colour = "palegreen3", shape = 16, size = 4, show.legend = F, MultiCultiGrowth1PC0) +
    geom_point(aes(x = WLNum, y = meanPigmentsRatio), colour = "brown4", shape = 16, size = 4, show.legend = F, MultiCultiGrowth1PE0) +
  
    geom_line(aes(x = WLNum, y = meanPigmentsRatio, linetype = as.factor(O2)), size = 0.6, show.legend = F) +
  #geom_line(aes(x = WLNum, y = svr_pred, linetype = as.factor(O2)), size = 0.6, show.legend = F, MCDataHourSVRRatio) +
  
  geom_errorbar(aes(x = WLNum, ymin = meanPigmentsRatio - sdPigmentsRatio, ymax = meanPigmentsRatio + sdPigmentsRatio, colour = as.factor(Strain)), width=0, size=0.3, show.legend = F) +
  #geom_text(data=data_textB, aes(x=720, y=4, label=label), size=6, parse = TRUE) +
  stat_wl_strip(aes(x = WLNum), ymin = -Inf, ymax = -0.025, alpha = 0.5) +
  scale_fill_identity() +
  scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab2) +
  scale_shape_manual(values = c(16, 1), name="", labels = lab2) +
  scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab2) +
  labs(y = "Pigment ratio (µg:µg)", x = "Growth waveband (nm)") +
  ggh4x::facet_nested(cols = vars(factor(PigmentsRatioName, levels=c("Phycobiliproteins:Chlorophyll~italic(a)","Carotenoids:Chlorophyll~italic(a)"))), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        panel.spacing.x = unit(0.4, 'cm'),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.position = c(0.10,0.90),
        legend.text = element_text(size=10))
```
# Save plot 

```{r save plot}
#ggsave(file = file.path(FigPath, paste("SFig_PigmentRatio",".png",sep = "")), height=5, width= 6,  dpi = 300, limitsize = TRUE)
```



```{r fig.height = 7, fig.width = 6, warning = FALSE}
ggp<- PigRatioPUR/GrowthPURPlot
ggp

```

# Save plot 

```{r save plot}
ggsave(file = file.path(FigPath, paste("SFig_GrowthPUR",".png",sep = "")), height=9, width= 7,  dpi = 300, limitsize = TRUE)
```



```{r fig.height = 8, fig.width = 8, warning = FALSE}
ggp<- PigPlot/FigGrowthPig
ggp  
```

# Save plot 

```{r save plot}
ggsave(file = file.path(FigPath, paste("Fig_GrowthPig",".png",sep = "")), height=8, width= 6,  dpi = 300, limitsize = TRUE)
```


----------------------------------------------- ANOVA ------------------------------------

------------------------------ Trim no growt data ------------------------------

# Filter condition where no growt

```{r}
SolFitsMetaLightCorr445590Trim1<-MCPigmentChoosen %>% 
  filter(Strain == "PC-rich") %>% 
  filter(O2 == 21) %>% 
  filter(WL != 405) 

SolFitsMetaLightCorr445590Trim3<-MCPigmentChoosen %>% 
  filter(Strain == "PC-rich") %>% 
  filter(O2 == 0) 

SolFitsMetaLightCorr445590Trim4<-MCPigmentChoosen %>% 
  filter(Strain == "PE-rich") %>% 
  filter(O2 == 21) %>% 
  filter(WL != 405) %>% 
  filter(WL != 450) %>% 
  filter(WL != 730) 
  
SolFitsMetaLightCorr445590Trim5<-MCPigmentChoosen %>% 
  filter(Strain == "PE-rich") %>% 
  filter(O2 == 0) 


MCPigmentChoosenTrim<-rbind(SolFitsMetaLightCorr445590Trim1, SolFitsMetaLightCorr445590Trim3, SolFitsMetaLightCorr445590Trim4, SolFitsMetaLightCorr445590Trim5)

rm(SolFitsMetaLightCorr445590Trim1, SolFitsMetaLightCorr445590Trim3, SolFitsMetaLightCorr445590Trim4, SolFitsMetaLightCorr445590Trim5)
```






  ggh4x::facet_nested(cols = vars(factor(PigmentsName, levels=c("Chlorophyll~italic(a)","Phycobiliproteins", "Carotenoids"))), rows = vars(Strain), labeller = label_parsed) +

  
# Calculated Anova and Tukey test

Pig
```{r calculated statistics}
Stat<-MCPigmentChoosenTrim %>% 
  filter(E_days == 7 | E_days == 8| E_days == 6 | E_days == 5| E_days == 10) 
  #filter(PigmentsName=="Chlorophyll~italic(a)")
Stat$O2 <- factor(Stat$O2)
Stat$WL <- factor(Stat$WL)
Stat$Strain <- factor(Stat$Strain)
# Three way Anova with interactions
model<-aov(Chlapgcell~O2*WL*Strain, data=Stat)
AnovaTest_Chla<-data.frame(unclass(summary(model)), check.names = FALSE, stringsAsFactors = FALSE)
AnovaTest_Chla$Pigments<-"Chla"

Stat<-MCPigmentChoosenTrim %>% 
  filter(E_days == 7 | E_days == 8| E_days == 6 | E_days == 5| E_days == 10) 
  #filter(PigmentsName=="Phycobiliproteins")
Stat$O2 <- factor(Stat$O2)
Stat$WL <- factor(Stat$WL)
Stat$Strain <- factor(Stat$Strain)
# Three way Anova with interactions
model<-aov(Phycopgcell~O2*WL*Strain, data=Stat)
AnovaTest_Phyco<-data.frame(unclass(summary(model)), check.names = FALSE, stringsAsFactors = FALSE)
AnovaTest_Phyco$Pigments<-"Phyco"

Stat<-MCPigmentChoosenTrim %>% 
  filter(E_days == 7 | E_days == 8| E_days == 6 | E_days == 5| E_days == 10) 
  #filter(PigmentsName=="Carotenoids")
Stat$O2 <- factor(Stat$O2)
Stat$WL <- factor(Stat$WL)
Stat$Strain <- factor(Stat$Strain)
# Three way Anova with interactions
model<-aov(Carpgcell~O2*WL*Strain, data=Stat)
AnovaTest_Car<-data.frame(unclass(summary(model)), check.names = FALSE, stringsAsFactors = FALSE)
AnovaTest_Car$Pigments<-"Car"

AnovaPigments<-rbind(AnovaTest_Chla, AnovaTest_Phyco, AnovaTest_Car)
rm(AnovaTest_Chla, AnovaTest_Phyco, AnovaTest_Car)
```

# Save RDS that create stats and tables

```{r}
saveRDS(AnovaPigments, file.path(TableRdsPath, paste(Project, "Anova_Pig.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

```








# Save rds for further analysis

```{r save rds}
saveRDS(MCPigmentChoosen, file.path(DataOut, paste(Project, "Processed_Pigments.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

```


# Variable names used in Data Dictionary

```{r}
colnames(MCPigmentChoosen)
```





