---
title: "Process_OlisJazEmData"
author:
- Sylwia Sliwinska-Wilczewska
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: BalticPhotoperiod.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

Process_OlisJazEmData.Rmd processes and combines Baltic_Photoperiod_Imported_JazEmData.Rds from Data/ImportedData/ImportedJazEmData folder and Baltic_Photoperiod_Imported_OlisData.Rds from Data/ImportedData/ImportedOlisData folder. This .Rmd generates Baltic_Photoperiod_Processed_OlisSpectraAll.Rds and Baltic_Photoperiod_Processed_OlisSpectraTidy.Rds (both stored in Data/ProcessedData/ProcessedOlisJazData folder) and OlisSpectra_Plot.png (stored in Output/Plots folder).

# Load Libraries and set Project Variables

```{r load libraries, warning = FALSE, echo=FALSE} 
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(strucchange)
library(ggspectra)
library(ggpubr)
library(caret)
library(photobiologyWavebands)
library(reshape2)
library(photobiology)
library(gcookbook)
```

```{r set project variables}
Project <- "BalticO2"
DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedOlisJazData")
DataInOlis <- file.path("..", "Data", "ImportedData", "ImportedOlisData", fsep = .Platform$file.sep)
DataInJaz <- file.path("..", "Data", "ImportedData", "ImportedJazEmData", fsep = .Platform$file.sep)

PlotsPath <- file.path("..", "Output", "Plots")
RDSPlotPath <- file.path("..", "Output", "PlotsRDS")

FileEncode <- "UTF-8" 
Delimiter <- ""
HeaderRows <- 0
```

# List and read imported Olis and Jaz files

```{r exported Rmd only first time in session}
list.files(path = DataInOlis, pattern = Project, full.names = TRUE)
list.files(path = DataInJaz, pattern = Project, full.names = TRUE)
```

```{r read imported Olis file}
OLISSpectraFile <- "../Data/ImportedData/ImportedOlisData/BalticO2_Imported_OlisData.Rds"
OLISSpectraFileName <- str_split(string = OLISSpectraFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")
OLISSpectra <- readRDS(OLISSpectraFile)  %>%
  ungroup()

JazFile <- "../Data/ImportedData/ImportedJazEmData/BalticO2_Imported_JazEmData.Rds"
JazFileName <- str_split(string = JazFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")
JazData <- readRDS(JazFile)  %>%
  ungroup()
```

# Preparing df for further analysis

```{r round nm}
JazData <- JazData %>%
   mutate(WavelengthRound = round(Wavelength))
colnames(JazData)

JazDataRound <- JazData %>%
group_by(FilenameJaz, WavelengthRound) %>%
  summarize(Counts, FilenameJaz, ObsDate, Strain, Par_ue, WL, WavelengthRound, CountsMean = mean(Counts)) %>%
ungroup()

JazDataRound <- JazDataRound %>%
  summarize(FilenameJaz, Strain, Par_ue, WL, WavelengthRound, CountsMean) %>%
  unique()

# JazDataRound <- JazDataRound %>%
#   filter(WavelengthRound >= 400 & WavelengthRound <= 700)
```



# Normalize Jaz emission to 405 nm

```{r Normalization Jaz emission at 405}
EmissionJaz405 <- JazDataRound %>%
  group_by(WL, Strain, Par_ue) %>%
  filter(WavelengthRound == 393) %>%
  mutate(EmJaz393 = CountsMean) %>%
  select(Strain, EmJaz393, Par_ue) %>%
  ungroup()

JazDataRoundMeta405 <- JazDataRound %>%
  filter(WL==405) %>% 
  left_join(., EmissionJaz405) %>%
  mutate(EmNormJaz393 = CountsMean / EmJaz393)

rm(EmissionJaz405)
```

# Normalize Jaz emission to 450 nm

```{r Normalization Jaz emission at 450}
EmissionJaz450 <- JazDataRound %>%
  group_by(WL, Strain, Par_ue) %>%
  filter(WavelengthRound == 441) %>%
  mutate(EmJaz441 = CountsMean) %>%
  select(Strain, EmJaz441, Par_ue) %>%
  ungroup()

JazDataRoundMeta450 <- JazDataRound %>%
  filter(WL==450) %>% 
  left_join(., EmissionJaz450) %>%
  mutate(EmNormJaz441 = CountsMean / EmJaz441)

rm(EmissionJaz450)
```

# Normalize Jaz emission to 470 nm

```{r Normalization Jaz emission at 470}
EmissionJaz470 <- JazDataRound %>%
  group_by(WL, Strain, Par_ue) %>%
  filter(WavelengthRound == 469) %>%
  mutate(EmJaz469 = CountsMean) %>%
  select(Strain, EmJaz469, Par_ue) %>%
  ungroup()

JazDataRoundMeta470 <- JazDataRound %>%
  filter(WL==470) %>% 
  left_join(., EmissionJaz470) %>%
  mutate(EmNormJaz469 = CountsMean / EmJaz469)

rm(EmissionJaz470)
```

# Normalize Jaz emission to 530 nm

```{r Normalization Jaz emission at 530}
EmissionJaz530 <- JazDataRound %>%
  group_by(WL, Strain, Par_ue) %>%
  filter(WavelengthRound == 521) %>%
  mutate(EmJaz521 = CountsMean) %>%
  select(Strain, EmJaz521, Par_ue) %>%
  ungroup()

JazDataRoundMeta530 <- JazDataRound %>%
  filter(WL==530) %>% 
  left_join(., EmissionJaz530) %>%
  mutate(EmNormJaz521 = CountsMean / EmJaz521)

rm(EmissionJaz530)
```

# Normalize Jaz emission to 620 nm

```{r Normalization Jaz emission at 620}
EmissionJaz620 <- JazDataRound %>%
  group_by(WL, Strain, Par_ue) %>%
  filter(WavelengthRound == 612) %>%
  mutate(EmJaz612 = CountsMean) %>%
  select(Strain, EmJaz612, Par_ue) %>%
  ungroup()

JazDataRoundMeta620 <- JazDataRound %>%
  filter(WL==620) %>% 
  left_join(., EmissionJaz620) %>%
  mutate(EmNormJaz612 = CountsMean / EmJaz612)

rm(EmissionJaz620)
```

# Normalize Jaz emission to 660 nm

```{r Normalization Jaz emission at 660}
EmissionJaz660 <- JazDataRound %>%
  group_by(WL, Strain, Par_ue) %>%
  filter(WavelengthRound == 647) %>%
  mutate(EmJaz647 = CountsMean) %>%
  select(Strain, EmJaz647, Par_ue) %>%
  ungroup()

JazDataRoundMeta660 <- JazDataRound %>%
  filter(WL==660) %>% 
  left_join(., EmissionJaz660) %>%
  mutate(EmNormJaz647 = CountsMean / EmJaz647)

rm(EmissionJaz660)
```

# Normalize Jaz emission to 730 nm

```{r Normalization Jaz emission at 730}
EmissionJaz730 <- JazDataRound %>%
  group_by(WL, Strain, Par_ue) %>%
  filter(WavelengthRound == 722) %>%
  mutate(EmJaz722 = CountsMean) %>%
  select(Strain, EmJaz722, Par_ue) %>%
  ungroup()

JazDataRoundMeta730 <- JazDataRound %>%
  filter(WL==730) %>% 
  left_join(., EmissionJaz730) %>%
  mutate(EmNormJaz722 = CountsMean / EmJaz722)

rm(EmissionJaz730)
```

# Normalize Jaz emission to WW

```{r Normalization Jaz emission at WW}
EmissionJazWW <- JazDataRound %>%
  group_by(WL, Strain, Par_ue) %>%
  filter(WavelengthRound == 600) %>%
  mutate(EmJaz600 = CountsMean) %>%
  select(Strain, EmJaz600, Par_ue) %>%
  ungroup()

JazDataRoundMetaWW <- JazDataRound %>%
  filter(WL== "WW") %>% 
  left_join(., EmissionJazWW) %>%
  mutate(EmNormJaz600 = CountsMean / EmJaz600)

rm(EmissionJazWW)
```
# Merge df to have all WL

```{r}
JazDataRoundMeta1 <- JazDataRoundMeta730 %>%
  full_join(., JazDataRoundMetaWW, by = c("FilenameJaz"= "FilenameJaz", "Strain" = "Strain", "Par_ue" = "Par_ue", "WL" = "WL", "WavelengthRound" = "WavelengthRound", "CountsMean" = "CountsMean"))
 
JazDataRoundMeta2 <- JazDataRoundMeta1 %>%
  full_join(., JazDataRoundMeta660, by = c("FilenameJaz"= "FilenameJaz", "Strain" = "Strain", "Par_ue" = "Par_ue", "WL" = "WL", "WavelengthRound" = "WavelengthRound", "CountsMean" = "CountsMean")) 

JazDataRoundMeta3 <- JazDataRoundMeta2 %>%
  full_join(., JazDataRoundMeta620, by = c("FilenameJaz"= "FilenameJaz", "Strain" = "Strain", "Par_ue" = "Par_ue", "WL" = "WL", "WavelengthRound" = "WavelengthRound", "CountsMean" = "CountsMean")) 

JazDataRoundMeta4 <- JazDataRoundMeta3 %>%
  full_join(., JazDataRoundMeta530, by = c("FilenameJaz"= "FilenameJaz", "Strain" = "Strain", "Par_ue" = "Par_ue", "WL" = "WL", "WavelengthRound" = "WavelengthRound", "CountsMean" = "CountsMean")) 

JazDataRoundMeta5 <- JazDataRoundMeta4 %>%
  full_join(., JazDataRoundMeta470, by = c("FilenameJaz"= "FilenameJaz", "Strain" = "Strain", "Par_ue" = "Par_ue", "WL" = "WL", "WavelengthRound" = "WavelengthRound", "CountsMean" = "CountsMean")) 

JazDataRoundMeta6 <- JazDataRoundMeta5 %>%
  full_join(., JazDataRoundMeta450, by = c("FilenameJaz"= "FilenameJaz", "Strain" = "Strain", "Par_ue" = "Par_ue", "WL" = "WL", "WavelengthRound" = "WavelengthRound", "CountsMean" = "CountsMean")) 

JazDataRoundMeta <- JazDataRoundMeta6 %>%
  full_join(., JazDataRoundMeta405, by = c("FilenameJaz"= "FilenameJaz", "Strain" = "Strain", "Par_ue" = "Par_ue", "WL" = "WL", "WavelengthRound" = "WavelengthRound", "CountsMean" = "CountsMean")) 


rm(JazDataRoundMeta1, JazDataRoundMeta2, JazDataRoundMeta3, JazDataRoundMeta4, JazDataRoundMeta5, JazDataRoundMeta6, JazDataRoundMeta405, JazDataRoundMeta450, JazDataRoundMeta470, JazDataRoundMeta530, JazDataRoundMeta620, JazDataRoundMeta660, JazDataRoundMeta730, JazDataRoundMetaWW)
```


# Merge Olis and Jaz data

```{r combine Olis spectra and Jaz data}
OLISSpectraMeta <- OLISSpectra %>%
  left_join(., JazDataRoundMeta, by = c("Par_ue" = "Par_ue", "nm" = "WavelengthRound" , "Strain" = "Strain", "WL" = "WL")) %>%
  unique()
```

# Estimate PUR

```{r estimate PUR}
OLISSpectraMetaPUR405 <- OLISSpectraMeta %>%
  filter(WL==405) %>% 
  mutate(PURNorm = (AbsNorm440*EmNormJaz393)) %>% 
  group_by(WL, Strain, Par_ue, Photoperiod, E_days, O2) %>%
  mutate(PURNormSum = sum(PURNorm)) %>% 
  mutate(SumEmNormJaz = sum(EmNormJaz393)) %>% 
  mutate(PUR = Par_ue*(PURNormSum/SumEmNormJaz)) %>% 
  ungroup() 

OLISSpectraMetaPUR450 <- OLISSpectraMeta %>%
  filter(WL==450) %>% 
  mutate(PURNorm = (AbsNorm440*EmNormJaz441)) %>% 
  group_by(WL, Strain, Par_ue, Photoperiod, E_days, O2) %>%
  mutate(PURNormSum = sum(PURNorm)) %>% 
  mutate(SumEmNormJaz = sum(EmNormJaz441)) %>% 
  mutate(PUR = Par_ue*(PURNormSum/SumEmNormJaz)) %>% 
  ungroup() 

OLISSpectraMetaPUR470 <- OLISSpectraMeta %>%
  filter(WL==470) %>% 
  mutate(PURNorm = (AbsNorm440*EmNormJaz469)) %>% 
  group_by(WL, Strain, Par_ue, Photoperiod, E_days, O2) %>%
  mutate(PURNormSum = sum(PURNorm)) %>% 
  mutate(SumEmNormJaz = sum(EmNormJaz469)) %>% 
  mutate(PUR = Par_ue*(PURNormSum/SumEmNormJaz)) %>% 
  ungroup() 

OLISSpectraMetaPUR530 <- OLISSpectraMeta %>%
  filter(WL==530) %>% 
  mutate(PURNorm = (AbsNorm440*EmNormJaz521)) %>% 
  group_by(WL, Strain, Par_ue, Photoperiod, E_days, O2) %>%
  mutate(PURNormSum = sum(PURNorm)) %>% 
  mutate(SumEmNormJaz = sum(EmNormJaz521)) %>% 
  mutate(PUR = Par_ue*(PURNormSum/SumEmNormJaz)) %>% 
  ungroup() 

OLISSpectraMetaPUR620 <- OLISSpectraMeta %>%
  filter(WL==620) %>% 
  mutate(PURNorm = (AbsNorm440*EmNormJaz612)) %>% 
  group_by(WL, Strain, Par_ue, Photoperiod, E_days, O2) %>%
  mutate(PURNormSum = sum(PURNorm)) %>% 
  mutate(SumEmNormJaz = sum(EmNormJaz612)) %>% 
  mutate(PUR = Par_ue*(PURNormSum/SumEmNormJaz)) %>% 
  ungroup() 

OLISSpectraMetaPUR660 <- OLISSpectraMeta %>%
  filter(WL==660) %>% 
  mutate(PURNorm = (AbsNorm440*EmNormJaz647)) %>% 
  group_by(WL, Strain, Par_ue, Photoperiod, E_days, O2) %>%
  mutate(PURNormSum = sum(PURNorm)) %>% 
  mutate(SumEmNormJaz = sum(EmNormJaz647)) %>% 
  mutate(PUR = Par_ue*(PURNormSum/SumEmNormJaz)) %>% 
  ungroup() 

OLISSpectraMetaPUR730 <- OLISSpectraMeta %>%
  filter(WL==730) %>% 
  mutate(PURNorm = (AbsNorm440*EmNormJaz722)) %>% 
  group_by(WL, Strain, Par_ue, Photoperiod, E_days, O2) %>%
  mutate(PURNormSum = sum(PURNorm)) %>% 
  mutate(SumEmNormJaz = sum(EmNormJaz722)) %>% 
  mutate(PUR = Par_ue*(PURNormSum/SumEmNormJaz)) %>% 
  ungroup() 

OLISSpectraMetaPURWW <- OLISSpectraMeta %>%
  filter(WL=="WW") %>% 
  mutate(PURNorm = (AbsNorm440*EmNormJaz600)) %>% 
  group_by(WL, Strain, Par_ue, Photoperiod, E_days, O2) %>%
  mutate(PURNormSum = sum(PURNorm)) %>% 
  mutate(SumEmNormJaz = sum(EmNormJaz600)) %>% 
  mutate(PUR = Par_ue*(PURNormSum/SumEmNormJaz)) %>% 
  ungroup() 

OLISSpectraMetaPUR<-rbind(OLISSpectraMetaPUR405, OLISSpectraMetaPUR450, OLISSpectraMetaPUR470, OLISSpectraMetaPUR530, OLISSpectraMetaPUR620, OLISSpectraMetaPUR660, OLISSpectraMetaPUR730, OLISSpectraMetaPURWW)

rm(OLISSpectraMetaPUR405, OLISSpectraMetaPUR450, OLISSpectraMetaPUR470, OLISSpectraMetaPUR530, OLISSpectraMetaPUR620, OLISSpectraMetaPUR660, OLISSpectraMetaPUR730, OLISSpectraMetaPURWW)
```

# Calculate daily PUR photon dose

```{r calculate PUR Photon dose}
OLISSpectraMetaPUR1 <- OLISSpectraMetaPUR %>%
  filter(Photoperiod != "24") %>% 
  mutate(PURPhotonDose_day =(PUR/2)*Photoperiod*3600)

OLISSpectraMetaPUR2 <- OLISSpectraMetaPUR %>%
  filter(Photoperiod == "24") %>% 
  mutate(PURPhotonDose_day = PUR*Photoperiod*3600)
  
  OLISSpectraMetaPUR <-rbind(OLISSpectraMetaPUR1, OLISSpectraMetaPUR2)
  rm(OLISSpectraMetaPUR1,OLISSpectraMetaPUR2)
```

# Filter unrevelant data

```{r filter unrevelant data}
OLISSpectraMetaPUR<-OLISSpectraMetaPUR %>% 
  filter(PUR>=0) %>% 
  filter(PUR<=180)
```

```{r Changes strain names}
OLISSpectraMetaPUR <- OLISSpectraMetaPUR %>%
      mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA77G"~"PC-rich_077"))
```

# Create plot

```{r Create plot}

OLISSpectraMetaPUR %>%
  filter(Par_ue!=30) %>% 
  # filter(E_days == 4 | E_days == 7 | E_days == 6) %>% 
  ggplot() +
  geom_area(aes(x = nm, y = EmNormJaz722, fill = "gray84"), alpha = 0.6, show.legend = F) +
  geom_area(aes(x = nm, y = EmNormJaz600, fill = "gray84"), alpha = 0.6, show.legend = F) +
  geom_area(aes(x = nm, y = EmNormJaz647, fill = "gray84"), alpha = 0.6, show.legend = F) +
  geom_area(aes(x = nm, y = EmNormJaz612, fill = "gray84"), alpha = 0.6, show.legend = F) +
  geom_area(aes(x = nm, y = EmNormJaz521, fill = "gray84"), alpha = 0.6, show.legend = F) +
  geom_area(aes(x = nm, y = EmNormJaz469, fill = "gray84"), alpha = 0.6, show.legend = F) +
  geom_area(aes(x = nm, y = EmNormJaz441, fill = "gray84"), alpha = 0.6, show.legend = F) +
  geom_area(aes(x = nm, y = EmNormJaz393, fill = "gray84"), alpha = 0.6, show.legend = F) +
  
  # geom_area(aes(x = nm, y = PURNorm, fill = "gray20"), alpha = 0.5, show.legend = F) +
  # geom_area(aes(x = nm, y = PURNormBA77G, fill = "palegreen3"), alpha = 0.5, show.legend = F) +
  geom_line(aes(x = nm, y = AbsNorm440, colour = as.factor(Strain)), show.legend = T, size = 0.4) +

  scale_color_manual(values = c("PC-rich_077" ="palegreen3", "PE-rich_127" ="brown4")) +
  # scale_linetype_manual(values = c("PC-rich_077" ="solid", "PE-rich_127" ="longdash")) +
  stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = -0.025, alpha = 0.5) +
  scale_fill_identity() +
  labs(y = "Normalized absorbance", x = "Wavelength (nm)") +
  scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  coord_cartesian(ylim = c (-0.01, 1.6)) +
  ggh4x::facet_nested(cols = vars(WL), rows = vars(Strain, O2),labeller = labeller(Ex_WL = label_value, WL = label_value)) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        panel.spacing.x = unit(0.4, 'cm'),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.title = element_blank(),
        legend.direction="horizontal",
        legend.position = c(0.08,0.97),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text.align = 0,
        legend.key.width= unit(0.3, 'cm'),
        legend.text = element_text(size=10))
```

# Save plot 

```{r save plot}
ggsave(file = file.path(PlotsPath, paste("OlisSpectra_Plot",".png",sep = "")), height=10, width= 8,  dpi = 300, limitsize = TRUE)
```

# Cleaning df before saving as rds and removed unnecessary files from the environment

```{r delete unused df from the environment}
rm(JazData, JazDataRound, JazDataRoundMeta, OLISSpectraMeta, OLISSpectra)
```

# Create tidy df without all nm

```{r clean df, create smaller df - without absorbance and all nm}
OLISAllPURTidy<-OLISSpectraMetaPUR %>% 
  select(-c(Absorbance, nm, Abs440, AbsNorm440, EmJaz393, EmNormJaz393, EmJaz441, EmNormJaz441, EmJaz469, EmNormJaz469, EmJaz521, EmNormJaz521, EmJaz612, EmNormJaz612, EmJaz647, EmNormJaz647, EmJaz600, EmNormJaz600, EmJaz722, EmNormJaz722, PURNorm, CountsMean, SumAbNorm, PURNormSum, SumEmNormJaz)) %>% 
  unique()

OLISAllPURTidy<-OLISAllPURTidy %>% 
  group_by(Strain, Par_ue, Photoperiod, E_days, MC, Run, O2) %>%
  mutate(PURPARRatio = PUR/Par_ue) %>% 
ungroup()

OLISAllPURTidy <- OLISAllPURTidy %>% 
  mutate(E_hours = E_days*24) %>% 
  filter(PURPARRatio<=1) %>% 
  filter(PURPARRatio>0)
```

# Create preliminary PUR/PAR ratio plot

```{r preliminary plot}
lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

OLISAllPURTidy %>%
  filter(Par_ue!=30) %>% 
  ggplot() +
  geom_point(aes(x = E_hours, y = PURPARRatio, colour = as.factor(Strain)), alpha = 0.9, size = 3, show.legend = T) +
  scale_colour_discrete(type=c("palegreen3", "brown4"), name="", labels = lab1) +
  scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  coord_cartesian(ylim = c(0, 1.7)) +
  ggh4x::facet_nested(cols = vars(WL), rows = vars(O2), labeller = label_parsed) +
  theme_bw()
```
# Save plot 

```{r save plot}
ggsave(file = file.path(PlotsPath, paste("PURPARRatio_Plot",".png",sep = "")), height=10, width= 8,  dpi = 300, limitsize = TRUE)
```


# Save rds for further analysis

```{r save rds}
saveRDS(OLISSpectraMetaPUR, file.path(DataOut, paste(Project, "Processed_OlisSpectraAll.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

saveRDS(OLISAllPURTidy, file.path(DataOut, paste(Project, "Processed_OlisSpectraTidy.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

# saveRDS(OLISSpectraMetaPURShort, file.path(RDSPlotPath, paste(Project, "Plot_OlisSpectra.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Variable names used in Data Dictionary

```{r}
colnames(OLISSpectraMetaPUR)
```

# Variable names used in Data Dictionary

```{r}
colnames(OLISAllPURTidy)
```

