---
title: "Process_GrowthRateData"
author:
- Sylwia Sliwinska-Wilczewska
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: BalticPhotoperiod.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

Process_GrowthRateData.Rmd processes and combines PICO_Cleaned_MCData.Rds from Data/CleanedData/CleanedMCData folder and both BalticPhotoperiod_Processed_PigmentsAll.Rds and BalticPhotoperiod_Processed_PigmentsExp.Rds from Data/ProcessedData/ProcessedPigmentsData. This .Rmd generates BalticPhotoperiod_Processed_GrowthRateAll.Rds (stored in Data/ProcessedData/ProcessesGrowthRateData folder) and 2 plots (stored in Output/Figures folder).

# Load Libraries and set Project Variables

```{r load libraries} 
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(strucchange)
library(ggpubr)
library(caret)
library(reshape2)
library(gcookbook)
library(ggspectra)
library(photobiologyWavebands)
library(photobiology)
library(scales)
library(minpack.lm) #Standard 'nls' framework that uses 'nls.lm' for fitting
library(data.table)
library(googledrive)
library(googlesheets4)
library(tidyverse)
library("patchwork") # merging plots

```

```{r set project variables}
Project <- "BalticO2"
DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedGrowthRateData")
DataIn <- file.path("..", "Data", "CleanedData", "CleanedMCData", fsep = .Platform$file.sep)

FigPath <- file.path("..", "Output", "Figures")
FigRdsPath <- file.path("..", "Output", "FiguresRds")
TableRdsPath <- file.path("..", "Output", "TablesRDS")

FileEncode <- "UTF-8" 
Delimiter <- ""
HeaderRows <- 0
```

# List and read files

```{r Exported Rmd only first time in session}
list.files(path = DataIn, full.names = TRUE)
```

```{r read file}
MultiCultiGrowthFile <- "../Data/CleanedData/CleanedMCData/PICO_Cleaned_MCData.Rds"

MultiCultiGrowthFileName <- str_split(string = MultiCultiGrowthFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 

MultiCultiGrowth <- readRDS(MultiCultiGrowthFile)  %>%
  ungroup()
```

# Select revelant variables and preparing for further analysis

```{r}
MultiCultiGrowth<-MultiCultiGrowth %>% 
  dplyr::select(c(Tube, ExpDate, MC, Run, SampleID, Strain, Par_ue, Photoperiod, WL, O2, LightShape, PARPhotonDose_day, OD720_Lmu_se, OD720_Lmu_corr, deltaOD_Lmu_se, deltaOD_Lmu_corr))
  
MultiCultiGrowth<-MultiCultiGrowth %>% 
  mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA77G"~"PC-rich_077"))

```


# Growth rate per day

```{r}
MultiCultiGrowth<-MultiCultiGrowth %>% 
  mutate(deltaOD_Lmu_corr=deltaOD_Lmu_corr*24)
```

# Adding facets labels

```{r}
MultiCultiGrowth<-MultiCultiGrowth %>% 
  mutate(Oxygen=case_when(O2==21~"250~µM",
         O2==0~"2.5~µM"))
```


```{r}
MultiCultiGrowth %>%
  filter(WL != "WW") %>% 
  ggplot() +
  geom_point(aes(x = WL, y = deltaOD_Lmu_corr,colour=as.factor(Strain)), size = 3.5, alpha = 0.9, show.legend = T) +
  ggh4x::facet_nested(cols = vars(Oxygen), rows = vars(Strain)) +
  theme_bw()
```

```{r}
lab1=c(expression("PC-rich_077"), expression("PE-rich_127"))

MultiCultiGrowth %>%
  mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(WL != "WW") %>%
  ggplot() +
  geom_point(aes(x = WLNum, y = deltaOD_Lmu_corr, colour = as.factor(Strain), shape = as.factor(Strain)), size = 4, show.legend = T) +
  geom_line(aes(x = WLNum, y = deltaOD_Lmu_corr, colour = as.factor(Strain), linetype = as.factor(Strain)), show.legend = F) +
  # geom_errorbar(aes(x = WLNum, ymin = deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = deltaOD_Lmu_corr + deltaOD_Lmu_se, colour = as.factor(Strain)), width=20, size=0.3, show.legend = F) +
  
  stat_wl_strip(aes(x = WLNum), ymin = -Inf, ymax = -0.025, alpha = 0.5) +
  scale_fill_identity() +
  scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab1) +
  scale_shape_manual(values = c(16, 18), name="", labels = lab1) +
  scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab1) +
  labs(y = "Chlorophyll-specific exponential growth rate " ~ "("~d^-1~")", x = "Growth wavelength (nm)") +
  #scale_x_continuous(breaks=seq(0, 200, by = 50)) +
  #coord_cartesian(xlim = c (0, 200)) +
  #coord_cartesian(xlim = c (400, 800)) +
  # guides(colour = FALSE) +
  #ggh4x::facet_nested(rows = vars(O2), cols = vars(Strain), labeller = label_parsed) +
  labs(y = "µ " ~ "("~d^-1~")", x = "Wavelength (nm)") +
  ggh4x::facet_nested(rows = vars(factor(Oxygen, levels=c("250~µM","2.5~µM"))), labeller = label_parsed) +
 #ggh4x::facet_nested(cols = vars(Strain), rows = vars(factor(O2, levels=c("21","0"))), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        panel.spacing.x = unit(0.4, 'cm'),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.position = c(0.10,0.90),
        legend.text = element_text(size=10))

```

# Save plot 

```{r save plot}
ggsave(file = file.path(FigPath, paste("Fig_GrowthRate",".png",sep = "")), height=5.5, width= 6,  dpi = 300, limitsize = TRUE)
```


```{r}
lab1=c(expression("PC-rich_077"), expression("PE-rich_127"))

MultiCultiGrowth %>%
  mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(WL != "WW") %>%
  ggplot() +
  geom_point(aes(x = WLNum, y = deltaOD_Lmu_corr, colour = as.factor(Strain), shape = as.factor(Strain)), size = 4, show.legend = T) +
  geom_line(aes(x = WLNum, y = deltaOD_Lmu_corr, colour = as.factor(Strain), linetype = as.factor(Strain)), show.legend = F) +
  # geom_errorbar(aes(x = WLNum, ymin = deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = deltaOD_Lmu_corr + deltaOD_Lmu_se, colour = as.factor(Strain)), width=50, size=0.3, show.legend = F) +
  scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab1) +
  scale_shape_manual(values = c(16, 18), name="", labels = lab1) +
  scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab1) +
  
  stat_wl_strip(aes(x = WLNum), ymin = -Inf, ymax = -0.04, alpha = 0.5) +
  scale_fill_identity() +
  labs(y = "µ " ~ "("~d^-1~")", x = "Growth wavelength (nm)") +
  # scale_x_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  # coord_cartesian(xlim = c (0, 1.2)) +

  coord_flip()+
  ggh4x::facet_nested(rows = vars(factor(Oxygen, levels=c("250~µM","2.5~µM"))), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        panel.spacing.x = unit(0.4, 'cm'),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.position = c(0.15,0.85),
        legend.text = element_text(size=10))
```
# Save plot 

```{r save plot}
ggsave(file = file.path(FigPath, paste("Fig_GrowthRate2",".png",sep = "")), height=5.5, width= 6,  dpi = 300, limitsize = TRUE)
```



-----------------------------------------------------------------------------------------------------------


# Calculated Anova and Tukey test

```{r calculated statistics}
MultiCultiGrowth2<-MultiCultiGrowth %>% 
  filter(WL != "WW")

MCGrowthRateStats<-rbind(MultiCultiGrowth2, MultiCultiGrowth2) #I created double data here

MCGrowthRateStats$O2 <- factor(MCGrowthRateStats$O2)
MCGrowthRateStats$WL <- factor(MCGrowthRateStats$WL)
MCGrowthRateStats$Strain <- factor(MCGrowthRateStats$Strain)

# Two way Anova with interactions
model<-aov(deltaOD_Lmu_corr~O2*WL*Strain, data=MCGrowthRateStats)
AnovaTest_GrowthRate<-data.frame(unclass(summary(model)), check.names = FALSE, stringsAsFactors = FALSE)
TukeyHSDTest_GrowthRate<-TukeyHSD(model, which = c("O2", "WL", "Strain"))
```



# Save RDS that create stats and tables

```{r}
saveRDS(AnovaTest_GrowthRate, file.path(TableRdsPath, paste(Project, "Anova_GrowthRate.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

saveRDS(TukeyHSDTest_GrowthRate, file.path(TableRdsPath, paste(Project, "HSD_GrowthRate.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Cleaning the environment

```{r}
rm(MCGrowthRateStats, model, MultiCultiGrowth2)
```

# Save Rds for further analysis

```{r save rds}
saveRDS(MultiCultiGrowth, file.path(DataOut, paste(Project, "Processed_GrowthRate.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

```


------------------------------------------------------------------------------------------------------------------
-------------------------------------------------------------------------------------------------------------------



```{r set project variables}
Project <- "BalticO2"
DataIn <- file.path("..", "Data", "ImportedData", "ImportedJazEmData", fsep = .Platform$file.sep)
```

# List and read processed Olis and Jaz files

```{r exported Rmd only first time in session}
list.files(path = DataIn, pattern = Project, full.names = TRUE)
```

```{r read imported pigments Exp file}
JazDataFile <- "../Data/ImportedData/ImportedJazEmData/BalticO2_Imported_JazEmData.Rds"
JazDataFileName <- str_split(string = JazDataFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")
JazData <- readRDS(JazDataFile)  %>%
  ungroup()

JazData<-JazData %>% 
  select(-c(MCMeasuredPar_uE, MCSetPar_uE))
```


```{r Preliminary plot}

JazData %>%
  ggplot() +
  geom_point(aes(x = MCEm_nm, y = Emission, colour = as.factor(WL))) +
  geom_text(aes(x = EmMax_nm, y= max(Emission), label= EmMax_nm), alpha = 0.5 ,hjust = 0.5, vjust=-0.5) +
  geom_vline(aes(xintercept = EmMax_nm), linetype = "dashed") +
  scale_y_continuous(limits = c(0,100000)) +
  ggh4x::facet_nested(rows = vars(MC, WL), labeller = labeller(WL = label_both, Par = label_both, MultiCulti = label_both)) +
  theme_bw() 
```
# Normalize Jaz emission to 405 nm

```{r Normalization Jaz emission at 405}
EmissionJaz405 <- JazData %>%
  filter(WL==405) %>% 
  filter(MCEm_nm == 393) %>%
  mutate(EmJaz393 = Emission) %>%
  select(EmJaz393) 

JazDataRoundMeta405 <- JazData %>%
  filter(WL==405) %>% 
  cross_join(., EmissionJaz405) %>%
  mutate(EmNormJaz393 = Emission / EmJaz393)

rm(EmissionJaz405)
```

# Normalize Jaz emission to 450 nm

```{r Normalization Jaz emission at 450}
EmissionJaz450 <- JazData %>%
  filter(WL==450) %>% 
  filter(MCEm_nm == 441) %>%
  mutate(EmJaz441 = Emission) %>%
  select(EmJaz441)

JazDataRoundMeta450 <- JazData %>%
  filter(WL==450) %>% 
  cross_join(., EmissionJaz450) %>%
  mutate(EmNormJaz441 = Emission / EmJaz441)

rm(EmissionJaz450)
```

# Normalize Jaz emission to 470 nm

```{r Normalization Jaz emission at 470}
EmissionJaz470 <- JazData %>%
  filter(WL==470) %>% 
  filter(MCEm_nm == 469) %>%
  mutate(EmJaz469 = Emission) %>%
  select(EmJaz469) 

JazDataRoundMeta470 <- JazData %>%
  filter(WL==470) %>% 
  cross_join(., EmissionJaz470) %>%
  mutate(EmNormJaz469 = Emission / EmJaz469)

rm(EmissionJaz470)
```

# Normalize Jaz emission to 530 nm

```{r Normalization Jaz emission at 530}
EmissionJaz530 <- JazData %>%
  filter(WL==530) %>% 
  filter(MCEm_nm == 521) %>%
  mutate(EmJaz521 = Emission) %>%
  select(EmJaz521)

JazDataRoundMeta530 <- JazData %>%
  filter(WL==530) %>% 
  cross_join(., EmissionJaz530) %>%
  mutate(EmNormJaz521 = Emission / EmJaz521)

rm(EmissionJaz530)
```

# Normalize Jaz emission to 620 nm

```{r Normalization Jaz emission at 620}
EmissionJaz620 <- JazData %>%
  filter(WL==620) %>% 
  filter(MCEm_nm == 612) %>%
  mutate(EmJaz612 = Emission) %>%
  select(EmJaz612) 

JazDataRoundMeta620 <- JazData %>%
  filter(WL==620) %>% 
  cross_join(., EmissionJaz620) %>%
  mutate(EmNormJaz612 = Emission / EmJaz612)

rm(EmissionJaz620)
```

# Normalize Jaz emission to 660 nm

```{r Normalization Jaz emission at 660}
EmissionJaz660 <- JazData %>%
  filter(WL==660) %>% 
  filter(MCEm_nm == 647) %>%
  mutate(EmJaz647 = Emission) %>%
  select(EmJaz647)

JazDataRoundMeta660 <- JazData %>%
  filter(WL==660) %>% 
  cross_join(., EmissionJaz660) %>%
  mutate(EmNormJaz647 = Emission / EmJaz647)

rm(EmissionJaz660)
```

# Normalize Jaz emission to 730 nm

```{r Normalization Jaz emission at 730}
EmissionJaz730 <- JazData %>%
  filter(WL==730) %>% 
  filter(MCEm_nm == 722) %>%
  mutate(EmJaz722 = Emission) %>%
  select(EmJaz722) 

JazDataRoundMeta730 <- JazData %>%
  filter(WL==730) %>% 
  cross_join(., EmissionJaz730) %>%
  mutate(EmNormJaz722 = Emission / EmJaz722)

rm(EmissionJaz730)
```

# Normalize Jaz emission to WW

```{r Normalization Jaz emission at WW}
EmissionJazWW <- JazData %>%
  filter(WL== "WW") %>%
  filter(MCEm_nm == 600) %>%
  mutate(EmJaz600 = Emission) %>%
  select(EmJaz600) 

JazDataRoundMetaWW <- JazData %>%
  filter(WL== "WW") %>%
  cross_join(., EmissionJazWW) %>%
  mutate(EmNormJaz600 = Emission / EmJaz600)

rm(EmissionJazWW)
```
# Merge df to have all WL

```{r}
JazDataRoundMeta1 <- JazDataRoundMeta730 %>%
  full_join(., JazDataRoundMetaWW, by = c("FilenameJaz"= "FilenameJaz", "WL" = "WL", "MCEm_nm" = "MCEm_nm", "Emission" = "Emission", "MC"="MC", "EmMax_nm"="EmMax_nm", "ObsDateJaz"="ObsDateJaz"))
 
JazDataRoundMeta2 <- JazDataRoundMeta1 %>%
  full_join(., JazDataRoundMeta660, by = c("FilenameJaz"= "FilenameJaz", "WL" = "WL", "MCEm_nm" = "MCEm_nm", "Emission" = "Emission", "MC"="MC", "EmMax_nm"="EmMax_nm", "ObsDateJaz"="ObsDateJaz")) 

JazDataRoundMeta3 <- JazDataRoundMeta2 %>%
  full_join(., JazDataRoundMeta620, by = c("FilenameJaz"= "FilenameJaz", "WL" = "WL", "MCEm_nm" = "MCEm_nm", "Emission" = "Emission", "MC"="MC", "EmMax_nm"="EmMax_nm", "ObsDateJaz"="ObsDateJaz")) 

JazDataRoundMeta4 <- JazDataRoundMeta3 %>%
  full_join(., JazDataRoundMeta530, by = c("FilenameJaz"= "FilenameJaz", "WL" = "WL", "MCEm_nm" = "MCEm_nm", "Emission" = "Emission", "MC"="MC", "EmMax_nm"="EmMax_nm", "ObsDateJaz"="ObsDateJaz")) 

JazDataRoundMeta5 <- JazDataRoundMeta4 %>%
  full_join(., JazDataRoundMeta470, by = c("FilenameJaz"= "FilenameJaz", "WL" = "WL", "MCEm_nm" = "MCEm_nm", "Emission" = "Emission", "MC"="MC", "EmMax_nm"="EmMax_nm", "ObsDateJaz"="ObsDateJaz")) 

JazDataRoundMeta6 <- JazDataRoundMeta5 %>%
  full_join(., JazDataRoundMeta450, by = c("FilenameJaz"= "FilenameJaz", "WL" = "WL", "MCEm_nm" = "MCEm_nm", "Emission" = "Emission", "MC"="MC", "EmMax_nm"="EmMax_nm", "ObsDateJaz"="ObsDateJaz")) 

JazDataRoundMeta <- JazDataRoundMeta6 %>%
  full_join(., JazDataRoundMeta405, by = c("FilenameJaz"= "FilenameJaz", "WL" = "WL", "MCEm_nm" = "MCEm_nm", "Emission" = "Emission", "MC"="MC", "EmMax_nm"="EmMax_nm", "ObsDateJaz"="ObsDateJaz")) 


rm(JazDataRoundMeta1, JazDataRoundMeta2, JazDataRoundMeta3, JazDataRoundMeta4, JazDataRoundMeta5, JazDataRoundMeta6, JazDataRoundMeta405, JazDataRoundMeta450, JazDataRoundMeta470, JazDataRoundMeta530, JazDataRoundMeta620, JazDataRoundMeta660, JazDataRoundMeta730, JazDataRoundMetaWW)
```

```{r}
JazDataRoundMeta<-JazDataRoundMeta %>% 
  rename(nm=MCEm_nm) %>% 
  select(-c(MC))
```


```{r}
MultiCultiGrowth1<-MultiCultiGrowth %>% 
  mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(WL != "WW") 
```
```{r}
JazDataRoundMeta21<-JazDataRoundMeta 
  JazDataRoundMeta21$Oxygen<-"250~µM"
  
JazDataRoundMeta0<-JazDataRoundMeta 
  JazDataRoundMeta0$Oxygen<-"2.5~µM"

JazDataRoundMeta2<-rbind(JazDataRoundMeta21, JazDataRoundMeta0)
rm(JazDataRoundMeta21, JazDataRoundMeta0)
```


```{r Create plot}
lab1=c(expression("PC-rich_077"), expression("PE-rich_127"))

JazDataRoundMeta2 %>%
  ggplot() +
  geom_area(aes(x = nm, y = EmNormJaz722, fill = "indianred4"), alpha = 0.1, show.legend = F) +
  #geom_area(aes(x = nm, y = EmNormJaz600, fill = "gray84"), alpha = 0.6, show.legend = F) +
  geom_area(aes(x = nm, y = EmNormJaz647, fill = "brown1"), alpha = 0.1, show.legend = F) +
  geom_area(aes(x = nm, y = EmNormJaz612, fill = "coral"), alpha = 0.1, show.legend = F) +
  geom_area(aes(x = nm, y = EmNormJaz521, fill = "limegreen"), alpha = 0.1, show.legend = F) +
  geom_area(aes(x = nm, y = EmNormJaz469, fill = "lightseagreen"), alpha = 0.1, show.legend = F) +
  geom_area(aes(x = nm, y = EmNormJaz441, fill = "steelblue3"), alpha = 0.1, show.legend = F) +
  geom_area(aes(x = nm, y = EmNormJaz393, fill = "royalblue4"), alpha = 0.1, show.legend = F) +
  
  geom_point(aes(x = WLNum, y = deltaOD_Lmu_corr, colour = as.factor(Strain), shape = as.factor(Strain)), size = 4, show.legend = T, MultiCultiGrowth1) +
  geom_line(aes(x = WLNum, y = deltaOD_Lmu_corr, colour = as.factor(Strain), linetype = as.factor(Strain)), show.legend = F, MultiCultiGrowth1) +
  scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab1) +
  scale_shape_manual(values = c(16, 18), name="", labels = lab1) +
  scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab1) +
  
  stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = -0.025, alpha = 0.5) +
  scale_fill_identity() +
  labs(y = "µ " ~ "("~d^-1~") and normalized emission spectra", x = "Growth wavelength (nm)") +
  #labs(y = "Normalized absorbance", x = "Wavelength (nm)") +
  # scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  # coord_cartesian(ylim = c (-0.01, 1.6)) +
  #ggh4x::facet_nested(rows = vars(factor(O2)),labeller = labeller(Ex_WL = label_value, WL = label_value)) +
  ggh4x::facet_nested(rows = vars(factor(Oxygen, levels=c("250~µM","2.5~µM"))), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        panel.spacing.x = unit(0.4, 'cm'),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.position = c(0.15,0.90),
        legend.text = element_text(size=10))
```

# Save plot 

```{r save plot}
ggsave(file = file.path(FigPath, paste("Fig_GrowthRate3",".png",sep = "")), height=5.5, width= 6,  dpi = 300, limitsize = TRUE)
```


```{r Create plot}
lab1=c(expression("PC-rich_077"), expression("PE-rich_127"))

JazDataRoundMeta2 %>%
  ggplot() +
  geom_area(aes(x = nm, y = EmNormJaz722, fill = "indianred4"), alpha = 0.1, show.legend = F) +
  #geom_area(aes(x = nm, y = EmNormJaz600, fill = "gray84"), alpha = 0.6, show.legend = F) +
  geom_area(aes(x = nm, y = EmNormJaz647, fill = "brown1"), alpha = 0.1, show.legend = F) +
  geom_area(aes(x = nm, y = EmNormJaz612, fill = "coral"), alpha = 0.1, show.legend = F) +
  geom_area(aes(x = nm, y = EmNormJaz521, fill = "limegreen"), alpha = 0.1, show.legend = F) +
  geom_area(aes(x = nm, y = EmNormJaz469, fill = "lightseagreen"), alpha = 0.1, show.legend = F) +
  geom_area(aes(x = nm, y = EmNormJaz441, fill = "steelblue3"), alpha = 0.1, show.legend = F) +
  geom_area(aes(x = nm, y = EmNormJaz393, fill = "royalblue4"), alpha = 0.1, show.legend = F) +
  
  geom_point(aes(x = WLNum, y = deltaOD_Lmu_corr, colour = as.factor(Strain), shape = as.factor(Strain)), size = 4, show.legend = T, MultiCultiGrowth1) +
  geom_line(aes(x = WLNum, y = deltaOD_Lmu_corr, colour = as.factor(Strain), linetype = as.factor(Strain)), show.legend = F, MultiCultiGrowth1) +
  scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab1) +
  scale_shape_manual(values = c(16, 18), name="", labels = lab1) +
  scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab1) +
  
  stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = -0.04, alpha = 0.5) +
  scale_fill_identity() +
  coord_flip()+
  
  labs(y = "µ " ~ "("~d^-1~") and normalized emission spectra", x = "Growth wavelength (nm)") +
  #labs(y = "Normalized absorbance", x = "Wavelength (nm)") +
  # scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  # coord_cartesian(ylim = c (-0.01, 1.6)) +
  #ggh4x::facet_nested(rows = vars(factor(O2)),labeller = labeller(Ex_WL = label_value, WL = label_value)) +
  ggh4x::facet_nested(rows = vars(factor(Oxygen, levels=c("250~µM","2.5~µM"))), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        panel.spacing.x = unit(0.4, 'cm'),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.position = c(0.15,0.90),
        legend.text = element_text(size=10))
```

# Save plot 

```{r save plot}
ggsave(file = file.path(FigPath, paste("Fig_GrowthRate4",".png",sep = "")), height=8, width= 6,  dpi = 300, limitsize = TRUE)
```


-------------------------------------------------------------------------------------------

```{r set project variables}
Project <- "BalticO2"
DataIn <- file.path("..", "Data", "ProcessedData", "ProcessedOlisJazData", fsep = .Platform$file.sep)
```

# List and read processed Olis and Jaz files

```{r exported Rmd only first time in session}
list.files(path = DataIn, pattern = Project, full.names = TRUE)
```

```{r read imported pigments Exp file}
OlisFile <- "../Data/ProcessedData/ProcessedOlisJazData/BalticO2_Processed_OlisSpectraTidy.Rds"
OlisFileName <- str_split(string = OlisFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")
Olis <- readRDS(OlisFile)  %>%
  ungroup()

```


# Combine growth rate and Exp pigments to get PUR

```{r}
MCGrowthRate <- MultiCultiGrowth %>% 
  left_join(., Olis, by = c("Run" = "Run", "SampleID" = "SampleID","Strain" = "Strain", "Par_ue" = "Par_ue", "Photoperiod" = "Photoperiod",  "O2" = "O2", "WL" = "WL", "Tube" = "Tube", "ExpDate" = "ExpDate", "LightShape" = "LightShape", "PARPhotonDose_day" = "PARPhotonDose_day")) 
  
```

# Save Rds for further analysis

```{r save rds}
saveRDS(MCGrowthRate, file.path(DataOut, paste(Project, "Processed_GrowthRatePUR.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

```



